---
title: "CanadaLogin Reporting Readership"
author: "EDCP Data and Research Team"  # colin.douglas@cds-snc.ca
slug: readership
format:
  dashboard:
    # Written by the setup chunk at render time
    include-before-body: page-header.html
    include-after-body: analytics-tag.html # see _analytics.qmd
params:
  ga_page_title: "Reporting Readership Dashboard"
---

```{r setup}
#| include: false

# The working directory is this folder; the shared layer is two levels up.
source("../../common/setup.R")

source("R/metrics.R")
source("R/preflight.R")

con <- connect_athena()

# A failed check adds a banner. See R/preflight.R.
preflight <- run_preflight_safety_check(con)
write_preflight_status(preflight)

traffic <- page_traffic(con)
events <- page_events(con)

# The newest day exported. A day nobody read leaves no rows, so this comes
# from the export, not the meta tables.
through <- export_through(con)

editions <- edition_list(traffic)
coverage <- edition_coverage(editions, through)
days <- edition_days(traffic, editions)
cumulative <- cumulative_views(days, coverage)

# Editions with all of their first 14 days tracked, newest last, and the
# newest one with any days at all: the one in the value boxes.
comparable <- dplyr::filter(coverage, comparable, days_seen > 0)
latest <- dplyr::slice_tail(comparable, n = 1)
complete <- dplyr::filter(coverage, complete, number != latest$number)

dashboards <- dashboard_list(traffic)

# Three months, as whole Monday-to-Sunday weeks, for every daily or weekly
# chart.
chart_from <- monday_of(through) - 12L * 7L

page_header <- "page-header.html"

write_preflight_banner(preflight, page_header)

cat(
  c(
    '<div class="page-strip">',
    glue("  <p><strong>Data through {format_long_date(through)}.</strong> ",
         "Internal to Enterprise Digital Credentials, not for public ",
         "consumption.</p>"),
    "</div>"
  ),
  file = page_header, sep = "\n", append = TRUE
)

# Presentation ---------------------------------------------------------------

# Chart colours from _theme.scss: margin red for the newest Signal Check and
# our own links, sepia ink for the rest, paper behind.
palette <- list(accent = "#A63A26", ink = "#3B2A20", quiet = "#D6CBB9")

# One ink per Signal Check in the daily chart, cycled oldest first so
# neighbours differ; the newest takes the margin red.
inks <- c("#3B2A20", "#2F4E7A", "#B98A2E", "#4E6E3A", "#6E4A7E", "#7C8791")

# Where a session started, in legend order. Our own links take the accent.
source_colours <- c(
  slack = unname(colors$brand["blue"]),
  teams = unname(colors$brand["green"]),
  email = unname(colors$brand["orange"]),
  our_links = palette$accent,
  direct = "#9AA3AB",
  other = "#D3D7DB"
)

# A one-row legend above the plot, flush left.
legend_top <- theme(legend.position = "top", legend.justification = "left",
                    legend.key.size = unit(0.35, "cm"),
                    legend.text = element_text(margin = margin(r = 12)),
                    legend.margin = margin(0, 0, 0, 0))

# Weekly bars sit mid-week (Monday + 3). A tick under every second bar,
# counting back from the newest, labelled with the Sunday the week ends.
week_axis <- function(weeks) {
  scale_x_date(breaks = seq(max(weeks), min(weeks), by = "-2 weeks") + 3L,
               labels = \(x) format_short_date(x + 3L))
}

brand_figure <- function(p, height = 0.09) {
  add_cds_logo(
    add_watermark(p, report_name = "CanadaLogin Reporting Readership",
                  date = through),
    height = height
  )
}

# One panel per page: its curve over the others', a dashed line at half, and
# its views and median read in the corner. `colours`, by panel, overrides accent.
dwell_panels <- function(curve, panel, ncol, colours = NULL) {
  curve <- dplyr::mutate(curve, panel = .data[[panel]])
  others <- curve |>
    dplyr::rename(other = panel) |>
    tidyr::crossing(panel = unique(curve$panel)) |>
    dplyr::filter(other != panel)
  counts <- curve |>
    dplyr::group_by(panel) |>
    dplyr::summarise(
      label = paste0(comma(dplyr::first(page_views)), " views\n",
                     "median ", fmt_read(median_read(seconds, share))),
      .groups = "drop"
    )

  ggplot(curve, aes(seconds, share)) +
    geom_hline(yintercept = 0.5, linetype = "dashed", colour = "grey55",
               linewidth = 0.35) +
    geom_line(data = others, aes(group = other), colour = palette$quiet,
              linewidth = 0.5) +
    geom_line(aes(colour = panel), linewidth = 1) +
    geom_point(aes(colour = panel), size = 1.4) +
    geom_text(data = counts, aes(x = 600, y = 1, label = label),
              inherit.aes = FALSE, hjust = 1, vjust = 1, size = 3,
              lineheight = 0.9, colour = "grey35") +
    scale_colour_manual(
      values = colours %||% setNames(rep(palette$accent, length(unique(curve$panel))),
                                     unique(as.character(curve$panel))),
      guide = "none"
    ) +
    scale_x_log10(breaks = dwell_marks, labels = fmt_mark_short(dwell_marks)) +
    scale_y_continuous(labels = label_percent(), limits = c(0, 1),
                       breaks = c(0, 0.5, 1)) +
    facet_wrap(~panel, ncol = ncol) +
    theme_cds() +
    theme(panel.grid.minor = element_blank(),
          strip.background = element_blank(),
          strip.text = element_text(face = "bold", hjust = 0, size = 11)) +
    labs(x = "Time on the page, visible", y = "Page views still open")
}

# Sessions by where they started, one stacked bar per row of `group`, in the
# order of `levels` from the top.
source_bars <- function(rows, group, levels) {
  rows <- rows |>
    dplyr::mutate(row = factor(.data[[group]], levels = rev(levels)),
                  source = factor(source_group(sessionsource),
                                  levels = rev(source_groups$group))) |>
    dplyr::group_by(row, source) |>
    dplyr::summarise(sessions = sum(sessions), .groups = "drop")
  totals <- rows |>
    dplyr::group_by(row) |>
    dplyr::summarise(sessions = sum(sessions), .groups = "drop")

  ggplot(rows, aes(sessions, row)) +
    geom_col(aes(fill = source), width = 0.7) +
    geom_text(data = totals, aes(label = comma(sessions)), hjust = -0.3,
              size = 3.2, colour = "grey30") +
    scale_fill_manual(values = source_colours,
                      labels = setNames(source_groups$label, source_groups$group),
                      breaks = source_groups$group, name = NULL) +
    scale_x_continuous(expand = expansion(mult = c(0, 0.08))) +
    guides(fill = guide_legend(nrow = 1)) +
    theme_cds() +
    theme(panel.grid.minor = element_blank(),
          panel.grid.major.y = element_blank()) +
    legend_top +
    labs(x = "Sessions", y = NULL)
}

table_options <- function(gt_table) {
  tab_options(gt_table, table.width = pct(100), table.font.size = px(14),
              data_row.padding = px(3), table.border.top.style = "none",
              column_labels.font.weight = "bold")
}
```

# Overview

```{r overview-summary}
#| include: false
# A year of whole weeks, or every week since tracking began if that is less.
year_from <- max(monday_of(through) - 51L * 7L, monday_of(tracking_from))
products <- c(signal_check = "Signal Checks", dashboard = "Dashboards",
              cookbook = "Metrics Cookbook")

weekly_all <- traffic |>
  dplyr::filter(page_kind %in% names(products), day >= year_from,
                day <= through) |>
  dplyr::mutate(week = monday_of(day)) |>
  dplyr::group_by(week, page_kind) |>
  dplyr::summarise(views = sum(views), .groups = "drop") |>
  tidyr::complete(week = seq(year_from, monday_of(through), by = "week"),
                  page_kind = names(products), fill = list(views = 0)) |>
  dplyr::mutate(product = factor(products[page_kind], levels = rev(products)),
                partial = week + 6L > through)

year_note <- glue(
  "Monday-to-Sunday weeks ",
  if (year_from > monday_of(tracking_from)) "over the last year" else
    "since tracking began on {format_long_date(tracking_from)}",
  ". The lighter bar is this week so far."
)
```

## Row {height="auto"}

::: {.card title="About this dashboard"}

This dashboard reports **how much attention our own analytics products
get**: Signal Check, the dashboards and the Metrics Cookbook. It does not
measure CanadaLogin. It shows who opens each product, how long they keep it
open, and which link brought them. It reads the analytics tag on our published
pages, the same kind of tag that measures CanadaLogin itself. It is internal to Enterprise
Digital Credentials and the link is unlisted. For anything that leaves EDCP,
please reach out to the
[Data and Research team](https://gcdigital.slack.com/archives/C0A6S9F7KV4).

**A red banner at the top of the page means a check failed at render time.**
Do not quote anything until it clears.

How long a page stays open is defined in the
[metrics cookbook](https://cds-snc.github.io/canadalogin-metrics-cookbook/cookbook/google_analytics/dwell-time.html).
This page is republished in place every week.

The **Signal Check** page follows each Signal Check over **its first 14
days**, the two weeks before the next one arrives, so every Signal Check is
measured over the same span. Views before a Signal Check is sent come from our
own review link and are left out of its first 14 days. The page shows views
each day, how long readers keep each Signal Check open, and which link started
each session.

The **Dashboards** page covers each published dashboard over the last three
months, and compares the last four weeks with the four before them.

The **Metrics Cookbook** page counts views of the Cookbook. The Cookbook does
not record how long a page stays open.

Volumes are small, a few dozen views per Signal Check, so one reader can move
a percentage a long way. Check the view counts before the percentages. A view
is one opening of a page, not one person: a reader who opens a Signal Check
twice counts twice.

:::

## Row {height="460px"}

::: {.card title="Views each week: Signal Checks, dashboards and the Cookbook"}

```{r overview-weeks-chart}
#| fig-width: 10
#| fig-height: 3.6
#| fig-alt: |
#|   Stacked bar chart of page views each week, split into Signal Checks,
#|   dashboards and the Metrics Cookbook, from the start of tracking or the
#|   last year, whichever is shorter. This week so far is lighter.
product_colours <- setNames(c(palette$accent, palette$ink, inks[[3]]),
                            unname(products))

p <- ggplot(weekly_all, aes(week + 3, views, fill = product)) +
  geom_col(aes(alpha = partial), width = 5.5) +
  scale_fill_manual(values = product_colours, breaks = unname(products),
                    name = NULL) +
  scale_alpha_manual(values = c(`FALSE` = 1, `TRUE` = 0.4), guide = "none") +
  week_axis(weekly_all$week) +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.08))) +
  theme_cds() +
  theme(panel.grid.minor = element_blank()) +
  legend_top +
  labs(x = "Week ending", y = "Views", subtitle = year_note)
brand_figure(p)
```

:::

# Signal Check

```{r signal-check-summary}
#| include: false
latest_age <- latest$days_seen - 1L
latest_views <- max(cumulative$cumulative[cumulative$number == latest$number])
typical_views <- typical_at_age(cumulative, complete, latest_age)

# Dwell over the latest edition's days so far, and every complete edition's
# over the same number of days.
dwell_so_far <- edition_dwell(events, dplyr::filter(editions, number %in%
                                                      c(latest$number,
                                                        complete$number)),
                              days = latest$days_seen)
latest_dwell <- dplyr::filter(dwell_so_far, number == latest$number)
typical_reading <- stats::median(
  dwell_so_far$reading_seconds[dwell_so_far$number %in% complete$number]
)

# The median dwell of every complete edition's views together.
pooled_median <- edition_window_events(
  events, dplyr::filter(editions, number %in% complete$number)
) |>
  dplyr::mutate(all = "all") |>
  dwell_curve("all") |>
  dplyr::summarise(m = median_read(seconds, share)) |>
  dplyr::pull(m)

so_far <- if (latest$days_seen < edition_window_days) {
  glue("first {latest$days_seen} {if (latest$days_seen == 1) 'day' else 'days'}")
} else {
  "first 14 days"
}

window_curve <- edition_window_events(
  events, dplyr::filter(editions, number %in% comparable$number)
) |>
  dwell_curve(c("number", "label")) |>
  dplyr::left_join(dplyr::select(coverage, number, published), by = "number") |>
  dplyr::mutate(panel = factor(
    paste0(label, ", ", format_short_date(published)),
    levels = paste0(comparable$label, ", ", format_short_date(comparable$published))
  ))
window_dwell <- edition_dwell(events, editions)

daily <- days |>
  dplyr::filter(day >= chart_from, day <= through)

window_sessions <- traffic |>
  dplyr::inner_join(dplyr::filter(coverage, comparable),
                    by = "pagepath_redacted") |>
  dplyr::filter(day >= published, day < published + edition_window_days)

# The share of first-14-day sessions started from the three announcement posts.
posts <- sum(window_sessions$sessions[
  source_group(window_sessions$sessionsource) %in% c("slack", "teams", "email")
]) / sum(window_sessions$sessions)

daily_alt <- glue(
  "Stacked bar chart of Signal Check views each day over the last three ",
  "months, one colour per Signal Check. Each Signal Check's views spike on ",
  "the day it is sent and trail off over the following weeks. ",
  "{latest$label} has {comma(latest_views)} views in its {so_far}."
)
```

## Row {height="150px"}

::: {.valuebox color="primary"}
`r latest$label` views, `r so_far`

`r nbsp(comma(latest_views))`

`r if (is.na(typical_views)) "No earlier Signal Check to compare" else glue("{fmt_delta(relative_change(latest_views, typical_views))} vs typical by day {latest$days_seen}")`
:::

::: {.valuebox color="info"}
`r latest$label` median read, `r so_far`

`r nbsp(fmt_read(latest_dwell$median_seconds))`

`r fmt_delta(relative_change(latest_dwell$median_seconds, pooled_median))` vs typical
:::

::: {.valuebox color="secondary"}
Total reading time, `r latest$label`

`r nbsp(fmt_reading(latest_dwell$reading_seconds))`

`r if (is.na(typical_reading)) "No earlier Signal Check to compare" else glue("{fmt_delta(relative_change(latest_dwell$reading_seconds, typical_reading))} vs typical by day {latest$days_seen}")`
:::

## Row {height="520px"}

::: {.card title="Signal Check views each day, last three months"}

```{r daily-chart}
#| fig-width: 10
#| fig-height: 3.7
#| fig-alt: !expr daily_alt
shown <- sort(unique(daily$number))
check_colours <- setNames(rep_len(inks, length(shown)), shown)
check_colours[as.character(latest$number)] <- palette$accent

# A tick on the Monday of each send week, even when a Signal Check went out
# later in the week.
send_mondays <- monday_of(coverage$published)
send_mondays <- send_mondays[send_mondays >= chart_from - 1L &
                               send_mondays <= through + 1L]

# Each Signal Check is named over its busiest day, leaning inward at the edges;
# one with under five views in the chart is left unnamed.
totals <- daily |>
  dplyr::group_by(day) |>
  dplyr::summarise(total = sum(views), .groups = "drop")
names_at <- daily |>
  dplyr::group_by(number, label) |>
  dplyr::filter(sum(views) >= 5) |>
  dplyr::slice_max(views, n = 1, with_ties = FALSE) |>
  dplyr::ungroup() |>
  dplyr::select(number, label, day) |>
  dplyr::left_join(totals, by = "day") |>
  dplyr::mutate(hjust = dplyr::case_when(day - chart_from < 6 ~ 0,
                                         through - day < 6 ~ 1,
                                         .default = 0.5))

p <- ggplot(daily, aes(day, views, fill = factor(number))) +
  geom_col(width = 0.85) +
  geom_text(data = names_at,
            aes(day, total, label = label, colour = factor(number),
                hjust = hjust),
            inherit.aes = FALSE, vjust = -0.6, size = 3, fontface = "bold") +
  scale_fill_manual(values = check_colours, guide = "none") +
  scale_colour_manual(values = check_colours, guide = "none") +
  scale_x_date(limits = c(chart_from - 1L, through + 1L), expand = c(0, 0),
               breaks = send_mondays,
               date_labels = "%b %d") +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.15))) +
  theme_cds() +
  theme(panel.grid.minor = element_blank()) +
  labs(x = NULL, y = "Views")
brand_figure(p)
```

:::

## Row {height="620px"}

::: {.card title="How long readers keep each Signal Check open, first 14 days"}

```{r edition-dwell-chart}
#| fig-width: 10
#| fig-height: 4.6
#| fig-alt: |
#|   Small multiples, one panel per Signal Check, each showing the share of
#|   its page views still open from 1 second to 10 minutes, with the other
#|   Signal Checks' curves behind it and a dashed line at 50 percent.
brand_figure(dwell_panels(window_curve, "panel", ncol = 3), height = 0.07)
```

::: {.figure-note}
Each curve is the share of page views that stayed open, and visible, at
least that long. The pale lines behind it are the other Signal Checks, for
comparison. Where it crosses the dashed line is the median read. A tab
in the background does not count. Most Signal Checks have a few dozen views, so
one reader can move a curve by several percentage points.
:::

:::

## Row {height="500px"}

::: {.card title="Where Signal Check sessions started, first 14 days"}

```{r edition-sources-chart}
#| fig-width: 10
#| fig-height: 3.2
#| fig-alt: |
#|   Horizontal stacked bars, one per Signal Check, newest at the top,
#|   splitting each Signal Check's sessions in its first 14 days by where
#|   they started: Slack, Teams, email, our own links, no link recorded and
#|   other sites. The total is at the end of each bar.
p <- source_bars(window_sessions, "label", rev(comparable$label))
brand_figure(p)
```

::: {.figure-note}
Every Signal Check goes out by Slack, Teams and email, each link tagged, so a
session that starts from one is counted under it. From
`r comparable$label[1]` onward, those three posts started
**`r percent(posts, accuracy = 1)`** of sessions in the first 14 days. *Our
own links* are the link to the latest Signal Check and links inside a Signal
Check or a dashboard. *No link recorded* is a bookmark, a typed address, or an
app that drops the link's source. A session counts once for each Signal Check
it opened.
:::

:::

## Row {height="auto"}

::: {.card title="Every Signal Check"}

```{r edition-table}
since <- days |>
  dplyr::filter(age >= 0) |>
  dplyr::group_by(number) |>
  dplyr::summarise(all_time = sum(views), .groups = "drop")
first_window <- cumulative |>
  dplyr::group_by(number) |>
  dplyr::summarise(first = max(cumulative), .groups = "drop")

coverage |>
  dplyr::left_join(first_window, by = "number") |>
  dplyr::left_join(dplyr::filter(window_dwell, number %in% comparable$number),
                   by = c("number", "label")) |>
  dplyr::left_join(since, by = "number") |>
  dplyr::arrange(dplyr::desc(published)) |>
  dplyr::transmute(
    label,
    sent = format_short_date(published),
    first = dplyr::case_when(
      !comparable ~ "Before tracking",
      days_seen < edition_window_days ~
        glue("{comma(first)} ({days_seen} of 14 days)"),
      .default = comma(first)
    ),
    median = ifelse(comparable, fmt_read(median_seconds), "-"),
    past_minute, past_five,
    reading = ifelse(comparable, fmt_reading(reading_seconds), "-"),
    all_time = dplyr::coalesce(all_time, 0)
  ) |>
  gt() |>
  fmt_percent(c(past_minute, past_five), decimals = 0) |>
  fmt_number(all_time, decimals = 0) |>
  sub_missing(missing_text = "-") |>
  cols_align("right", c(first, median, reading)) |>
  cols_label(label = "Signal Check", sent = "Sent", first = "Views, first 14 days",
             median = "Median read", past_minute = "Open 1 min+",
             past_five = "Open 5 min+", reading = "Total reading time",
             all_time = "Views since published") |>
  table_options()
```

::: {.figure-note}
Median read and the two *Open* columns cover the first 14 days. *Median read*
is the time half the views were still open, estimated between the two time
marks either side of it. *Total reading time* adds up the time of every view
by every reader, each counted down to the last milestone it reached, so it is
a floor. Tracking began July 23, 2026, after Signal Check #1 and Signal
Check #2 were sent.
:::

:::

# Dashboards

```{r dashboards-summary}
#| include: false
dashboard_rows <- traffic |>
  dplyr::filter(page_kind == "dashboard") |>
  dplyr::mutate(file = dashboard_file(pagepath_redacted)) |>
  dplyr::inner_join(dashboards, by = "file")

dashboard_recent <- dplyr::filter(dashboard_rows, day >= chart_from)

# Each dashboard in its own accent; one with no theme found falls back to ink.
accents <- dashboard_accent(dashboards$file)
accents <- setNames(dplyr::coalesce(accents, palette$ink), dashboards$name)

all_window <- window_totals(dashboard_rows, "views", through)
all_change <- relative_change(all_window[["current"]], all_window[["prior"]])

per_dashboard <- dashboard_rows |>
  dplyr::group_by(name) |>
  dplyr::group_modify(\(rows, key) {
    totals <- window_totals(rows, "views", through)
    tibble::tibble(current = totals[["current"]], prior = totals[["prior"]])
  }) |>
  dplyr::ungroup() |>
  dplyr::mutate(change = relative_change(current, prior))

dashboard_events <- events |>
  dplyr::filter(page_kind == "dashboard", day >= chart_from) |>
  dplyr::mutate(file = dashboard_file(pagepath_redacted)) |>
  dplyr::inner_join(dashboards, by = "file")
dashboard_curve <- dwell_curve(dashboard_events, "name")
dashboard_dwell <- dwell_summary(dashboard_curve, "name")

# Dwell over the last 4 weeks and the 4 before, all dashboards together.
window_dwell_dashboards <- events |>
  dplyr::filter(page_kind == "dashboard") |>
  dplyr::mutate(file = dashboard_file(pagepath_redacted),
                window = window_of(day, through)) |>
  dplyr::filter(file %in% dashboards$file, !is.na(window)) |>
  dwell_curve("window") |>
  dwell_summary("window")
window_median <- setNames(window_dwell_dashboards$median_seconds,
                          window_dwell_dashboards$window)[c("current", "prior")]
window_reading <- setNames(window_dwell_dashboards$reading_seconds,
                           window_dwell_dashboards$window)[c("current", "prior")]

weeks <- dashboard_recent |>
  dplyr::mutate(week = monday_of(day)) |>
  dplyr::group_by(name, week) |>
  dplyr::summarise(views = sum(views), .groups = "drop") |>
  tidyr::complete(name = dashboards$name,
                  week = seq(chart_from, monday_of(through), by = "week"),
                  fill = list(views = 0)) |>
  dplyr::mutate(partial = week + 6L > through)
```

## Row {height="150px"}

::: {.valuebox color="primary"}
Dashboard views, last 4 weeks

`r nbsp(comma(all_window[["current"]]))`

`r fmt_delta(all_change)` on the 4 weeks before
:::

::: {.valuebox color="info"}
Median read, last 4 weeks

`r nbsp(fmt_read(window_median[["current"]]))`

`r fmt_delta(relative_change(window_median[["current"]], window_median[["prior"]]))` on the 4 weeks before
:::

::: {.valuebox color="secondary"}
Total reading time, last 4 weeks

`r nbsp(fmt_reading(window_reading[["current"]]))`

`r fmt_delta(relative_change(window_reading[["current"]], window_reading[["prior"]]))` on the 4 weeks before
:::

## Row {height="460px"}

::: {.card title="Views each week, last three months"}

```{r dashboard-weeks-chart}
#| fig-width: 10
#| fig-height: 3.1
#| fig-alt: |
#|   Small multiples of weekly bar charts, one panel per dashboard, showing
#|   page views each Monday-to-Sunday week over the last three months, each in
#|   its dashboard's own colour. The newest week, not yet over, is lighter.
p <- ggplot(weeks, aes(week + 3, views)) +
  geom_col(aes(fill = name, alpha = partial), width = 5.5) +
  scale_fill_manual(values = accents, guide = "none") +
  scale_alpha_manual(values = c(`FALSE` = 1, `TRUE` = 0.35), guide = "none") +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.08))) +
  week_axis(weeks$week) +
  facet_wrap(~name, nrow = 1) +
  theme_cds() +
  theme(panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(face = "bold", hjust = 0, size = 11)) +
  labs(x = "Week ending", y = "Views",
       subtitle = "Weeks run Monday to Sunday. The lighter bar is this week so far.")
brand_figure(p)
```

:::

## Row {height="460px"}

::: {.card title="How long readers keep each dashboard open, last three months"}

```{r dashboard-dwell-chart}
#| fig-width: 10
#| fig-height: 3.1
#| fig-alt: |
#|   Small multiples, one panel per dashboard, each showing the share of its
#|   page views still open after 1 second up to 10 minutes in the dashboard's
#|   own colour, with the other dashboards' curves in the background and a
#|   dashed line at 50 percent.
brand_figure(dwell_panels(dashboard_curve, "name", ncol = nrow(dashboards),
                          colours = accents))
```

:::

## Row {height="400px"}

::: {.card title="Where dashboard sessions started, last three months"}

```{r dashboard-sources-chart}
#| fig-width: 10
#| fig-height: 2.7
#| fig-alt: |
#|   Horizontal stacked bars, one per dashboard, splitting its sessions over
#|   the last three months by where they started: Slack, Teams, email, our own
#|   links, no link recorded and other sites.
p <- source_bars(dashboard_recent, "name", sort(dashboards$name))
brand_figure(p, height = 0.11)
```

:::

## Row {height="auto"}

::: {.card title="Every dashboard"}

```{r dashboard-table}
per_dashboard |>
  dplyr::left_join(dashboard_dwell, by = "name") |>
  dplyr::left_join(dplyr::select(dashboards, name, first_seen), by = "name") |>
  dplyr::arrange(dplyr::desc(current)) |>
  dplyr::transmute(
    name, current, prior,
    direction = delta_direction(change), change = fmt_delta(change),
    median = fmt_read(median_seconds), past_minute, past_five,
    first_seen = format_short_date(first_seen)
  ) |>
  gt() |>
  fmt_number(c(current, prior), decimals = 0) |>
  fmt_percent(c(past_minute, past_five), decimals = 0) |>
  sub_missing(missing_text = "-") |>
  tab_style(cell_text(color = delta_colours[["up"]]),
            cells_body(change, rows = direction == "up")) |>
  tab_style(cell_text(color = delta_colours[["down"]]),
            cells_body(change, rows = direction == "down")) |>
  tab_style(cell_text(color = delta_colours[["flat"]]),
            cells_body(change, rows = direction == "flat")) |>
  cols_hide(direction) |>
  cols_align("right", c(change, median)) |>
  cols_label(name = "Dashboard", current = "Views, last 4 weeks",
             prior = "4 weeks before", change = "Change",
             median = "Median read", past_minute = "Open 1 min+",
             past_five = "Open 5 min+", first_seen = "First view") |>
  table_options()
```

::: {.figure-note}
Read times cover the last three months. Task Success Monitoring, Experience
Monitoring's earlier name, is counted as Experience Monitoring. This page
counts its own readers too.
:::

:::

# Metrics Cookbook

```{r cookbook-summary}
#| include: false
cookbook_colours <- c(Cookbook = inks[[1]], `Data catalog` = inks[[2]],
                      Other = inks[[6]])
cookbook <- traffic |>
  dplyr::filter(page_kind == "cookbook") |>
  dplyr::mutate(
    section = sub("^/canadalogin-metrics-cookbook/([^/]*).*$", "\\1",
                  pagepath_redacted),
    section = ifelse(grepl("\\.html$", section) | section == "", "home",
                     section),
    part = factor(dplyr::case_match(section, "cookbook" ~ "Cookbook",
                                    "catalog" ~ "Data catalog",
                                    .default = "Other"),
                  levels = names(cookbook_colours))
  )

cookbook_weeks <- cookbook |>
  dplyr::mutate(week = monday_of(day)) |>
  dplyr::group_by(week, part) |>
  dplyr::summarise(views = sum(views), .groups = "drop") |>
  tidyr::complete(week = seq(monday_of(tracking_from), monday_of(through),
                             by = "week"),
                  part, fill = list(views = 0)) |>
  dplyr::mutate(partial = week + 6L > through)

cookbook_pages <- cookbook |>
  dplyr::mutate(
    title = sub("\\s*\u2013 CanadaLogin Metrics Cookbook$", "", pagetitle),
    title = dplyr::case_when(
      section == "home" ~ "Front page",
      endsWith(pagepath_redacted, "/") ~ paste(tools::toTitleCase(section), "index"),
      .default = title
    )
  ) |>
  dplyr::group_by(pagepath_redacted) |>
  dplyr::summarise(title = dplyr::last(title), part = dplyr::first(part),
                   views = sum(views), .groups = "drop") |>
  dplyr::mutate(
    # Cut a long title at the last whole word that fits.
    page = ifelse(nchar(title) > 28,
                  paste0(sub("\\s+\\S*$", "", substr(title, 1, 28)), "..."),
                  title)
  ) |>
  dplyr::slice_max(views, n = 12, with_ties = FALSE)
```

## Row {height="520px"}

::: {.card title="Cookbook views each week, since tracking began"}

```{r cookbook-weeks-chart}
#| fig-width: 6.5
#| fig-height: 4.4
#| fig-alt: |
#|   Stacked bar chart of Metrics Cookbook page views each Monday-to-Sunday
#|   week since tracking began in July 2026, split into Cookbook, data catalog
#|   and other pages. This week so far is lighter.
p <- ggplot(cookbook_weeks, aes(week + 3, views, fill = part)) +
  geom_col(aes(alpha = partial), width = 5.5,
           position = position_stack(reverse = TRUE)) +
  scale_fill_manual(values = cookbook_colours, name = NULL) +
  scale_alpha_manual(values = c(`FALSE` = 1, `TRUE` = 0.4), guide = "none") +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.08))) +
  week_axis(cookbook_weeks$week) +
  theme_cds() +
  theme(panel.grid.minor = element_blank()) +
  legend_top +
  labs(x = "Week ending", y = "Views")
brand_figure(p)
```

:::

::: {.card title="Most viewed pages, since tracking began"}

```{r cookbook-pages-chart}
#| fig-width: 6.5
#| fig-height: 4.4
#| fig-alt: |
#|   Horizontal bar chart of the twelve most viewed Metrics Cookbook pages
#|   since tracking began, most viewed at the top, coloured as Cookbook, data
#|   catalog or other, each labelled with its views.
# Keyed on the path: a recipe and its catalog entry can share a title.
p <- ggplot(cookbook_pages,
            aes(views, stats::reorder(pagepath_redacted, views), fill = part)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = comma(views)), hjust = -0.3, size = 3.2,
            colour = "grey30") +
  scale_fill_manual(values = cookbook_colours, name = NULL, drop = FALSE) +
  scale_y_discrete(labels = setNames(cookbook_pages$page,
                                     cookbook_pages$pagepath_redacted)) +
  # Room on the right, so the longest bar and its label clear the logo.
  scale_x_continuous(expand = expansion(mult = c(0, 0.2))) +
  theme_cds() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank()) +
  legend_top +
  labs(x = "Views", y = NULL)
brand_figure(p)
```

:::

```{r cleanup}
#| include: false
# include: false matters for layout: this chunk sits in the last Row, where
# anything visible becomes a card and takes width from the chart.
DBI::dbDisconnect(con)
```

{{< include ../../_analytics.qmd >}}
