---
title: "CanadaLogin Readership"
author: "EDCP Data and Research Team"  # colin.douglas@cds-snc.ca
slug: readership
format:
  dashboard:
    # Written by the setup chunk at render time
    include-before-body: page-header.html
    include-after-body: analytics-tag.html # see _analytics.qmd
params:
  ga_page_title: "Readership Dashboard"
  # A saved snapshot to read instead of Athena, e.g. notes/snapshot.rds. The
  # live-data check fails on one, so the page carries the banner.
  snapshot: ""
---

```{r setup}
#| include: false

# The working directory is this folder; the shared layer is two levels up.
source("../../common/setup.R")

source("R/metrics.R")
source("R/preflight.R")

snapshot <- if (nzchar(params$snapshot)) params$snapshot else NULL
if (is.null(snapshot)) {
  con <- connect_athena()
} else {
  con <- NULL
  use_snapshot(snapshot)
}

# A failed check adds a banner. See R/preflight.R.
preflight <- run_preflight_safety_check(con, snapshot = snapshot)
write_preflight_status(preflight)

traffic <- page_traffic(con)
events <- page_events(con)

# The newest day exported. A day nobody read leaves no rows, so this comes
# from the export, not the meta tables.
through <- export_through(con)

editions <- edition_list(traffic)
coverage <- edition_coverage(editions, through)
days <- edition_days(traffic, editions)
cumulative <- cumulative_views(days, coverage)

# Editions with all of their first 14 days tracked, newest last, and the
# newest one with any days at all: the one in the value boxes.
comparable <- dplyr::filter(coverage, comparable, days_seen > 0)
latest <- dplyr::slice_tail(comparable, n = 1)
complete <- dplyr::filter(coverage, complete, number != latest$number)

dashboards <- dashboard_list(traffic)

page_header <- "page-header.html"

write_preflight_banner(preflight, page_header)

cat(
  c(
    '<div class="page-strip">',
    glue("  <p><strong>Data through {format_long_date(through)}.</strong> ",
         "Internal to Enterprise Digital Credentials, not for public ",
         "consumption.</p>"),
    "</div>"
  ),
  file = page_header, sep = "\n", append = TRUE
)

# Presentation ---------------------------------------------------------------

# Chart colours, mirroring _theme.scss ("Marginalia"): the margin's red marks
# the newest edition and our own links, sepia ink the rest of a series, and
# paper the context behind it.
palette <- list(accent = "#A63A26", ink = "#3B2A20", quiet = "#D6CBB9")

# Where a session started, in legend order. Our own links take the accent.
source_colours <- c(
  slack = unname(colors$brand["blue"]),
  teams = unname(colors$brand["green"]),
  email = unname(colors$brand["orange"]),
  our_links = palette$accent,
  direct = "#9AA3AB",
  other = "#D3D7DB"
)

brand_figure <- function(p, height = 0.09) {
  add_cds_logo(
    add_watermark(p, report_name = "CanadaLogin Readership", date = through),
    height = height
  )
}

dwell_breaks <- dwell_marks

# One panel per page: its drop-off curve in the accent, every other page's in
# the background, and a dashed line where half the views have left.
dwell_panels <- function(curve, panel, ncol) {
  curve <- dplyr::mutate(curve, panel = .data[[panel]])
  others <- curve |>
    dplyr::rename(other = panel) |>
    tidyr::crossing(panel = unique(curve$panel)) |>
    dplyr::filter(other != panel)
  counts <- curve |>
    dplyr::distinct(panel, page_views) |>
    dplyr::mutate(label = paste(comma(page_views), "views"))

  ggplot(curve, aes(seconds, share)) +
    geom_hline(yintercept = 0.5, linetype = "dashed", colour = "grey55",
               linewidth = 0.35) +
    geom_line(data = others, aes(group = other), colour = palette$quiet,
              linewidth = 0.5) +
    geom_line(colour = palette$accent, linewidth = 1) +
    geom_point(colour = palette$accent, size = 1.4) +
    geom_text(data = counts, aes(x = 600, y = 1, label = label),
              inherit.aes = FALSE, hjust = 1, vjust = 1, size = 3,
              colour = "grey35") +
    scale_x_log10(breaks = dwell_breaks, labels = fmt_mark_short(dwell_breaks)) +
    scale_y_continuous(labels = label_percent(), limits = c(0, 1),
                       breaks = c(0, 0.5, 1)) +
    facet_wrap(~panel, ncol = ncol) +
    theme_cds() +
    theme(panel.grid.minor = element_blank(),
          strip.background = element_blank(),
          strip.text = element_text(face = "bold", hjust = 0, size = 11)) +
    labs(x = "Time on the page, visible", y = "Page views still open")
}

# Sessions by where they started, one stacked bar per row of `group`, in the
# order of `levels` from the top.
source_bars <- function(rows, group, levels) {
  rows <- rows |>
    dplyr::mutate(row = factor(.data[[group]], levels = rev(levels)),
                  source = factor(source_group(sessionsource),
                                  levels = rev(source_groups$group))) |>
    dplyr::group_by(row, source) |>
    dplyr::summarise(sessions = sum(sessions), .groups = "drop")
  totals <- rows |>
    dplyr::group_by(row) |>
    dplyr::summarise(sessions = sum(sessions), .groups = "drop")

  ggplot(rows, aes(sessions, row)) +
    geom_col(aes(fill = source), width = 0.7) +
    geom_text(data = totals, aes(label = comma(sessions)), hjust = -0.3,
              size = 3.2, colour = "grey30") +
    scale_fill_manual(values = source_colours,
                      labels = setNames(source_groups$label, source_groups$group),
                      breaks = source_groups$group, name = NULL) +
    scale_x_continuous(expand = expansion(mult = c(0, 0.08))) +
    guides(fill = guide_legend(nrow = 1)) +
    theme_cds() +
    theme(panel.grid.minor = element_blank(),
          panel.grid.major.y = element_blank(),
          legend.position = "top", legend.justification = "left",
          legend.key.size = unit(0.35, "cm"),
          legend.text = element_text(margin = margin(r = 12)),
          legend.margin = margin(0, 0, 0, 0)) +
    labs(x = "Sessions", y = NULL)
}

table_options <- function(gt_table) {
  tab_options(gt_table, table.width = pct(100), table.font.size = px(14),
              data_row.padding = px(3), table.border.top.style = "none")
}
```

# Signal Check

```{r signal-check-summary}
#| include: false
latest_age <- latest$days_seen - 1L
latest_views <- max(cumulative$cumulative[cumulative$number == latest$number])
typical_views <- typical_at_age(cumulative, complete, latest_age)

# Dwell over the latest edition's days so far, and every complete edition's
# over the same number of days.
dwell_so_far <- edition_dwell(events, dplyr::filter(editions, number %in%
                                                      c(latest$number,
                                                        complete$number)),
                              days = latest$days_seen)
latest_dwell <- dplyr::filter(dwell_so_far, number == latest$number)
typical_reading <- stats::median(
  dwell_so_far$reading_seconds[dwell_so_far$number %in% complete$number]
)

# The median dwell of every complete edition's views together.
pooled_median <- edition_window_events(
  events, dplyr::filter(editions, number %in% complete$number)
) |>
  dplyr::mutate(all = "all") |>
  dwell_curve("all") |>
  dplyr::summarise(m = median_dwell(seconds, share)) |>
  dplyr::pull(m)

so_far <- if (latest$days_seen < edition_window_days) {
  glue("first {latest$days_seen} {if (latest$days_seen == 1) 'day' else 'days'}")
} else {
  "first 14 days"
}

window_curve <- edition_window_events(
  events, dplyr::filter(editions, number %in% comparable$number)
) |>
  dwell_curve(c("number", "label")) |>
  dplyr::left_join(dplyr::select(coverage, number, published), by = "number") |>
  dplyr::mutate(panel = factor(
    paste0(label, ", ", format_short_date(published)),
    levels = paste0(comparable$label, ", ", format_short_date(comparable$published))
  ))
window_dwell <- edition_dwell(events, editions)

cumulative_alt <- glue(
  "Line chart of each edition's views, added up day by day over its first ",
  "14 days, for editions {comparable$label[1]} to {latest$label}. Most of ",
  "each edition's views come on the day it is sent and the day after, then ",
  "the lines flatten. {latest$label} has {comma(latest_views)} views in its ",
  "{so_far}."
)
```

## Row {height="auto"}

::: {.card title="Reading this dashboard"}

This dashboard shows how much attention our own reporting gets: who opens
each Signal Check edition and dashboard, how long they keep it open, and which
link brought them. It reads the analytics tag on our pages, the same kind of
tag that measures CanadaLogin itself. It is internal to Enterprise Digital
Credentials and the link is unlisted.

Editions are compared over **their first 14 days**, the fortnight before the
next one arrives, so every edition is measured over the same span.
Views before an edition is sent are our own review, and are left out.

:::

## Row {height="150px"}

::: {.valuebox color="primary"}
`r latest$label` views, `r so_far`

`r nbsp(comma(latest_views))`

`r if (is.na(typical_views)) "No earlier edition to compare" else glue("{comma(typical_views)} for a typical edition by day {latest$days_seen}")`
:::

::: {.valuebox color="info"}
`r latest$label` median read, `r so_far`

`r nbsp(fmt_dwell(latest_dwell$median_seconds))`

`r glue("{fmt_dwell(pooled_median)} across earlier editions")`
:::

::: {.valuebox color="secondary"}
Time spent reading `r latest$label`, at least

`r nbsp(fmt_reading(latest_dwell$reading_seconds))`

`r if (is.na(typical_reading)) "No earlier edition to compare" else glue("{fmt_reading(typical_reading)} for a typical edition by day {latest$days_seen}")`
:::

## Row {height="520px"}

::: {.card title="Views in each edition's first 14 days, added up day by day"}

```{r cumulative-chart}
#| fig-width: 10
#| fig-height: 3.7
#| fig-alt: !expr cumulative_alt
lines <- dplyr::mutate(cumulative, newest = number == latest$number)
ends <- lines |>
  dplyr::group_by(number) |>
  dplyr::filter(age == max(age)) |>
  dplyr::ungroup()
# Labels of editions that ended on the same day can collide.
ends <- ends |>
  dplyr::group_by(age) |>
  dplyr::mutate(label_y = spread_labels(cumulative,
                                        0.045 * max(lines$cumulative))) |>
  dplyr::ungroup()

p <- ggplot(lines, aes(age, cumulative, group = number)) +
  geom_step(data = dplyr::filter(lines, !newest), colour = palette$ink,
            linewidth = 0.6, alpha = 0.55, direction = "hv") +
  geom_step(data = dplyr::filter(lines, newest), colour = palette$accent,
            linewidth = 1.3, direction = "hv") +
  geom_point(data = ends, aes(colour = newest), size = 2) +
  geom_text(data = ends, aes(y = label_y, label = label, colour = newest),
            hjust = -0.35, fontface = "bold", size = 3.4) +
  scale_colour_manual(values = c(`TRUE` = palette$accent, `FALSE` = palette$ink),
                      guide = "none") +
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10, 13),
                     labels = \(x) ifelse(x == 0, "Day sent", paste("Day", x + 1)),
                     limits = c(0, 13.6), expand = expansion(mult = c(0.01, 0))) +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.08))) +
  theme_cds() +
  theme(panel.grid.minor = element_blank()) +
  labs(x = NULL, y = "Views so far",
       subtitle = glue("{latest$label} in colour. Editions {comparable$label[1]} ",
                       "onward: earlier ones were sent before tracking began."))
brand_figure(p)
```

:::

## Row {height="620px"}

::: {.card title="How long readers keep each edition open, first 14 days"}

```{r edition-dwell-chart}
#| fig-width: 10
#| fig-height: 4.6
#| fig-alt: |
#|   Small multiples, one panel per Signal Check edition. Each shows the share
#|   of the edition's page views still open after 1 second, 5, 15 and 30
#|   seconds, and 1, 2, 5 and 10 minutes, with every other edition's curve in
#|   the background and a dashed line at 50 percent.
brand_figure(dwell_panels(window_curve, "panel", ncol = 3), height = 0.07)
```

::: {.figure-note}
Each curve is the share of page views that stayed open, and visible, at
least that long. Where it crosses the dashed line is the median read. A tab
in the background does not count. Most editions have a few dozen views, so
one reader can move a curve by several percentage points.
:::

:::

## Row {height="auto"}

::: {.card title="Every edition"}

```{r edition-table}
review <- days |>
  dplyr::filter(age < 0) |>
  dplyr::group_by(number) |>
  dplyr::summarise(review = sum(views), .groups = "drop")
since <- days |>
  dplyr::filter(age >= 0) |>
  dplyr::group_by(number) |>
  dplyr::summarise(all_time = sum(views), .groups = "drop")
first_window <- cumulative |>
  dplyr::group_by(number) |>
  dplyr::summarise(first = max(cumulative), .groups = "drop")

coverage |>
  dplyr::left_join(first_window, by = "number") |>
  dplyr::left_join(dplyr::filter(window_dwell, number %in% comparable$number),
                   by = c("number", "label")) |>
  dplyr::left_join(since, by = "number") |>
  dplyr::left_join(review, by = "number") |>
  dplyr::arrange(dplyr::desc(published)) |>
  dplyr::transmute(
    label,
    sent = format_short_date(published),
    first = dplyr::case_when(
      !comparable ~ "Before tracking",
      days_seen < edition_window_days ~
        glue("{comma(first)} ({days_seen} of 14 days)"),
      .default = comma(first)
    ),
    median = ifelse(comparable, fmt_dwell(median_seconds), "-"),
    past_minute, past_five,
    reading = ifelse(comparable, fmt_reading(reading_seconds), "-"),
    all_time = dplyr::coalesce(all_time, 0),
    review = dplyr::coalesce(review, 0)
  ) |>
  gt() |>
  fmt_percent(c(past_minute, past_five), decimals = 0) |>
  fmt_number(c(all_time, review), decimals = 0) |>
  sub_missing(missing_text = "-") |>
  cols_align("right", c(first, median, reading)) |>
  cols_label(label = "Edition", sent = "Sent", first = "Views, first 14 days",
             median = "Median read", past_minute = "Open 1 min+",
             past_five = "Open 5 min+", reading = "Reading time, at least",
             all_time = "Views since sent", review = "Review views") |>
  table_options()
```

::: {.figure-note}
Median read and the two *Open* columns cover the first 14 days. *Reading time*
adds up each view's time, counted down to the last milestone it reached, so
it is a floor. *Review views* came before the edition was sent, from our own
review link, and count nowhere else. Tracking began July 23, 2026, after
editions #1 and #2 were sent.
:::

:::

# Where readers come from

```{r sources-summary}
#| include: false
window_sessions <- traffic |>
  dplyr::inner_join(dplyr::filter(coverage, comparable),
                    by = "pagepath_redacted") |>
  dplyr::filter(day >= published, day < published + edition_window_days)

source_table <- window_sessions |>
  dplyr::group_by(sessionsource) |>
  dplyr::summarise(sessions = sum(sessions), .groups = "drop") |>
  dplyr::mutate(
    what = describe_source(sessionsource),
    group = source_groups$label[match(source_group(sessionsource),
                                      source_groups$group)],
    share = sessions / sum(sessions)
  ) |>
  dplyr::group_by(what, group) |>
  dplyr::summarise(sources = paste(sort(unique(sessionsource)), collapse = ", "),
                   sessions = sum(sessions), share = sum(share),
                   .groups = "drop") |>
  dplyr::arrange(dplyr::desc(sessions))

posts <- sum(source_table$share[source_table$group %in%
                                  c("Slack", "Teams", "Email")])

chart_from <- monday_of(through) - 12L * 7L
dashboard_sessions <- traffic |>
  dplyr::filter(page_kind == "dashboard", day >= chart_from) |>
  dplyr::mutate(file = dashboard_file(pagepath_redacted)) |>
  dplyr::inner_join(dashboards, by = "file")
```

## Row {height="auto"}

::: {.card title="How readers reach Signal Check"}

Every edition goes out by Slack, Teams and email, and each of those links
is tagged, so a session that starts from one is counted under it. *Our own
links* are the link to the latest edition and links inside an edition or a
dashboard. *No link recorded* is a bookmark, a typed address, or an app that
drops the link's source. In editions `r comparable$label[1]` onward, the
three posts started **`r percent(posts, accuracy = 1)`** of sessions in the
first 14 days.

:::

## Row {height="460px"}

::: {.card title="Signal Check sessions by where they started, first 14 days"}

```{r edition-sources-chart}
#| fig-width: 10
#| fig-height: 3.2
#| fig-alt: |
#|   Horizontal stacked bars, one per Signal Check edition, newest at the
#|   top, splitting each edition's sessions in its first 14 days by where
#|   they started: Slack, Teams, email, our own links, no link recorded and
#|   other sites. The total is at the end of each bar.
p <- source_bars(window_sessions, "label", rev(comparable$label))
brand_figure(p)
```

::: {.figure-note}
A session counts once for each edition it opened, and starts from one place.
:::

:::

## Row {height="auto"}

::: {.card title="Every source, editions `r comparable$label[1]` to `r latest$label`, first 14 days"}

```{r source-table}
source_table |>
  dplyr::select(what, sources, group, sessions, share) |>
  gt() |>
  fmt_number(sessions, decimals = 0) |>
  fmt_percent(share, decimals = 0) |>
  cols_label(what = "Where", sources = "Recorded as", group = "Grouped as",
             sessions = "Sessions", share = "Share") |>
  table_options()
```

:::

## Row {height="400px"}

::: {.card title="Dashboard sessions by where they started, last three months"}

```{r dashboard-sources-chart}
#| fig-width: 10
#| fig-height: 2.7
#| fig-alt: |
#|   Horizontal stacked bars, one per dashboard, splitting its sessions over
#|   the last three months by where they started: Slack, Teams, email, our own
#|   links, no link recorded and other sites.
p <- source_bars(dashboard_sessions, "name", sort(dashboards$name))
brand_figure(p, height = 0.11)
```

:::

# Dashboards

```{r dashboards-summary}
#| include: false
dashboard_rows <- traffic |>
  dplyr::filter(page_kind == "dashboard") |>
  dplyr::mutate(file = dashboard_file(pagepath_redacted)) |>
  dplyr::inner_join(dashboards, by = "file")

all_window <- window_totals(dashboard_rows, "views", through)
all_change <- relative_change(all_window[["current"]], all_window[["prior"]])

per_dashboard <- dashboard_rows |>
  dplyr::group_by(name) |>
  dplyr::group_modify(\(rows, key) {
    totals <- window_totals(rows, "views", through)
    tibble::tibble(current = totals[["current"]], prior = totals[["prior"]])
  }) |>
  dplyr::ungroup() |>
  dplyr::mutate(change = relative_change(current, prior))
top <- dplyr::slice_max(per_dashboard, current, n = 1, with_ties = FALSE)

dashboard_events <- events |>
  dplyr::filter(page_kind == "dashboard", day >= chart_from) |>
  dplyr::mutate(file = dashboard_file(pagepath_redacted)) |>
  dplyr::inner_join(dashboards, by = "file")
dashboard_curve <- dwell_curve(dashboard_events, "name")
dashboard_dwell <- dwell_summary(dashboard_curve, "name")

pooled_dashboard_median <- dashboard_events |>
  dplyr::mutate(all = "all") |>
  dwell_curve("all") |>
  dplyr::summarise(m = median_dwell(seconds, share)) |>
  dplyr::pull(m)

weeks <- dashboard_rows |>
  dplyr::filter(day >= chart_from) |>
  dplyr::mutate(week = monday_of(day)) |>
  dplyr::group_by(name, week) |>
  dplyr::summarise(views = sum(views), .groups = "drop") |>
  tidyr::complete(name = dashboards$name,
                  week = seq(chart_from, monday_of(through), by = "week"),
                  fill = list(views = 0)) |>
  dplyr::mutate(partial = week + 6L > through)
```

## Row {height="150px"}

::: {.valuebox color="primary"}
Dashboard views, last 4 weeks

`r nbsp(comma(all_window[["current"]]))`

`r fmt_delta(all_change)` on the 4 weeks before
:::

::: {.valuebox color="info"}
Most viewed, last 4 weeks

`r nbsp(top$name)`

`r glue("{comma(top$current)} views")`
:::

::: {.valuebox color="secondary"}
Median read, last three months

`r nbsp(fmt_dwell(pooled_dashboard_median))`

All dashboards together
:::

## Row {height="460px"}

::: {.card title="Views each week, last three months"}

```{r dashboard-weeks-chart}
#| fig-width: 10
#| fig-height: 3.1
#| fig-alt: |
#|   Small multiples of weekly bar charts, one panel per dashboard, showing
#|   page views each Monday-to-Sunday week over the last three months. The newest
#|   week, not yet over, is lighter.
p <- ggplot(weeks, aes(week + 3, views)) +
  geom_col(aes(fill = partial), width = 5.5) +
  scale_fill_manual(values = c(`FALSE` = palette$accent, `TRUE` = palette$quiet),
                    guide = "none") +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.08))) +
  scale_x_date(date_labels = "%b %d",
               breaks = rev(seq(monday_of(through), chart_from, by = "-4 weeks"))) +
  facet_wrap(~name, nrow = 1) +
  theme_cds() +
  theme(panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(face = "bold", hjust = 0, size = 11)) +
  labs(x = NULL, y = "Views",
       subtitle = "Weeks run Monday to Sunday. The lighter bar is this week so far.")
brand_figure(p)
```

:::

## Row {height="460px"}

::: {.card title="How long readers keep each dashboard open, last three months"}

```{r dashboard-dwell-chart}
#| fig-width: 10
#| fig-height: 3.1
#| fig-alt: |
#|   Small multiples, one panel per dashboard, each showing the share of its
#|   page views still open after 1 second up to 10 minutes, with the other
#|   dashboards' curves in the background and a dashed line at 50 percent.
brand_figure(dwell_panels(dashboard_curve, "name", ncol = nrow(dashboards)))
```

:::

## Row {height="auto"}

::: {.card title="Every dashboard"}

```{r dashboard-table}
per_dashboard |>
  dplyr::left_join(dashboard_dwell, by = "name") |>
  dplyr::left_join(dplyr::select(dashboards, name, first_seen), by = "name") |>
  dplyr::arrange(dplyr::desc(current)) |>
  dplyr::transmute(
    name, current, prior,
    direction = delta_direction(change), change = fmt_delta(change),
    median = fmt_dwell(median_seconds), past_minute, past_five,
    first_seen = format_short_date(first_seen)
  ) |>
  gt() |>
  fmt_number(c(current, prior), decimals = 0) |>
  fmt_percent(c(past_minute, past_five), decimals = 0) |>
  sub_missing(missing_text = "-") |>
  tab_style(cell_text(color = delta_colours[["up"]]),
            cells_body(change, rows = direction == "up")) |>
  tab_style(cell_text(color = delta_colours[["down"]]),
            cells_body(change, rows = direction == "down")) |>
  tab_style(cell_text(color = delta_colours[["flat"]]),
            cells_body(change, rows = direction == "flat")) |>
  cols_hide(direction) |>
  cols_align("right", c(change, median)) |>
  cols_label(name = "Dashboard", current = "Views, last 4 weeks",
             prior = "4 weeks before", change = "Change",
             median = "Median read", past_minute = "Open 1 min+",
             past_five = "Open 5 min+", first_seen = "First view") |>
  table_options()
```

::: {.figure-note}
Read times cover the last three months. Task Success Monitoring, Experience
Monitoring's earlier name, is counted as Experience Monitoring. This page
counts its own readers too.
:::

:::

# Metrics Cookbook

```{r cookbook-summary}
#| include: false
cookbook <- dplyr::filter(traffic, page_kind == "cookbook")
previews <- sum(traffic$views[traffic$page_kind == "preview"])

cookbook_weeks <- cookbook |>
  dplyr::mutate(week = monday_of(day)) |>
  dplyr::group_by(week) |>
  dplyr::summarise(views = sum(views), .groups = "drop") |>
  tidyr::complete(week = seq(monday_of(tracking_from), monday_of(through),
                             by = "week"),
                  fill = list(views = 0)) |>
  dplyr::mutate(partial = week + 6L > through)

# Two pages share a title (a recipe and its table), so the section names them.
cookbook_pages <- cookbook |>
  dplyr::mutate(
    section = sub("^/canadalogin-metrics-cookbook/([^/]*).*$", "\\1",
                  pagepath_redacted),
    section = ifelse(grepl("\\.html$", section) | section == "", "home",
                     section),
    title = sub("\\s*\u2013 CanadaLogin Metrics Cookbook$", "", pagetitle),
    title = dplyr::case_when(
      section == "home" ~ "Front page",
      endsWith(pagepath_redacted, "/") ~ paste(tools::toTitleCase(section), "index"),
      .default = title
    )
  ) |>
  dplyr::group_by(pagepath_redacted) |>
  dplyr::summarise(title = dplyr::last(title), section = dplyr::first(section),
                   views = sum(views), .groups = "drop") |>
  dplyr::mutate(page = ifelse(section == "home" | grepl(" index$", title),
                              title, glue("{title} ({section})"))) |>
  dplyr::slice_max(views, n = 12, with_ties = FALSE)
```

## Row {height="380px"}

::: {.card title="Cookbook views each week, since tracking began"}

```{r cookbook-weeks-chart}
#| fig-width: 10
#| fig-height: 2.6
#| fig-alt: |
#|   Bar chart of Metrics Cookbook page views each Monday-to-Sunday week since
#|   tracking began in July 2026. The newest week, not yet over, is lighter.
p <- ggplot(cookbook_weeks, aes(week + 3, views)) +
  geom_col(aes(fill = partial), width = 5.5) +
  scale_fill_manual(values = c(`FALSE` = palette$ink, `TRUE` = palette$quiet),
                    guide = "none") +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.08))) +
  scale_x_date(date_labels = "%b %d") +
  theme_cds() +
  theme(panel.grid.minor = element_blank()) +
  labs(x = NULL, y = "Views")
brand_figure(p, height = 0.12)
```

::: {.figure-note}
Previews of changes under review are left out: `r comma(previews)` views, all
ours. The Cookbook does not track how long a page stays open.
:::

:::

## Row {height="480px"}

::: {.card title="Most viewed pages, since tracking began"}

```{r cookbook-pages-chart}
#| fig-width: 10
#| fig-height: 3.5
#| fig-alt: |
#|   Horizontal bar chart of the twelve most viewed Metrics Cookbook pages
#|   since tracking began, most viewed at the top, each bar labelled with its
#|   views.
p <- ggplot(cookbook_pages, aes(views, stats::reorder(page, views))) +
  geom_col(fill = palette$ink, width = 0.7) +
  geom_text(aes(label = comma(views)), hjust = -0.3, size = 3.2,
            colour = "grey30") +
  scale_x_continuous(expand = expansion(mult = c(0, 0.08))) +
  theme_cds() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank()) +
  labs(x = "Views", y = NULL)
brand_figure(p)
```

:::

```{r cleanup}
#| include: false
# include: false matters for layout: this chunk sits in the last Row, where
# anything visible becomes a card and takes width from the chart.
if (!is.null(con)) DBI::dbDisconnect(con)
```

{{< include ../../_analytics.qmd >}}
