---
title: "CanadaLogin Readership"
author: "EDCP Data and Research Team"  # colin.douglas@cds-snc.ca
slug: readership
format:
  dashboard:
    # Written by the setup chunk at render time
    include-before-body: page-header.html
    include-after-body: analytics-tag.html # see _analytics.qmd
params:
  ga_page_title: "Readership Dashboard"
  # A saved snapshot to read instead of Athena, e.g. notes/snapshot.rds. The
  # live-data check fails on one, so the page carries the banner.
  snapshot: ""
---

```{r setup}
#| include: false

# The working directory is this folder; the shared layer is two levels up.
source("../../common/setup.R")

source("R/metrics.R")
source("R/preflight.R")

snapshot <- if (nzchar(params$snapshot)) params$snapshot else NULL
if (is.null(snapshot)) {
  con <- connect_athena()
} else {
  con <- NULL
  use_snapshot(snapshot)
}

# A failed check adds a banner. See R/preflight.R.
preflight <- run_preflight_safety_check(con, snapshot = snapshot)
write_preflight_status(preflight)

traffic <- page_traffic(con)
events <- page_events(con)

# The newest day exported. A day nobody read leaves no rows, so this comes
# from the export, not the meta tables.
through <- export_through(con)

editions <- edition_list(traffic)
coverage <- edition_coverage(editions, through)
days <- edition_days(traffic, editions)
cumulative <- cumulative_views(days, coverage)

# Editions with all of their first 14 days tracked, newest last, and the
# newest one with any days at all: the one in the value boxes.
comparable <- dplyr::filter(coverage, comparable, days_seen > 0)
latest <- dplyr::slice_tail(comparable, n = 1)
complete <- dplyr::filter(coverage, complete, number != latest$number)

dashboards <- dashboard_list(traffic)

# Three months, as whole Monday-to-Sunday weeks, for every daily or weekly
# chart.
chart_from <- monday_of(through) - 12L * 7L

page_header <- "page-header.html"

write_preflight_banner(preflight, page_header)

cat(
  c(
    '<div class="page-strip">',
    glue("  <p><strong>Data through {format_long_date(through)}.</strong> ",
         "Internal to Enterprise Digital Credentials, not for public ",
         "consumption.</p>"),
    "</div>"
  ),
  file = page_header, sep = "\n", append = TRUE
)

# Presentation ---------------------------------------------------------------

# Chart colours from _theme.scss: margin red for the newest Signal Check and
# our own links, sepia ink for the rest, paper behind.
palette <- list(accent = "#A63A26", ink = "#3B2A20", quiet = "#D6CBB9")

# One ink per Signal Check in the daily chart, cycled oldest first so
# neighbours differ; the newest takes the margin red.
inks <- c("#3B2A20", "#2F4E7A", "#B98A2E", "#4E6E3A", "#6E4A7E", "#7C8791")

# Where a session started, in legend order. Our own links take the accent.
source_colours <- c(
  slack = unname(colors$brand["blue"]),
  teams = unname(colors$brand["green"]),
  email = unname(colors$brand["orange"]),
  our_links = palette$accent,
  direct = "#9AA3AB",
  other = "#D3D7DB"
)

brand_figure <- function(p, height = 0.09) {
  add_cds_logo(
    add_watermark(p, report_name = "CanadaLogin Readership", date = through),
    height = height
  )
}

dwell_breaks <- dwell_marks

# One panel per page: its curve in the accent over every other page's, a
# dashed line at half, and its views and median read in the corner.
dwell_panels <- function(curve, panel, ncol) {
  curve <- dplyr::mutate(curve, panel = .data[[panel]])
  others <- curve |>
    dplyr::rename(other = panel) |>
    tidyr::crossing(panel = unique(curve$panel)) |>
    dplyr::filter(other != panel)
  counts <- curve |>
    dplyr::group_by(panel) |>
    dplyr::summarise(
      label = paste0(comma(dplyr::first(page_views)), " views\n",
                     "median ", fmt_read(median_read(seconds, share))),
      .groups = "drop"
    )

  ggplot(curve, aes(seconds, share)) +
    geom_hline(yintercept = 0.5, linetype = "dashed", colour = "grey55",
               linewidth = 0.35) +
    geom_line(data = others, aes(group = other), colour = palette$quiet,
              linewidth = 0.5) +
    geom_line(colour = palette$accent, linewidth = 1) +
    geom_point(colour = palette$accent, size = 1.4) +
    geom_text(data = counts, aes(x = 600, y = 1, label = label),
              inherit.aes = FALSE, hjust = 1, vjust = 1, size = 3,
              lineheight = 0.9, colour = "grey35") +
    scale_x_log10(breaks = dwell_breaks, labels = fmt_mark_short(dwell_breaks)) +
    scale_y_continuous(labels = label_percent(), limits = c(0, 1),
                       breaks = c(0, 0.5, 1)) +
    facet_wrap(~panel, ncol = ncol) +
    theme_cds() +
    theme(panel.grid.minor = element_blank(),
          strip.background = element_blank(),
          strip.text = element_text(face = "bold", hjust = 0, size = 11)) +
    labs(x = "Time on the page, visible", y = "Page views still open")
}

# Sessions by where they started, one stacked bar per row of `group`, in the
# order of `levels` from the top.
source_bars <- function(rows, group, levels) {
  rows <- rows |>
    dplyr::mutate(row = factor(.data[[group]], levels = rev(levels)),
                  source = factor(source_group(sessionsource),
                                  levels = rev(source_groups$group))) |>
    dplyr::group_by(row, source) |>
    dplyr::summarise(sessions = sum(sessions), .groups = "drop")
  totals <- rows |>
    dplyr::group_by(row) |>
    dplyr::summarise(sessions = sum(sessions), .groups = "drop")

  ggplot(rows, aes(sessions, row)) +
    geom_col(aes(fill = source), width = 0.7) +
    geom_text(data = totals, aes(label = comma(sessions)), hjust = -0.3,
              size = 3.2, colour = "grey30") +
    scale_fill_manual(values = source_colours,
                      labels = setNames(source_groups$label, source_groups$group),
                      breaks = source_groups$group, name = NULL) +
    scale_x_continuous(expand = expansion(mult = c(0, 0.08))) +
    guides(fill = guide_legend(nrow = 1)) +
    theme_cds() +
    theme(panel.grid.minor = element_blank(),
          panel.grid.major.y = element_blank(),
          legend.position = "top", legend.justification = "left",
          legend.key.size = unit(0.35, "cm"),
          legend.text = element_text(margin = margin(r = 12)),
          legend.margin = margin(0, 0, 0, 0)) +
    labs(x = "Sessions", y = NULL)
}

table_options <- function(gt_table) {
  tab_options(gt_table, table.width = pct(100), table.font.size = px(14),
              data_row.padding = px(3), table.border.top.style = "none")
}
```

# Signal Check

```{r signal-check-summary}
#| include: false
latest_age <- latest$days_seen - 1L
latest_views <- max(cumulative$cumulative[cumulative$number == latest$number])
typical_views <- typical_at_age(cumulative, complete, latest_age)

# Dwell over the latest edition's days so far, and every complete edition's
# over the same number of days.
dwell_so_far <- edition_dwell(events, dplyr::filter(editions, number %in%
                                                      c(latest$number,
                                                        complete$number)),
                              days = latest$days_seen)
latest_dwell <- dplyr::filter(dwell_so_far, number == latest$number)
typical_reading <- stats::median(
  dwell_so_far$reading_seconds[dwell_so_far$number %in% complete$number]
)

# The median dwell of every complete edition's views together.
pooled_median <- edition_window_events(
  events, dplyr::filter(editions, number %in% complete$number)
) |>
  dplyr::mutate(all = "all") |>
  dwell_curve("all") |>
  dplyr::summarise(m = median_read(seconds, share)) |>
  dplyr::pull(m)

so_far <- if (latest$days_seen < edition_window_days) {
  glue("first {latest$days_seen} {if (latest$days_seen == 1) 'day' else 'days'}")
} else {
  "first 14 days"
}

window_curve <- edition_window_events(
  events, dplyr::filter(editions, number %in% comparable$number)
) |>
  dwell_curve(c("number", "label")) |>
  dplyr::left_join(dplyr::select(coverage, number, published), by = "number") |>
  dplyr::mutate(panel = factor(
    paste0(label, ", ", format_short_date(published)),
    levels = paste0(comparable$label, ", ", format_short_date(comparable$published))
  ))
window_dwell <- edition_dwell(events, editions)

daily <- days |>
  dplyr::filter(age >= 0, day >= chart_from, day <= through)

daily_alt <- glue(
  "Stacked bar chart of Signal Check views each day over the last three ",
  "months, one colour per Signal Check. Each Signal Check's views spike on ",
  "the day it is sent and trail off over the following weeks. ",
  "{latest$label} has {comma(latest_views)} views in its {so_far}."
)
```

## Row {height="auto"}

::: {.card title="Reading this dashboard"}

This dashboard shows how much attention our own reporting gets: who opens
each Signal Check and dashboard, how long they keep it open, and which
link brought them. It reads the analytics tag on our pages, the same kind of
tag that measures CanadaLogin itself. It is internal to Enterprise Digital
Credentials and the link is unlisted.

Signal Checks are compared over **their first 14 days**, the two weeks before
the next one arrives, so every Signal Check is measured over the same span.
Views before a Signal Check is sent are our own review, and are left out.

:::

## Row {height="150px"}

::: {.valuebox color="primary"}
`r latest$label` views, `r so_far`

`r nbsp(comma(latest_views))`

`r if (is.na(typical_views)) "No earlier Signal Check to compare" else glue("{comma(typical_views)} for a typical Signal Check by day {latest$days_seen}")`
:::

::: {.valuebox color="info"}
`r latest$label` median read, `r so_far`

`r nbsp(fmt_read(latest_dwell$median_seconds))`

`r glue("{fmt_read(pooled_median)} across earlier Signal Checks")`
:::

::: {.valuebox color="secondary"}
Total reading time, `r latest$label`

`r nbsp(fmt_reading(latest_dwell$reading_seconds))`

`r if (is.na(typical_reading)) "No earlier Signal Check to compare" else glue("{fmt_reading(typical_reading)} for a typical Signal Check by day {latest$days_seen}")`
:::

## Row {height="520px"}

::: {.card title="Signal Check views each day, last three months"}

```{r daily-chart}
#| fig-width: 10
#| fig-height: 3.7
#| fig-alt: !expr daily_alt
shown <- sort(unique(daily$number))
check_colours <- setNames(rep_len(inks, length(shown)), shown)
check_colours[as.character(latest$number)] <- palette$accent

# Each Signal Check is named over its busiest day, the day it was sent unless
# that was before the chart; at the edges the label leans inward. One with
# only a few views here is left unnamed.
totals <- daily |>
  dplyr::group_by(day) |>
  dplyr::summarise(total = sum(views), .groups = "drop")
names_at <- daily |>
  dplyr::group_by(number, label) |>
  dplyr::filter(sum(views) >= 5) |>
  dplyr::slice_max(views, n = 1, with_ties = FALSE) |>
  dplyr::ungroup() |>
  dplyr::select(number, label, day) |>
  dplyr::left_join(totals, by = "day") |>
  dplyr::mutate(hjust = dplyr::case_when(day - chart_from < 6 ~ 0,
                                         through - day < 6 ~ 1,
                                         .default = 0.5))

p <- ggplot(daily, aes(day, views, fill = factor(number))) +
  geom_col(width = 0.85) +
  geom_text(data = names_at,
            aes(day, total, label = label, colour = factor(number),
                hjust = hjust),
            inherit.aes = FALSE, vjust = -0.6, size = 3, fontface = "bold") +
  scale_fill_manual(values = check_colours, guide = "none") +
  scale_colour_manual(values = check_colours, guide = "none") +
  scale_x_date(limits = c(chart_from - 1L, through + 1L), expand = c(0, 0),
               breaks = rev(seq(through, chart_from, by = "-2 weeks")),
               date_labels = "%b %d") +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.15))) +
  theme_cds() +
  theme(panel.grid.minor = element_blank()) +
  labs(x = NULL, y = "Views",
       subtitle = glue("Each Signal Check in its own colour, {latest$label} ",
                       "in red. Views before sending are left out."))
brand_figure(p)
```

:::

## Row {height="620px"}

::: {.card title="How long readers keep each Signal Check open, first 14 days"}

```{r edition-dwell-chart}
#| fig-width: 10
#| fig-height: 4.6
#| fig-alt: |
#|   Small multiples, one panel per Signal Check. Each shows the share of its
#|   page views still open after 1 second, 5, 15 and 30 seconds, and 1, 2, 5
#|   and 10 minutes, with every other Signal Check's curve in the background
#|   and a dashed line at 50 percent.
brand_figure(dwell_panels(window_curve, "panel", ncol = 3), height = 0.07)
```

::: {.figure-note}
Each curve is the share of page views that stayed open, and visible, at
least that long. The pale lines behind it are the other Signal Checks, for
comparison. Where it crosses the dashed line is the median read. A tab
in the background does not count. Most Signal Checks have a few dozen views, so
one reader can move a curve by several percentage points.
:::

:::

## Row {height="auto"}

::: {.card title="Every edition"}

```{r edition-table}
review <- days |>
  dplyr::filter(age < 0) |>
  dplyr::group_by(number) |>
  dplyr::summarise(review = sum(views), .groups = "drop")
since <- days |>
  dplyr::filter(age >= 0) |>
  dplyr::group_by(number) |>
  dplyr::summarise(all_time = sum(views), .groups = "drop")
first_window <- cumulative |>
  dplyr::group_by(number) |>
  dplyr::summarise(first = max(cumulative), .groups = "drop")

coverage |>
  dplyr::left_join(first_window, by = "number") |>
  dplyr::left_join(dplyr::filter(window_dwell, number %in% comparable$number),
                   by = c("number", "label")) |>
  dplyr::left_join(since, by = "number") |>
  dplyr::left_join(review, by = "number") |>
  dplyr::arrange(dplyr::desc(published)) |>
  dplyr::transmute(
    label,
    sent = format_short_date(published),
    first = dplyr::case_when(
      !comparable ~ "Before tracking",
      days_seen < edition_window_days ~
        glue("{comma(first)} ({days_seen} of 14 days)"),
      .default = comma(first)
    ),
    median = ifelse(comparable, fmt_read(median_seconds), "-"),
    past_minute, past_five,
    reading = ifelse(comparable, fmt_reading(reading_seconds), "-"),
    all_time = dplyr::coalesce(all_time, 0),
    review = dplyr::coalesce(review, 0)
  ) |>
  gt() |>
  fmt_percent(c(past_minute, past_five), decimals = 0) |>
  fmt_number(c(all_time, review), decimals = 0) |>
  sub_missing(missing_text = "-") |>
  cols_align("right", c(first, median, reading)) |>
  cols_label(label = "Signal Check", sent = "Sent", first = "Views, first 14 days",
             median = "Median read", past_minute = "Open 1 min+",
             past_five = "Open 5 min+", reading = "Total reading time",
             all_time = "Views since sent", review = "Review views") |>
  table_options()
```

::: {.figure-note}
Median read and the two *Open* columns cover the first 14 days. *Median read*
is the time half the views were still open, estimated between the two time
marks either side of it. *Total reading time* adds up the time of every view
by every reader, each counted down to the last milestone it reached, so it is
a floor. *Review views* came before the Signal Check was sent, from our own
review link, and count nowhere else. Tracking began July 23, 2026, after
Signal Check #1 and Signal Check #2 were sent.
:::

:::

# Where readers come from

```{r sources-summary}
#| include: false
window_sessions <- traffic |>
  dplyr::inner_join(dplyr::filter(coverage, comparable),
                    by = "pagepath_redacted") |>
  dplyr::filter(day >= published, day < published + edition_window_days)

source_table <- window_sessions |>
  dplyr::group_by(sessionsource) |>
  dplyr::summarise(sessions = sum(sessions), .groups = "drop") |>
  dplyr::mutate(
    what = describe_source(sessionsource),
    group = source_groups$label[match(source_group(sessionsource),
                                      source_groups$group)],
    share = sessions / sum(sessions)
  ) |>
  dplyr::group_by(what, group) |>
  dplyr::summarise(sources = paste(sort(unique(sessionsource)), collapse = ", "),
                   sessions = sum(sessions), share = sum(share),
                   .groups = "drop") |>
  dplyr::arrange(dplyr::desc(sessions))

posts <- sum(source_table$share[source_table$group %in%
                                  c("Slack", "Teams", "Email")])

chart_from <- monday_of(through) - 12L * 7L
dashboard_sessions <- traffic |>
  dplyr::filter(page_kind == "dashboard", day >= chart_from) |>
  dplyr::mutate(file = dashboard_file(pagepath_redacted)) |>
  dplyr::inner_join(dashboards, by = "file")
```

## Row {height="auto"}

::: {.card title="How readers reach Signal Check"}

Every edition goes out by Slack, Teams and email, and each of those links
is tagged, so a session that starts from one is counted under it. *Our own
links* are the link to the latest edition and links inside an edition or a
dashboard. *No link recorded* is a bookmark, a typed address, or an app that
drops the link's source. In editions `r comparable$label[1]` onward, the
three posts started **`r percent(posts, accuracy = 1)`** of sessions in the
first 14 days.

:::

## Row {height="460px"}

::: {.card title="Signal Check sessions by where they started, first 14 days"}

```{r edition-sources-chart}
#| fig-width: 10
#| fig-height: 3.2
#| fig-alt: |
#|   Horizontal stacked bars, one per Signal Check edition, newest at the
#|   top, splitting each edition's sessions in its first 14 days by where
#|   they started: Slack, Teams, email, our own links, no link recorded and
#|   other sites. The total is at the end of each bar.
p <- source_bars(window_sessions, "label", rev(comparable$label))
brand_figure(p)
```

::: {.figure-note}
A session counts once for each edition it opened, and starts from one place.
:::

:::

## Row {height="auto"}

::: {.card title="Every source, editions `r comparable$label[1]` to `r latest$label`, first 14 days"}

```{r source-table}
source_table |>
  dplyr::select(what, sources, group, sessions, share) |>
  gt() |>
  fmt_number(sessions, decimals = 0) |>
  fmt_percent(share, decimals = 0) |>
  cols_label(what = "Where", sources = "Recorded as", group = "Grouped as",
             sessions = "Sessions", share = "Share") |>
  table_options()
```

:::

## Row {height="400px"}

::: {.card title="Dashboard sessions by where they started, last three months"}

```{r dashboard-sources-chart}
#| fig-width: 10
#| fig-height: 2.7
#| fig-alt: |
#|   Horizontal stacked bars, one per dashboard, splitting its sessions over
#|   the last three months by where they started: Slack, Teams, email, our own
#|   links, no link recorded and other sites.
p <- source_bars(dashboard_sessions, "name", sort(dashboards$name))
brand_figure(p, height = 0.11)
```

:::

# Dashboards

```{r dashboards-summary}
#| include: false
dashboard_rows <- traffic |>
  dplyr::filter(page_kind == "dashboard") |>
  dplyr::mutate(file = dashboard_file(pagepath_redacted)) |>
  dplyr::inner_join(dashboards, by = "file")

all_window <- window_totals(dashboard_rows, "views", through)
all_change <- relative_change(all_window[["current"]], all_window[["prior"]])

per_dashboard <- dashboard_rows |>
  dplyr::group_by(name) |>
  dplyr::group_modify(\(rows, key) {
    totals <- window_totals(rows, "views", through)
    tibble::tibble(current = totals[["current"]], prior = totals[["prior"]])
  }) |>
  dplyr::ungroup() |>
  dplyr::mutate(change = relative_change(current, prior))
top <- dplyr::slice_max(per_dashboard, current, n = 1, with_ties = FALSE)

dashboard_events <- events |>
  dplyr::filter(page_kind == "dashboard", day >= chart_from) |>
  dplyr::mutate(file = dashboard_file(pagepath_redacted)) |>
  dplyr::inner_join(dashboards, by = "file")
dashboard_curve <- dwell_curve(dashboard_events, "name")
dashboard_dwell <- dwell_summary(dashboard_curve, "name")

pooled_dashboard_median <- dashboard_events |>
  dplyr::mutate(all = "all") |>
  dwell_curve("all") |>
  dplyr::summarise(m = median_read(seconds, share)) |>
  dplyr::pull(m)

weeks <- dashboard_rows |>
  dplyr::filter(day >= chart_from) |>
  dplyr::mutate(week = monday_of(day)) |>
  dplyr::group_by(name, week) |>
  dplyr::summarise(views = sum(views), .groups = "drop") |>
  tidyr::complete(name = dashboards$name,
                  week = seq(chart_from, monday_of(through), by = "week"),
                  fill = list(views = 0)) |>
  dplyr::mutate(partial = week + 6L > through)
```

## Row {height="150px"}

::: {.valuebox color="primary"}
Dashboard views, last 4 weeks

`r nbsp(comma(all_window[["current"]]))`

`r fmt_delta(all_change)` on the 4 weeks before
:::

::: {.valuebox color="info"}
Most viewed, last 4 weeks

`r nbsp(top$name)`

`r glue("{comma(top$current)} views")`
:::

::: {.valuebox color="secondary"}
Median read, last three months

`r nbsp(fmt_read(pooled_dashboard_median))`

All dashboards together
:::

## Row {height="460px"}

::: {.card title="Views each week, last three months"}

```{r dashboard-weeks-chart}
#| fig-width: 10
#| fig-height: 3.1
#| fig-alt: |
#|   Small multiples of weekly bar charts, one panel per dashboard, showing
#|   page views each Monday-to-Sunday week over the last three months, each in
#|   its dashboard's own colour. The newest week, not yet over, is lighter.
# Each dashboard in its own accent; one with no theme found falls back to ink.
accents <- dashboard_accent(dashboards$file)
accents <- setNames(dplyr::coalesce(accents, palette$ink), dashboards$name)

p <- ggplot(weeks, aes(week + 3, views)) +
  geom_col(aes(fill = name, alpha = partial), width = 5.5) +
  scale_fill_manual(values = accents, guide = "none") +
  scale_alpha_manual(values = c(`FALSE` = 1, `TRUE` = 0.35), guide = "none") +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.08))) +
  scale_x_date(date_labels = "%b %d",
               breaks = rev(seq(monday_of(through), chart_from, by = "-4 weeks"))) +
  facet_wrap(~name, nrow = 1) +
  theme_cds() +
  theme(panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(face = "bold", hjust = 0, size = 11)) +
  labs(x = NULL, y = "Views",
       subtitle = "Weeks run Monday to Sunday. The lighter bar is this week so far.")
brand_figure(p)
```

:::

## Row {height="460px"}

::: {.card title="How long readers keep each dashboard open, last three months"}

```{r dashboard-dwell-chart}
#| fig-width: 10
#| fig-height: 3.1
#| fig-alt: |
#|   Small multiples, one panel per dashboard, each showing the share of its
#|   page views still open after 1 second up to 10 minutes, with the other
#|   dashboards' curves in the background and a dashed line at 50 percent.
brand_figure(dwell_panels(dashboard_curve, "name", ncol = nrow(dashboards)))
```

:::

## Row {height="auto"}

::: {.card title="Every dashboard"}

```{r dashboard-table}
per_dashboard |>
  dplyr::left_join(dashboard_dwell, by = "name") |>
  dplyr::left_join(dplyr::select(dashboards, name, first_seen), by = "name") |>
  dplyr::arrange(dplyr::desc(current)) |>
  dplyr::transmute(
    name, current, prior,
    direction = delta_direction(change), change = fmt_delta(change),
    median = fmt_read(median_seconds), past_minute, past_five,
    first_seen = format_short_date(first_seen)
  ) |>
  gt() |>
  fmt_number(c(current, prior), decimals = 0) |>
  fmt_percent(c(past_minute, past_five), decimals = 0) |>
  sub_missing(missing_text = "-") |>
  tab_style(cell_text(color = delta_colours[["up"]]),
            cells_body(change, rows = direction == "up")) |>
  tab_style(cell_text(color = delta_colours[["down"]]),
            cells_body(change, rows = direction == "down")) |>
  tab_style(cell_text(color = delta_colours[["flat"]]),
            cells_body(change, rows = direction == "flat")) |>
  cols_hide(direction) |>
  cols_align("right", c(change, median)) |>
  cols_label(name = "Dashboard", current = "Views, last 4 weeks",
             prior = "4 weeks before", change = "Change",
             median = "Median read", past_minute = "Open 1 min+",
             past_five = "Open 5 min+", first_seen = "First view") |>
  table_options()
```

::: {.figure-note}
Read times cover the last three months. Task Success Monitoring, Experience
Monitoring's earlier name, is counted as Experience Monitoring. This page
counts its own readers too.
:::

:::

# Metrics Cookbook

```{r cookbook-summary}
#| include: false
cookbook <- dplyr::filter(traffic, page_kind == "cookbook")
previews <- sum(traffic$views[traffic$page_kind == "preview"])

cookbook_weeks <- cookbook |>
  dplyr::mutate(week = monday_of(day)) |>
  dplyr::group_by(week) |>
  dplyr::summarise(views = sum(views), .groups = "drop") |>
  tidyr::complete(week = seq(monday_of(tracking_from), monday_of(through),
                             by = "week"),
                  fill = list(views = 0)) |>
  dplyr::mutate(partial = week + 6L > through)

# Two pages share a title (a recipe and its table), so the section names them.
cookbook_pages <- cookbook |>
  dplyr::mutate(
    section = sub("^/canadalogin-metrics-cookbook/([^/]*).*$", "\\1",
                  pagepath_redacted),
    section = ifelse(grepl("\\.html$", section) | section == "", "home",
                     section),
    title = sub("\\s*\u2013 CanadaLogin Metrics Cookbook$", "", pagetitle),
    title = dplyr::case_when(
      section == "home" ~ "Front page",
      endsWith(pagepath_redacted, "/") ~ paste(tools::toTitleCase(section), "index"),
      .default = title
    )
  ) |>
  dplyr::group_by(pagepath_redacted) |>
  dplyr::summarise(title = dplyr::last(title), section = dplyr::first(section),
                   views = sum(views), .groups = "drop") |>
  dplyr::mutate(page = ifelse(section == "home" | grepl(" index$", title),
                              title, glue("{title} ({section})"))) |>
  dplyr::slice_max(views, n = 12, with_ties = FALSE)
```

## Row {height="380px"}

::: {.card title="Cookbook views each week, since tracking began"}

```{r cookbook-weeks-chart}
#| fig-width: 10
#| fig-height: 2.6
#| fig-alt: |
#|   Bar chart of Metrics Cookbook page views each Monday-to-Sunday week since
#|   tracking began in July 2026. The newest week, not yet over, is lighter.
p <- ggplot(cookbook_weeks, aes(week + 3, views)) +
  geom_col(aes(fill = partial), width = 5.5) +
  scale_fill_manual(values = c(`FALSE` = palette$ink, `TRUE` = palette$quiet),
                    guide = "none") +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.08))) +
  scale_x_date(date_labels = "%b %d") +
  theme_cds() +
  theme(panel.grid.minor = element_blank()) +
  labs(x = NULL, y = "Views")
brand_figure(p, height = 0.12)
```

::: {.figure-note}
Previews of changes under review are left out: `r comma(previews)` views, all
ours. The Cookbook does not track how long a page stays open.
:::

:::

## Row {height="480px"}

::: {.card title="Most viewed pages, since tracking began"}

```{r cookbook-pages-chart}
#| fig-width: 10
#| fig-height: 3.5
#| fig-alt: |
#|   Horizontal bar chart of the twelve most viewed Metrics Cookbook pages
#|   since tracking began, most viewed at the top, each bar labelled with its
#|   views.
p <- ggplot(cookbook_pages, aes(views, stats::reorder(page, views))) +
  geom_col(fill = palette$ink, width = 0.7) +
  geom_text(aes(label = comma(views)), hjust = -0.3, size = 3.2,
            colour = "grey30") +
  scale_x_continuous(expand = expansion(mult = c(0, 0.08))) +
  theme_cds() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank()) +
  labs(x = "Views", y = NULL)
brand_figure(p)
```

:::

```{r cleanup}
#| include: false
# include: false matters for layout: this chunk sits in the last Row, where
# anything visible becomes a card and takes width from the chart.
if (!is.null(con)) DBI::dbDisconnect(con)
```

{{< include ../../_analytics.qmd >}}
