---
title: "CanadaLogin Experience Monitoring"
author: "EDCP Data and Research Team"  # colin.douglas@cds-snc.ca
format:
  dashboard:
    orientation: rows
    embed-resources: true
    scrolling: true
    theme: [cosmo, _fonts.scss]   # _fonts.scss: self-hosted brand fonts
    css: styles.css
    # Written by the setup chunk at render time; empty unless a check failed.
    include-before-body: preflight-banner.html
    # Written by the analytics chunk at render time; see _analytics.qmd.
    include-after-body: analytics-tag.html
brand: _brand.yml
params:
  ga_page_title: "Experience Monitoring Dashboard"
execute:
  echo: false
  warning: false
  message: false
knitr:
  opts_chunk:
    # ragg reads brand families out of the systemfonts registry (see
    # register_cds_fonts) and sizes text the same on macOS and Linux.
    dev: ragg_png
---

```{r setup}
source("R/connection.R")
source("R/registry.R")
source("R/metrics.R")
source("R/preflight.R")
source("R/branding.R")
source("R/colours.R")

suppressPackageStartupMessages({
  library(DBI)
  library(RAthena)
  library(dplyr)
  library(dbplyr)
  library(tidyr)
  library(glue)
  library(purrr)
  library(ggplot2)
  library(scales)
  library(gt)
})

con <- connect_athena()

# The help tab filters on this stream alone. Keyed on the id, which an admin
# cannot rename; declared here because preflight checks 6 and 7 read both.
help_stream_id <- "13052807364"
help_stream_name <- "CanadaLogin Website (Help/About/GC Partner info)"

# A failed check banners the dashboard rather than stopping the render, so the
# banner is what stands between a holed number and a publish. See R/preflight.R.
ga_lag <- 2L
preflight <- run_preflight_safety_check(
  con, today = Sys.Date(), ga_export_lag_days = ga_lag
)
write_preflight_banner(preflight)
write_preflight_status(preflight)

today <- Sys.Date()
as_of <- today - ga_lag        # GA's ~2-day processing lag; newest day expected

# The newest complete 7-day window across the required funnels.
data_through <- tbl(
  con, in_schema("google_analytics", "funnel_metrics_current")
) |>
  filter(
    metric_id == "task_success",
    funnel_id %in% !!required_funnels,
    window_days == "7",
    breakdown_value == "RESERVED_TOTAL",
    !window_incomplete
  ) |>
  summarise(m = max(window_end)) |>
  pull(m) |>
  as.Date()

series_start   <- as.Date("2000-01-01")          # early bound; pulls all history
trailing_start <- data_through - (7L * 12L)       # ~12-week working window

# "August 8", not "August 08": the integer day avoids zero-padding.
format_long_date <- function(d) {
  d <- as.Date(d)
  paste0(format(d, "%B"), " ", as.integer(format(d, "%d")), ", ", format(d, "%Y"))
}
data_through_label <- format_long_date(data_through)

# Whole-number percent, or "n/a" for an undefined rate.
fmt_pct <- function(x) ifelse(is.na(x), "n/a", paste0(round(x * 100), "%"))

# GA's "" and "(not set)" mean the same thing, and internal services are not
# listed individually. Neither label is a service, so neither reaches the table.
internal_rp_label <- "Internal apps"
unrecorded_rp_label <- "Relying party not recorded"
pooled_rp_labels <- c(internal_rp_label, unrecorded_rp_label)

# GA caps the funnel breakdown at 15 parties and the tail of that list shuffles
# from day to day, so the table shows only the busiest few.
party_rows <- 5L

# Prose spells small numbers out, and 15 is as high as a party count can go.
number_words <- c(
  "one", "two", "three", "four", "five", "six", "seven", "eight", "nine",
  "ten", "eleven", "twelve", "thirteen", "fourteen", "fifteen"
)

# GA's rp_name is an alias, so this resolves it to the service name the lookup
# gives, which pools a service that GA knows by more than one name into one row.
#
# replace(), not ifelse(): ifelse() on an empty frame returns logical(0), which
# clashes on type the moment an empty period is joined to a full one.
rp_display_name <- function(rp_name) {
  service <- label_relying_parties(con, rp_name)$service_name
  out <- coalesce(service, rp_name)
  out <- replace(out, rp_name %in% ga_excluded_rp_names, unrecorded_rp_label)
  replace(out, is_internal_rp(con, rp_name), internal_rp_label)
}

# Read once per funnel, for the exit step named in the table headings.
step_labels <- lapply(required_funnels, \(f) funnel_step_names(con, f))
names(step_labels) <- required_funnels

# The names are slugs, so underscores are opened up.
format_step_name <- function(step) {
  if (is.na(step)) "unknown step" else paste0("'", gsub("_", " ", step), "'")
}

exit_step_label <- function(funnel_id) {
  format_step_name(step_labels[[funnel_id]]$exit_step)
}

entry_step_label <- function(funnel_id) {
  format_step_name(step_labels[[funnel_id]]$entry_step)
}

# The ratio denominator is not always the funnel's first step: the migration
# funnels are measured from a prompt part way through.
denominator_is_entry <- function(funnel_id) {
  isTRUE(step_labels[[funnel_id]]$entry_number == 1L)
}

# People reaching the entry step over the long window. One token, no spaces, or
# Quarto renders it at body size.
funnel_starts <- function(funnel_id) {
  format(
    task_success_long_window(con, funnel_id, data_through)$denominator,
    big.mark = ","
  )
}

long_window_label <- glue("{long_window_days}-day")

# funnel_starts() counts the ratio denominator, so only a funnel measured from
# its own first step can call that number "starts".
starts_box_title <- function(funnel_id) {
  if (denominator_is_entry(funnel_id)) {
    glue("{long_window_label} starts")
  } else {
    glue("{long_window_label} {entry_step_label(funnel_id)}")
  }
}

# The table's count column holds the same denominator as the value box.
starts_column_label <- function(funnel_id) {
  if (denominator_is_entry(funnel_id)) {
    "Started"
  } else {
    glue("Reached {entry_step_label(funnel_id)}")
  }
}

chart_title <- function(funnel_id) {
  glue("Task Success: {funnel_label(funnel_id)}")
}

# Hand-wrapped to two lines: one line runs under the logo, three eat plot area.
# Line two names the denominator where it is not the funnel's first step.
chart_subtitle <- function(funnel_id) {
  parties <- if (denominator_is_entry(funnel_id)) {
    "All relying parties, as reported by Google Analytics."
  } else {
    glue("All relying parties. Rate is of people who reached ",
         "{entry_step_label(funnel_id)}.")
  }
  paste(
    "7-day rolling rate (blue line) over the daily rate (grey points).",
    parties,
    sep = "\n"
  )
}

chart_alt <- function(funnel_id) {
  glue(
    "Chart of the task success rate over time for the ",
    "{tolower(funnel_label(funnel_id))} funnel, across all relying parties. ",
    "A bold blue line traces the 7-day ",
    "rolling rate, breaking wherever the funnel version changes; faint grey ",
    "points underneath are the noisier daily rate, sized by how many people ",
    "were in that day's denominator. The y-axis runs from zero to one ",
    "hundred percent."
  )
}

# Tested on the rate, not nrow(): an ungrouped summarise over no rows still
# returns a row, one reading 0 out of 0.
prior_period_complete <- function(funnel_id) {
  prior <- task_success_long_window(
    con, funnel_id, data_through - long_window_days
  )
  nrow(prior) > 0 && !is.na(prior$value)
}

# Direction is carried by the arrow and the sign, not colour alone; an
# uncalculable change is a dash, not a zero. gt colours it, see delta_colours.
fmt_delta <- function(delta) {
  case_when(
    is.na(delta) ~ "-",
    delta > 0.0005 ~ sprintf("\u25b2 %+.1f pts", delta * 100),
    delta < -0.0005 ~ sprintf("\u25bc %+.1f pts", delta * 100),
    .default = "no change"
  )
}

# Change colours: forest rather than brand green, too light to pass contrast.
delta_colours <- c(up = "#115740", down = "#AB2328", flat = "#5C6670")

# Makes a column of dashes read as "too early" rather than as broken.
comparison_note <- function(funnel_id) {
  if (prior_period_complete(funnel_id)) {
    return(NULL)
  }
  glue(
    "The change against the previous {long_window_days} days cannot be ",
    "calculated yet: this funnel does not yet have {2 * long_window_days} days ",
    "of history, and there is no earlier window to compare against."
  )
}

# Shown under every chart: point size is an encoding, not decoration.
points_note <- paste(
  "The daily points on the chart are sized by how many people were in that",
  "day's denominator."
)

# Shown under every chart and on the Overview: what the numbers cover.
internal_note <- glue(
  "The headline figures and the top row are Google Analytics' own total across ",
  "every relying party. The table lists the {number_words[party_rows]} busiest ",
  "services only."
)
```

# Overview

## Row {height="120px"}

```{r data-through-valuebox}
#| content: valuebox
#| title: "Data through"
list(
  icon = "calendar-event",
  color = "primary",
  value = data_through_label
)
```

## Row

::: {.card title="About this dashboard"}

This is an internal working instrument for the EDCP Data and Research Team. It
watches how people get through CanadaLogin between report cycles, so analysts
get the numbers in one place without digging through Google Analytics. 

Task success is the share of users who start a flow and reach its defined
finishing point, measured from [Google Analytics 4 funnel data](https://github.com/cds-snc/canadalogin-reporting-data-pipeline/tree/main/infra/modules/google_analytics/funnel_src/funnels). Google Analytics
runs on a deliberate two-day processing lag, so the data ends a couple of days
before today; the "Data through" date says how current it is.

Numbers from this dashboard are preliminary. The canonical task success metrics live in the
[monthly task success report](https://drive.google.com/drive/folders/1gqU2XQfkH5ARbdc1gVRS4SdnZivZzjnR).
This dashboard should not be shared with partners or the public. It is not a substitute
for the monthly report, which is created thoughtfully and contains proper analysis and
context.

:::

```{r funnel-pages}
#| output: asis
# Generated from one child template, since the pages differ only by funnel id
# and a copy-pasted mismatch would render one funnel's numbers under another's.
funnel_page <- function(fid, h1) {
  label <- funnel_label(fid)
  # Sent to stderr rather than message() so it shows up in the log
  log_render <- function(...) cat(sprintf(...), file = stderr())
  started <- Sys.time()
  log_render("[funnel] %s: rendering\n", fid)
  page <- knitr::knit_child("_funnel-page.qmd", envir = environment(), quiet = TRUE)
  log_render(
    "[funnel] %s: done in %.1fs\n", fid,
    as.numeric(difftime(Sys.time(), started, units = "secs"))
  )
  page
}

# Sign in and sign up stay first: they are the metric of record that feeds the
# monthly task success report.
standalone_funnels <- c("sign_in", "sign_up", "recover_password")

cat(unlist(lapply(standalone_funnels, funnel_page, h1 = "#")), sep = "\n")
```

# Migration

## Row

### Column {.tabset}

```{r migration-pages}
#| output: asis
# The two migration funnels are one flow split on whether the person already had
# a CanadaLogin account, so they share a tab. The tabset sits on the Column, not
# on the Row: on the Row, only the first tab's layout is read.
migration_funnels <- c("migration_existing_to_cl", "migration_new_to_cl")

cat(unlist(lapply(migration_funnels, funnel_page, h1 = "####")), sep = "\n")
```


# Help site

```{r help-site-data}
#| include: false
# One read serves the value boxes, all four tables and the chart. include: false
# so the chunk does not become a card.
help_top_n <- 15L

help_window <- tbl(con, in_schema("google_analytics", "page_traffic")) |>
  filter(
    streamid == !!help_stream_id,
    as.Date(date) >= as.Date(!!as.character(trailing_start)),
    as.Date(date) <= as.Date(!!as.character(data_through))
  ) |>
  select(date, pagepath, pagetitle, screenpageviews) |>
  collect() |>
  mutate(
    date = as.Date(date),
    # integer64 does not survive arithmetic with doubles cleanly.
    views = as.numeric(screenpageviews),
    # /en and /en/ are one page, and the site emits both.
    path = ifelse(pagepath == "/", pagepath, sub("/+$", "", pagepath)),
    # The bare root is the English landing page, so it folds into /en.
    path = ifelse(path == "/", "/en", path),
    # Every title ends in the site name, noise repeated down the column.
    title = sub(" - (CanadaLogin|ConnexionCanada)$", "", pagetitle),
    # Anything outside /en and /fr is vulnerability-scanner traffic
    # (oast.live callbacks, /swagger-ui, /login.php), not a page anyone wrote.
    lang = case_when(
      path == "/en" | startsWith(path, "/en/") ~ "en",
      path == "/fr" | startsWith(path, "/fr/") ~ "fr"
    )
  )

# Ranked once for every window and language, so each table below is a filter.
help_ranked <- bind_rows(
  filter(help_window, date > data_through - 7L) |> mutate(window = "7"),
  filter(help_window, date > data_through - long_window_days) |>
    mutate(window = as.character(long_window_days))
) |>
  filter(!is.na(lang)) |>
  group_by(window, lang, path, title) |>
  summarise(title_views = sum(views), .groups = "drop_last") |>
  # A page is a path, labelled with the title it was viewed under most often:
  # a reader whose browser translates the page reports a translated title.
  mutate(views = sum(title_views)) |>
  slice_max(title_views, n = 1, with_ties = FALSE) |>
  group_by(window, lang) |>
  arrange(desc(views), .by_group = TRUE) |>
  slice_head(n = help_top_n) |>
  ungroup() |>
  mutate(
    # The two languages are served from their own domains.
    page = paste0(
      '<a href="',
      ifelse(lang == "fr", "https://connexion.canada.ca",
             "https://login.canada.ca"),
      path, '" target="_blank" rel="noopener">',
      htmltools::htmlEscape(title), "</a>"
    )
  )

help_7d <- filter(help_window, date > data_through - 7L)
help_long <- filter(help_window, date > data_through - long_window_days)

# Language share over the long window. Scanner traffic has no language, so it
# is out of the denominator.
help_split <- help_long |>
  filter(!is.na(lang)) |>
  count(lang, wt = views, name = "views") |>
  mutate(share = round(100 * views / sum(views)))

# One token, no spaces, or Quarto renders it at body size.
help_split_label <- paste0(help_split$share[help_split$lang == "fr"], "%")
```

## Row {height="420px"}

### Column {width="24%"}

::: {.valuebox color="primary"}
Views, last 7 days

`r format(sum(help_7d$views), big.mark = ",")`
:::

::: {.valuebox color="secondary"}
Views, last `r long_window_days` days

`r format(sum(help_long$views), big.mark = ",")`
:::

::: {.valuebox color="info"}
French share, last `r long_window_days` days

`r help_split_label`
:::

### Column {width="76%"}

```{r help-site-chart}
#| title: "Help site page views over time"
#| fig-width: 7.7
#| fig-height: 3.6
#| fig-alt: |
#|   Chart of daily page views on the CanadaLogin help site over the last twelve
#|   weeks. A blue line traces total views per day across every help page, with
#|   a regular dip each weekend.

p <- help_window |>
  group_by(date) |>
  summarise(views = sum(views), .groups = "drop") |>
  ggplot(aes(date, views)) +
  geom_line(colour = colors$brand[["blue"]], linewidth = 0.8) +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.05))) +
  scale_x_date(date_labels = "%b %d") +
  theme_cds() +
  labs(
    x = NULL, y = "Page views",
    title = "Help site page views",
    # Wrapped by hand: a single-line subtitle runs under the logo.
    subtitle = "Daily views across every page of the CanadaLogin help stream."
  )

add_cds_logo(add_watermark(p, date = data_through), height = 0.09)
```

## Row

### Column {width="50%"}

::: {.card title="English pages, last 7 days"}

```{r help-table-en-7d}
help_ranked |>
  filter(window == "7", lang == "en") |>
  select(page, views) |>
  gt() |>
  fmt_markdown(page) |>
  fmt_number(views, decimals = 0) |>
  cols_label(page = "Page", views = "Views") |>
  tab_options(table.width = pct(100), table.font.size = px(13),
              data_row.padding = px(3), table.border.top.style = "none")
```

:::

::: {.card title="French pages, last 7 days"}

```{r help-table-fr-7d}
help_ranked |>
  filter(window == "7", lang == "fr") |>
  select(page, views) |>
  gt() |>
  fmt_markdown(page) |>
  fmt_number(views, decimals = 0) |>
  cols_label(page = "Page", views = "Views") |>
  tab_options(table.width = pct(100), table.font.size = px(13),
              data_row.padding = px(3), table.border.top.style = "none")
```

:::

### Column {width="50%"}

::: {.card title="English pages, last `r long_window_days` days"}

```{r help-table-en-long}
help_ranked |>
  filter(window == as.character(long_window_days), lang == "en") |>
  select(page, views) |>
  gt() |>
  fmt_markdown(page) |>
  fmt_number(views, decimals = 0) |>
  cols_label(page = "Page", views = "Views") |>
  tab_options(table.width = pct(100), table.font.size = px(13),
              data_row.padding = px(3), table.border.top.style = "none")
```

:::

::: {.card title="French pages, last `r long_window_days` days"}

```{r help-table-fr-long}
help_ranked |>
  filter(window == as.character(long_window_days), lang == "fr") |>
  select(page, views) |>
  gt() |>
  fmt_markdown(page) |>
  fmt_number(views, decimals = 0) |>
  cols_label(page = "Page", views = "Views") |>
  tab_options(table.width = pct(100), table.font.size = px(13),
              data_row.padding = px(3), table.border.top.style = "none")
```

:::

```{r cleanup}
#| include: false
# include: false is layout, not tidiness: this chunk sits in the last Row, and
# anything visible there becomes a card and takes width from the table.
DBI::dbDisconnect(con)
```

{{< include _analytics.qmd >}}
