---
title: "CanadaLogin Experience Monitoring"
author: "EDCP Data and Research Team"  # colin.douglas@cds-snc.ca
format:
  dashboard:
    orientation: rows
    embed-resources: true
    scrolling: true
    theme: [cosmo, _fonts.scss]   # _fonts.scss: self-hosted brand fonts
    css: styles.css
    # Written by the setup chunk at render time; empty unless a check failed.
    include-before-body: preflight-banner.html
    # Written by the analytics chunk at render time; see _analytics.qmd.
    include-after-body: analytics-tag.html
brand: _brand.yml
params:
  ga_page_title: "Experience Monitoring Dashboard"
execute:
  echo: false
  warning: false
  message: false
knitr:
  opts_chunk:
    # ragg reads brand families out of the systemfonts registry (see
    # register_cds_fonts) and sizes text the same on macOS and Linux.
    dev: ragg_png
---

```{r setup}
source("R/connection.R")
source("R/registry.R")
source("R/metrics.R")
source("R/preflight.R")
source("R/branding.R")
source("R/colours.R")

suppressPackageStartupMessages({
  library(DBI)
  library(RAthena)
  library(dplyr)
  library(dbplyr)
  library(tidyr)
  library(glue)
  library(purrr)
  library(ggplot2)
  library(scales)
  library(gt)
})

con <- connect_athena()

# The help tab filters on this stream alone. Keyed on the id, which an admin
# cannot rename; declared here because preflight checks 6 and 7 read both.
help_stream_id <- "13052807364"
help_stream_name <- "CanadaLogin Website (Help/About/GC Partner info)"

# A failed check banners the dashboard rather than stopping the render, so the
# banner is what stands between a holed number and a publish. See R/preflight.R.
ga_lag <- 2L
preflight <- run_preflight_safety_check(
  con, today = Sys.Date(), ga_export_lag_days = ga_lag
)
write_preflight_banner(preflight)
write_preflight_status(preflight)

today <- Sys.Date()
as_of <- today - ga_lag        # GA's ~2-day processing lag; newest day expected

# The newest complete 7-day window across the required funnels.
data_through <- tbl(
  con, in_schema("google_analytics", "funnel_metrics_current")
) |>
  filter(
    metric_id == "task_success",
    funnel_id %in% !!required_funnels,
    window_days == "7",
    breakdown_value == "RESERVED_TOTAL",
    !window_incomplete
  ) |>
  summarise(m = max(window_end)) |>
  pull(m) |>
  as.Date()

series_start   <- as.Date("2000-01-01")          # early bound; pulls all history
trailing_start <- data_through - (7L * 12L)       # ~12-week working window

# "August 8", not "August 08": the integer day avoids zero-padding.
format_long_date <- function(d) {
  d <- as.Date(d)
  paste0(format(d, "%B"), " ", as.integer(format(d, "%d")), ", ", format(d, "%Y"))
}
data_through_label <- format_long_date(data_through)

# Whole-number percent, or "n/a" for an undefined rate.
fmt_pct <- function(x) ifelse(is.na(x), "n/a", paste0(round(x * 100), "%"))

# Two pooled rows. Internal services are not listed individually, and GA's ""
# and "(not set)" mean the same thing. Both sort to the bottom of the table.
internal_rp_label <- "Internal apps"
unrecorded_rp_label <- "Relying party not recorded"
pooled_rp_labels <- c(internal_rp_label, unrecorded_rp_label)

# GA's rp_name is an alias, so this resolves it to the service name the lookup
# gives, which pools a service that GA knows by more than one name into one row.
#
# replace(), not ifelse(): ifelse() on an empty frame returns logical(0), which
# clashes on type the moment an empty period is joined to a full one.
rp_display_name <- function(rp_name) {
  service <- label_relying_parties(con, rp_name)$service_name
  out <- coalesce(service, rp_name)
  out <- replace(out, rp_name %in% ga_excluded_rp_names, unrecorded_rp_label)
  replace(out, is_internal_rp(con, rp_name), internal_rp_label)
}

# Read once per funnel, for the exit step named in the table headings.
step_labels <- lapply(required_funnels, \(f) funnel_step_names(con, f))
names(step_labels) <- required_funnels

# The names are slugs, so underscores are opened up.
format_step_name <- function(step) {
  if (is.na(step)) "unknown step" else paste0("'", gsub("_", " ", step), "'")
}

exit_step_label <- function(funnel_id) {
  format_step_name(step_labels[[funnel_id]]$exit_step)
}

# People reaching the entry step over the long window. One token, no spaces, or
# Quarto renders it at body size.
funnel_starts <- function(funnel_id) {
  format(
    task_success_long_window(con, funnel_id, data_through)$denominator,
    big.mark = ","
  )
}

long_window_label <- glue("{long_window_days}-day")

# Tested on the rate, not nrow(): an ungrouped summarise over no rows still
# returns a row, one reading 0 out of 0.
prior_period_complete <- function(funnel_id) {
  prior <- task_success_long_window(
    con, funnel_id, data_through - long_window_days
  )
  nrow(prior) > 0 && !is.na(prior$value)
}

# Direction is carried by the arrow and the sign, not colour alone; an
# uncalculable change is a dash, not a zero. gt colours it, see delta_colours.
fmt_delta <- function(delta) {
  case_when(
    is.na(delta) ~ "-",
    delta > 0.0005 ~ sprintf("\u25b2 %+.1f pts", delta * 100),
    delta < -0.0005 ~ sprintf("\u25bc %+.1f pts", delta * 100),
    .default = "no change"
  )
}

# Change colours: forest rather than brand green, too light to pass contrast.
delta_colours <- c(up = "#115740", down = "#AB2328", flat = "#5C6670")

# Makes a column of dashes read as "too early" rather than as broken.
comparison_note <- function(funnel_id) {
  if (prior_period_complete(funnel_id)) {
    return(NULL)
  }
  glue(
    "The change against the previous {long_window_days} days cannot be ",
    "calculated yet: this funnel does not yet have {2 * long_window_days} days ",
    "of history, and there is no earlier window to compare against."
  )
}

# Shown under every table and chart: the exclusion changes what the numbers mean.
internal_note <- paste(
  "The headline figures, the chart and the top row are Google Analytics'",
  "own total across every relying party. Internal services such as Manage",
  "CanadaLogin are pooled into one row rather than listed, so the rows below",
  "still add up to the top one. Service names and operators come from the",
  "shared relying-party tables in the data lake, which also combine a service",
  "that Google Analytics knows by more than one name into a single row."
)
```

# Overview

## Row {height="120px"}

```{r data-through-valuebox}
#| content: valuebox
#| title: "Data through"
list(
  icon = "calendar-event",
  color = "primary",
  value = data_through_label
)
```

## Row

::: {.card title="About this dashboard"}

This is an internal working instrument for the EDCP Data and Research Team. It
watches how people get through CanadaLogin between report cycles, so analysts
get the numbers in one place without digging through Google Analytics. The sign
in and sign up pages carry task success rates; the help site page carries the
most-read help pages, which is a read on what people look up when a flow does
not go smoothly.

It is not the source of truth. The canonical task success numbers live in the
monthly task success report, a written Google doc; this dashboard feeds that
report and should not be quoted as authoritative. It is internal only, not for
partners, executives, or the public.

Task success is the share of users who start a flow and reach its defined
finishing point, measured from Google Analytics 4 funnel data. Google Analytics
runs on a deliberate two-day processing lag, so the data ends a couple of days
before today; the "Data through" date says how current it is.

The longer-term figures are a rolling `r long_window_days`-day window computed in
the reporting pipeline, not a calendar month. Google Analytics counts each person
once per window, so a month-length rate cannot be built by adding up shorter
windows and has to come from the pipeline.

`r internal_note`

:::

# Sign in

## Row {height="420px"}

### Column {width="24%"}

::: {.valuebox color="primary"}
Latest 7-day rate

`r fmt_pct(task_success_latest(con, "sign_in", "7", trailing_start, data_through)$value)`
:::

::: {.valuebox color="secondary"}
`r long_window_label` rate (rolling)

`r fmt_pct(task_success_long_window(con, "sign_in", data_through)$value)`
:::

::: {.valuebox color="info"}
`r long_window_label` starts

`r funnel_starts("sign_in")`
:::

### Column {width="76%"}

```{r sign-in-chart}
#| title: "Task success rate over time"
#| fig-width: 7.7
#| fig-height: 3.6
#| fig-alt: |
#|   Chart of the sign-in task success rate over time, external relying parties
#|   only. A bold blue line traces the 7-day rolling rate, breaking wherever the
#|   funnel version changes; faint grey points underneath are the noisier daily
#|   rate. The y-axis runs from zero to one hundred percent.

s7 <- task_success_series(con, "sign_in", "7", series_start, data_through)
s1 <- task_success_series(con, "sign_in", "1", series_start, data_through)

p <- ggplot() +
  geom_point(
    data = s1, aes(window_end, value),
    colour = "grey70", size = 0.7, alpha = 0.6
  ) +
  # Grouped by version so the line BREAKS where the definition changes.
  geom_line(
    data = s7, aes(window_end, value, group = funnel_version),
    colour = colors$brand[["blue"]], linewidth = 1
  ) +
  scale_y_continuous(
    labels = label_percent(accuracy = 1), limits = c(0, 1),
    expand = expansion(mult = c(0, 0.05))
  ) +
  scale_x_date(date_labels = "%b %d") +
  theme_cds() +
  labs(
    x = NULL, y = "Task success rate",
    title = "Task Success: Sign in",
    # Wrapped by hand: a single-line subtitle runs under the logo.
    subtitle = paste(
      "7-day rolling rate (blue line) over the daily rate (grey points).",
      "All relying parties, as reported by Google Analytics.",
      sep = "\n"
    )
  )

# The logo is a fraction of figure height, so a small figure needs a smaller one.
add_cds_logo(add_watermark(p, date = data_through), height = 0.09)
```

## Row

::: {.card title="By relying party (latest values)"}

```{r sign-in-table}
exit_label <- exit_step_label("sign_in")
compare <- prior_period_complete("sign_in")

latest_7d <- party_step_counts(
  con, "sign_in", "7", trailing_start, data_through
) |>
  group_by(breakdown_value) |>
  slice_max(window_end, n = 1, with_ties = FALSE) |>
  ungroup() |>
  mutate(rp = rp_display_name(breakdown_value)) |>
  as_task_success(rp) |>
  select(rp, rate_7d = value)

# Both periods come through the long-window seam. They never share a day.
by_rp_long <- function(as_of) {
  task_success_long_window(con, "sign_in", as_of, breakdown_value,
                           counts = party_step_counts) |>
    mutate(rp = rp_display_name(breakdown_value)) |>
    as_task_success(rp)
}

counts_long <- by_rp_long(data_through) |>
  select(rp, rate_long = value, entered = denominator, finished = numerator)
prior_long <- by_rp_long(data_through - long_window_days) |>
  select(rp, prior_long = value)

merged <- reduce(list(latest_7d, counts_long, prior_long), full_join, by = "rp")

# rp is already the service name, so the operator is looked up by that. The
# two pooled rows are not services and come back empty.
per_rp <- merged |>
  mutate(Operator = coalesce(service_operators(con, merged$rp), "")) |>
  transmute(
    Service = rp, Operator,
    rate_7d, rate_long, prior_long, entered, finished
  ) |>
  # Busiest first, with the two pooled rows held at the end.
  arrange(Service %in% pooled_rp_labels, desc(entered))

overall <- task_success_long_window(con, "sign_in", data_through) |>
  transmute(
    Service = "All relying parties (Google Analytics total)",
    Operator = "",
    rate_7d = task_success_latest(
      con, "sign_in", "7", trailing_start, data_through
    )$value,
    rate_long = value,
    prior_long = task_success_long_window(
      con, "sign_in", data_through - long_window_days
    )$value,
    entered = denominator, finished = numerator
  )

rows <- bind_rows(overall, per_rp) |>
  # The column stays even with nothing to compare against; every row reads as
  # a dash and comparison_note() says why.
  mutate(delta = if (compare) rate_long - prior_long else NA_real_) |>
  transmute(
    Service, Operator, rate_7d, rate_long,
    change = fmt_delta(delta), entered, finished, delta
  )

gt(rows) |>
  cols_hide(delta) |>
  fmt_percent(c(rate_7d, rate_long), decimals = 0) |>
  fmt_number(c(entered, finished), decimals = 0) |>
  sub_missing(missing_text = "n/a") |>
  cols_label(
    rate_7d = "7-day rate",
    rate_long = glue("{long_window_label} rate"),
    change = glue("vs previous {long_window_days} days"),
    entered = html(glue("Started<br>({long_window_label})")),
    finished = html(glue("Reached {exit_label}<br>({long_window_label})"))
  ) |>
  tab_style(cell_text(weight = "bold"), cells_body(rows = 1)) |>
  tab_style(
    cell_text(color = delta_colours[["up"]]),
    cells_body(columns = change, rows = !is.na(delta) & delta > 0.0005)
  ) |>
  tab_style(
    cell_text(color = delta_colours[["down"]]),
    cells_body(columns = change, rows = !is.na(delta) & delta < -0.0005)
  ) |>
  tab_style(
    cell_text(color = delta_colours[["flat"]]),
    cells_body(columns = change, rows = is.na(delta) | abs(delta) <= 0.0005)
  ) |>
  tab_options(
    table.width = pct(100),
    table.font.size = px(14),
    data_row.padding = px(4),
    table.border.top.style = "none"
  )
```

::: {.figure-note}
**Caveat.** This rate stops at MFA selection, the last step Google Analytics can
see before the off-site redirect to IBM Verify. It is not a true completion rate,
and it is not comparable to sign up.

`r comparison_note("sign_in")`

`r internal_note`
:::

:::

# Sign up

## Row {height="420px"}

### Column {width="24%"}

::: {.valuebox color="primary"}
Latest 7-day rate

`r fmt_pct(task_success_latest(con, "sign_up", "7", trailing_start, data_through)$value)`
:::

::: {.valuebox color="secondary"}
`r long_window_label` rate (rolling)

`r fmt_pct(task_success_long_window(con, "sign_up", data_through)$value)`
:::

::: {.valuebox color="info"}
`r long_window_label` starts

`r funnel_starts("sign_up")`
:::

### Column {width="76%"}

```{r sign-up-chart}
#| title: "Task success rate over time"
#| fig-width: 7.7
#| fig-height: 3.6
#| fig-alt: |
#|   Chart of the sign-up task success rate over time, external relying parties
#|   only. A bold blue line traces the 7-day rolling rate, breaking wherever the
#|   funnel version changes; faint grey points underneath are the noisier daily
#|   rate. The y-axis runs from zero to one hundred percent.

s7 <- task_success_series(con, "sign_up", "7", series_start, data_through)
s1 <- task_success_series(con, "sign_up", "1", series_start, data_through)

p <- ggplot() +
  geom_point(
    data = s1, aes(window_end, value),
    colour = "grey70", size = 0.7, alpha = 0.6
  ) +
  # Grouped by version so the line BREAKS where the definition changes.
  geom_line(
    data = s7, aes(window_end, value, group = funnel_version),
    colour = colors$brand[["blue"]], linewidth = 1
  ) +
  scale_y_continuous(
    labels = label_percent(accuracy = 1), limits = c(0, 1),
    expand = expansion(mult = c(0, 0.05))
  ) +
  scale_x_date(date_labels = "%b %d") +
  theme_cds() +
  labs(
    x = NULL, y = "Task success rate",
    title = "Task Success: Sign up",
    # Wrapped by hand: a single-line subtitle runs under the logo.
    subtitle = paste(
      "7-day rolling rate (blue line) over the daily rate (grey points).",
      "All relying parties, as reported by Google Analytics.",
      sep = "\n"
    )
  )

# The logo is a fraction of figure height, so a small figure needs a smaller one.
add_cds_logo(add_watermark(p, date = data_through), height = 0.09)
```

## Row

::: {.card title="By relying party (latest values)"}

```{r sign-up-table}
exit_label <- exit_step_label("sign_up")
compare <- prior_period_complete("sign_up")

latest_7d <- party_step_counts(
  con, "sign_up", "7", trailing_start, data_through
) |>
  group_by(breakdown_value) |>
  slice_max(window_end, n = 1, with_ties = FALSE) |>
  ungroup() |>
  mutate(rp = rp_display_name(breakdown_value)) |>
  as_task_success(rp) |>
  select(rp, rate_7d = value)

# Both periods come through the long-window seam. They never share a day.
by_rp_long <- function(as_of) {
  task_success_long_window(con, "sign_up", as_of, breakdown_value,
                           counts = party_step_counts) |>
    mutate(rp = rp_display_name(breakdown_value)) |>
    as_task_success(rp)
}

counts_long <- by_rp_long(data_through) |>
  select(rp, rate_long = value, entered = denominator, finished = numerator)
prior_long <- by_rp_long(data_through - long_window_days) |>
  select(rp, prior_long = value)

merged <- reduce(list(latest_7d, counts_long, prior_long), full_join, by = "rp")

# rp is already the service name, so the operator is looked up by that. The
# two pooled rows are not services and come back empty.
per_rp <- merged |>
  mutate(Operator = coalesce(service_operators(con, merged$rp), "")) |>
  transmute(
    Service = rp, Operator,
    rate_7d, rate_long, prior_long, entered, finished
  ) |>
  # Busiest first, with the two pooled rows held at the end.
  arrange(Service %in% pooled_rp_labels, desc(entered))

overall <- task_success_long_window(con, "sign_up", data_through) |>
  transmute(
    Service = "All relying parties (Google Analytics total)",
    Operator = "",
    rate_7d = task_success_latest(
      con, "sign_up", "7", trailing_start, data_through
    )$value,
    rate_long = value,
    prior_long = task_success_long_window(
      con, "sign_up", data_through - long_window_days
    )$value,
    entered = denominator, finished = numerator
  )

rows <- bind_rows(overall, per_rp) |>
  # The column stays even with nothing to compare against; every row reads as
  # a dash and comparison_note() says why.
  mutate(delta = if (compare) rate_long - prior_long else NA_real_) |>
  transmute(
    Service, Operator, rate_7d, rate_long,
    change = fmt_delta(delta), entered, finished, delta
  )

gt(rows) |>
  cols_hide(delta) |>
  fmt_percent(c(rate_7d, rate_long), decimals = 0) |>
  fmt_number(c(entered, finished), decimals = 0) |>
  sub_missing(missing_text = "n/a") |>
  cols_label(
    rate_7d = "7-day rate",
    rate_long = glue("{long_window_label} rate"),
    change = glue("vs previous {long_window_days} days"),
    entered = html(glue("Started<br>({long_window_label})")),
    finished = html(glue("Reached {exit_label}<br>({long_window_label})"))
  ) |>
  tab_style(cell_text(weight = "bold"), cells_body(rows = 1)) |>
  tab_style(
    cell_text(color = delta_colours[["up"]]),
    cells_body(columns = change, rows = !is.na(delta) & delta > 0.0005)
  ) |>
  tab_style(
    cell_text(color = delta_colours[["down"]]),
    cells_body(columns = change, rows = !is.na(delta) & delta < -0.0005)
  ) |>
  tab_style(
    cell_text(color = delta_colours[["flat"]]),
    cells_body(columns = change, rows = is.na(delta) | abs(delta) <= 0.0005)
  ) |>
  tab_options(
    table.width = pct(100),
    table.font.size = px(14),
    data_row.padding = px(4),
    table.border.top.style = "none"
  )
```

::: {.figure-note}
**Note.** Sign up's exit is the account-creation confirmation page, a real
first-party event, so this is a true completion rate.

`r comparison_note("sign_up")`

`r internal_note`
:::

:::

# Help site

```{r help-site-data}
#| include: false
# One read serves the value boxes, all four tables and the chart. include: false
# so the chunk does not become a card.
help_top_n <- 15L

help_window <- tbl(con, in_schema("google_analytics", "page_traffic")) |>
  filter(
    streamid == !!help_stream_id,
    as.Date(date) >= as.Date(!!as.character(trailing_start)),
    as.Date(date) <= as.Date(!!as.character(data_through))
  ) |>
  select(date, pagepath, pagetitle, screenpageviews) |>
  collect() |>
  mutate(
    date = as.Date(date),
    # integer64 does not survive arithmetic with doubles cleanly.
    views = as.numeric(screenpageviews),
    # /en and /en/ are one page, and the site emits both.
    path = ifelse(pagepath == "/", pagepath, sub("/+$", "", pagepath)),
    # The bare root is the English landing page, so it folds into /en.
    path = ifelse(path == "/", "/en", path),
    # Every title ends in the site name, noise repeated down the column.
    title = sub(" - (CanadaLogin|ConnexionCanada)$", "", pagetitle),
    # Anything outside /en and /fr is vulnerability-scanner traffic
    # (oast.live callbacks, /swagger-ui, /login.php), not a page anyone wrote.
    lang = case_when(
      path == "/en" | startsWith(path, "/en/") ~ "en",
      path == "/fr" | startsWith(path, "/fr/") ~ "fr"
    )
  )

# Ranked once for every window and language, so each table below is a filter.
help_ranked <- bind_rows(
  filter(help_window, date > data_through - 7L) |> mutate(window = "7"),
  filter(help_window, date > data_through - long_window_days) |>
    mutate(window = as.character(long_window_days))
) |>
  filter(!is.na(lang)) |>
  group_by(window, lang, path, title) |>
  summarise(title_views = sum(views), .groups = "drop_last") |>
  # A page is a path, labelled with the title it was viewed under most often:
  # a reader whose browser translates the page reports a translated title.
  mutate(views = sum(title_views)) |>
  slice_max(title_views, n = 1, with_ties = FALSE) |>
  group_by(window, lang) |>
  arrange(desc(views), .by_group = TRUE) |>
  slice_head(n = help_top_n) |>
  ungroup() |>
  mutate(
    # The two languages are served from their own domains.
    page = paste0(
      '<a href="',
      ifelse(lang == "fr", "https://connexion.canada.ca",
             "https://login.canada.ca"),
      path, '" target="_blank" rel="noopener">',
      htmltools::htmlEscape(title), "</a>"
    )
  )

help_7d <- filter(help_window, date > data_through - 7L)
help_long <- filter(help_window, date > data_through - long_window_days)

# Language share over the long window. Scanner traffic has no language, so it
# is out of the denominator.
help_split <- help_long |>
  filter(!is.na(lang)) |>
  count(lang, wt = views, name = "views") |>
  mutate(share = round(100 * views / sum(views)))

# One token, no spaces, or Quarto renders it at body size.
help_split_label <- paste0(help_split$share[help_split$lang == "fr"], "%")
```

## Row {height="420px"}

### Column {width="24%"}

::: {.valuebox color="primary"}
Views, last 7 days

`r format(sum(help_7d$views), big.mark = ",")`
:::

::: {.valuebox color="secondary"}
Views, last `r long_window_days` days

`r format(sum(help_long$views), big.mark = ",")`
:::

::: {.valuebox color="info"}
French share, last `r long_window_days` days

`r help_split_label`
:::

### Column {width="76%"}

```{r help-site-chart}
#| title: "Help site page views over time"
#| fig-width: 7.7
#| fig-height: 3.6
#| fig-alt: |
#|   Chart of daily page views on the CanadaLogin help site over the last twelve
#|   weeks. A blue line traces total views per day across every help page, with
#|   a regular dip each weekend.

p <- help_window |>
  group_by(date) |>
  summarise(views = sum(views), .groups = "drop") |>
  ggplot(aes(date, views)) +
  geom_line(colour = colors$brand[["blue"]], linewidth = 0.8) +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.05))) +
  scale_x_date(date_labels = "%b %d") +
  theme_cds() +
  labs(
    x = NULL, y = "Page views",
    title = "Help site page views",
    # Wrapped by hand: a single-line subtitle runs under the logo.
    subtitle = "Daily views across every page of the CanadaLogin help stream."
  )

add_cds_logo(add_watermark(p, date = data_through), height = 0.09)
```

## Row

### Column {width="50%"}

::: {.card title="English pages, last 7 days"}

```{r help-table-en-7d}
help_ranked |>
  filter(window == "7", lang == "en") |>
  select(page, views) |>
  gt() |>
  fmt_markdown(page) |>
  fmt_number(views, decimals = 0) |>
  cols_label(page = "Page", views = "Views") |>
  tab_options(table.width = pct(100), table.font.size = px(13),
              data_row.padding = px(3), table.border.top.style = "none")
```

:::

::: {.card title="French pages, last 7 days"}

```{r help-table-fr-7d}
help_ranked |>
  filter(window == "7", lang == "fr") |>
  select(page, views) |>
  gt() |>
  fmt_markdown(page) |>
  fmt_number(views, decimals = 0) |>
  cols_label(page = "Page", views = "Views") |>
  tab_options(table.width = pct(100), table.font.size = px(13),
              data_row.padding = px(3), table.border.top.style = "none")
```

:::

### Column {width="50%"}

::: {.card title="English pages, last `r long_window_days` days"}

```{r help-table-en-long}
help_ranked |>
  filter(window == as.character(long_window_days), lang == "en") |>
  select(page, views) |>
  gt() |>
  fmt_markdown(page) |>
  fmt_number(views, decimals = 0) |>
  cols_label(page = "Page", views = "Views") |>
  tab_options(table.width = pct(100), table.font.size = px(13),
              data_row.padding = px(3), table.border.top.style = "none")
```

:::

::: {.card title="French pages, last `r long_window_days` days"}

```{r help-table-fr-long}
help_ranked |>
  filter(window == as.character(long_window_days), lang == "fr") |>
  select(page, views) |>
  gt() |>
  fmt_markdown(page) |>
  fmt_number(views, decimals = 0) |>
  cols_label(page = "Page", views = "Views") |>
  tab_options(table.width = pct(100), table.font.size = px(13),
              data_row.padding = px(3), table.border.top.style = "none")
```

:::

```{r cleanup}
#| include: false
# include: false is layout, not tidiness: this chunk sits in the last Row, and
# anything visible there becomes a card and takes width from the table.
DBI::dbDisconnect(con)
```

{{< include _analytics.qmd >}}
