---
title: "CanadaLogin Task Success Monitoring"
author: "EDCP Data and Research Team"  # colin.douglas@cds-snc.ca
format:
  dashboard:
    orientation: rows
    embed-resources: true
    scrolling: true
    theme: [cosmo, _fonts.scss]   # _fonts.scss: self-hosted brand fonts
    css: styles.css
    # Written by the setup chunk at render time; empty unless a check failed.
    include-before-body: preflight-banner.html
    # Written by the analytics chunk at render time; see _analytics.qmd.
    include-after-body: analytics-tag.html
brand: _brand.yml
params:
  ga_page_title: "Task Success Monitoring Dashboard"
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
source("R/connection.R")
source("R/registry.R")
source("R/metrics.R")
source("R/preflight.R")
source("R/branding.R")
source("R/colours.R")

suppressPackageStartupMessages({
  library(DBI)
  library(RAthena)
  library(dplyr)
  library(dbplyr)
  library(tidyr)
  library(glue)
  library(purrr)
  library(ggplot2)
  library(scales)
  library(gt)
})

con <- connect_athena()

# A failed check banners the dashboard rather than stopping the render, so the
# banner is what stands between a holed number and a publish. See R/preflight.R.
ga_lag <- 2L
preflight <- run_preflight_safety_check(
  con, today = Sys.Date(), ga_export_lag_days = ga_lag
)
write_preflight_banner(preflight)
write_preflight_status(preflight)

today <- Sys.Date()
as_of <- today - ga_lag        # GA's ~2-day processing lag; newest day expected

# The newest complete 7-day window across the required funnels.
data_through <- tbl(
  con, in_schema("google_analytics", "funnel_metrics_current")
) |>
  filter(
    metric_id == "task_success",
    funnel_id %in% !!required_funnels,
    window_days == "7",
    breakdown_value == "RESERVED_TOTAL",
    !window_incomplete
  ) |>
  summarise(m = max(window_end)) |>
  pull(m) |>
  as.Date()

series_start   <- as.Date("2000-01-01")          # early bound; pulls all history
trailing_start <- data_through - (7L * 12L)       # ~12-week working window

# "August 8", not "August 08": the integer day avoids zero-padding.
format_long_date <- function(d) {
  d <- as.Date(d)
  paste0(format(d, "%B"), " ", as.integer(format(d, "%d")), ", ", format(d, "%Y"))
}
data_through_label <- format_long_date(data_through)

# Whole-number percent, or "n/a" for an undefined rate.
fmt_pct <- function(x) ifelse(is.na(x), "n/a", paste0(round(x * 100), "%"))

# Page label and caveat prose. Step labels are not here: see step_labels.
funnel_meta <- list(
  sign_in = list(
    label = "Sign in",
    caveat = paste(
      "This rate stops at MFA selection, the last step Google Analytics can see",
      "before the off-site redirect to IBM Verify. It is not a true completion",
      "rate, and it is not comparable to sign up."
    )
  ),
  sign_up = list(
    label = "Sign up",
    caveat = paste(
      "Sign up's exit is the account-creation confirmation page, a real",
      "first-party event, so this is a true completion rate."
    )
  )
)

# Two pooled rows. Internal services are not listed individually, and GA's ""
# and "(not set)" mean the same thing. Both sort to the bottom of the table.
internal_rp_label <- "Internal apps"
unrecorded_rp_label <- "Relying party not recorded"
pooled_rp_labels <- c(internal_rp_label, unrecorded_rp_label)

# GA's rp_name is an alias, so this resolves it to the service name the lookup
# gives, which pools a service that GA knows by more than one name into one row.
#
# replace(), not ifelse(): ifelse() on an empty frame returns logical(0), which
# clashes on type the moment an empty period is joined to a full one.
rp_display_name <- function(rp_name) {
  service <- label_relying_parties(con, rp_name)$service_name
  out <- coalesce(service, rp_name)
  out <- replace(out, rp_name %in% ga_excluded_rp_names, unrecorded_rp_label)
  replace(out, is_internal_rp(con, rp_name), internal_rp_label)
}

# Read once per funnel, then used for the value box titles and table headings.
step_labels <- lapply(required_funnels, \(f) funnel_step_names(con, f))
names(step_labels) <- required_funnels

# Single quotes: a double quote in a value box title comes back escaped and
# truncates it. The names are slugs, so underscores are opened up.
format_step_name <- function(step) {
  if (is.na(step)) "unknown step" else paste0("'", gsub("_", " ", step), "'")
}

exit_step_label <- function(funnel_id) {
  format_step_name(step_labels[[funnel_id]]$exit_step)
}

# 7-day rate over the daily rate, GA's total, over the full GA history.
make_funnel_chart <- function(funnel_id, funnel_label) {
  s7 <- task_success_series(con, funnel_id, "7", series_start, data_through)
  s1 <- task_success_series(con, funnel_id, "1", series_start, data_through)

  p <- ggplot() +
    geom_point(
      data = s1, aes(window_end, value),
      colour = "grey70", size = 0.7, alpha = 0.6
    ) +
    # Grouped by version so the line BREAKS where the definition changes.
    geom_line(
      data = s7, aes(window_end, value, group = funnel_version),
      colour = colors$brand[["blue"]], linewidth = 1
    ) +
    scale_y_continuous(
      labels = label_percent(accuracy = 1), limits = c(0, 1),
      expand = expansion(mult = c(0, 0.05))
    ) +
    scale_x_date(date_labels = "%b %d") +
    theme_cds() +
    labs(
      x = NULL, y = "Task success rate",
      # Wrapped by hand: a single-line subtitle runs under the logo.
      title = glue("Task Success: {funnel_label}"),
      subtitle = paste(
        "7-day rolling rate (blue line) over the daily rate (grey points).",
        "All relying parties, as reported by Google Analytics.",
        sep = "\n"
      )
    )

  # The logo is a fraction of figure height, so a small figure needs a smaller one.
  add_cds_logo(add_watermark(p, date = data_through), height = 0.09)
}

# A funnel younger than 60 days returns a short preceding period rather than
# nothing, and a month against six days would read as a swing in the rate.
prior_period_complete <- function(funnel_id) {
  prior <- task_success_30d(con, funnel_id, data_through - 30L)
  nrow(prior) > 0 && prior$days >= 30
}

# Direction is carried by the arrow and the sign, not colour alone; an
# uncalculable change is a dash, not a zero. gt colours it, see build_rp_table().
fmt_delta <- function(delta) {
  case_when(
    is.na(delta) ~ "-",
    delta > 0.0005 ~ sprintf("\u25b2 %+.1f pts", delta * 100),
    delta < -0.0005 ~ sprintf("\u25bc %+.1f pts", delta * 100),
    .default = "no change"
  )
}

# Change colours: forest rather than brand green, too light to pass contrast.
delta_colours <- c(up = "#115740", down = "#AB2328", flat = "#5C6670")

# Latest 7-day rate, the 30-day rate and its change, and the counts it divides.
# The top row is GA's total, and the rows below it partition it.
build_rp_table <- function(funnel_id) {
  exit_label <- exit_step_label(funnel_id)
  compare <- prior_period_complete(funnel_id)

  latest_7d <- party_step_counts(
    con, funnel_id, "7", trailing_start, data_through
  ) |>
    group_by(breakdown_value) |>
    slice_max(window_end, n = 1, with_ties = FALSE) |>
    ungroup() |>
    mutate(rp = rp_display_name(breakdown_value)) |>
    as_task_success(rp) |>
    select(rp, rate_7d = value)

  # Both periods come through the 30-day seam. They never share a day.
  by_rp_30d <- function(as_of) {
    task_success_30d(con, funnel_id, as_of, breakdown_value,
                     counts = party_step_counts) |>
      mutate(rp = rp_display_name(breakdown_value)) |>
      as_task_success(rp)
  }

  counts_30d <- by_rp_30d(data_through) |>
    select(rp, rate_30d = value, entered = denominator, finished = numerator)
  prior_30d <- by_rp_30d(data_through - 30L) |>
    select(rp, prior_30d = value)

  merged <- reduce(list(latest_7d, counts_30d, prior_30d), full_join, by = "rp")

  # rp is already the service name, so the operator is looked up by that. The
  # two pooled rows are not services and come back empty.
  per_rp <- merged |>
    mutate(Operator = coalesce(service_operators(con, merged$rp), "")) |>
    transmute(
      Service = rp, Operator,
      rate_7d, rate_30d, prior_30d, entered, finished
    ) |>
    # Busiest first, with the two pooled rows held at the end.
    arrange(Service %in% pooled_rp_labels, desc(entered))

  overall <- task_success_30d(con, funnel_id, data_through) |>
    transmute(
      Service = "All relying parties (Google Analytics total)",
      Operator = "",
      rate_7d = task_success_latest(
        con, funnel_id, "7", trailing_start, data_through
      )$value,
      rate_30d = value,
      prior_30d = task_success_30d(con, funnel_id, data_through - 30L)$value,
      entered = denominator, finished = numerator
    )

  rows <- bind_rows(overall, per_rp) |>
    # The column stays even with nothing to compare against; every row reads as
    # a dash and comparison_note() says why.
    mutate(delta = if (compare) rate_30d - prior_30d else NA_real_) |>
    transmute(
      Service, Operator, rate_7d, rate_30d,
      change = fmt_delta(delta), entered, finished, delta
    )

  gt(rows) |>
    cols_hide(delta) |>
    fmt_percent(c(rate_7d, rate_30d), decimals = 0) |>
    fmt_number(c(entered, finished), decimals = 0) |>
    sub_missing(missing_text = "n/a") |>
    cols_label(
      rate_7d = "7-day rate",
      rate_30d = "30-day rate",
      change = "vs previous 30 days",
      entered = html("Started<br>(30 days)"),
      finished = html(glue("Reached {exit_label}<br>(30 days)"))
    ) |>
    tab_style(cell_text(weight = "bold"), cells_body(rows = 1)) |>
    tab_style(
      cell_text(color = delta_colours[["up"]]),
      cells_body(columns = change, rows = !is.na(delta) & delta > 0.0005)
    ) |>
    tab_style(
      cell_text(color = delta_colours[["down"]]),
      cells_body(columns = change, rows = !is.na(delta) & delta < -0.0005)
    ) |>
    tab_style(
      cell_text(color = delta_colours[["flat"]]),
      cells_body(columns = change, rows = is.na(delta) | abs(delta) <= 0.0005)
    ) |>
    tab_options(
      table.width = pct(100),
      table.font.size = px(14),
      data_row.padding = px(4),
      table.border.top.style = "none"
    )
}

# Shown wherever the 30-day figures appear, until window_days "30" lands.
proxy_note <- if (task_success_30d_is_proxy) {
  paste(
    "The 30-day figures are an interim approximation, summed from the 30",
    "trailing daily windows pending a stored 30-day window. Google Analytics",
    "counts each user once per day, so someone who came back on several days is",
    "counted several times in the two count columns."
  )
} else {
  NULL
}

# Makes a column of dashes read as "too early" rather than as broken.
comparison_note <- function(funnel_id) {
  if (prior_period_complete(funnel_id)) {
    return(NULL)
  }
  paste(
    "The change against the previous 30 days cannot be calculated yet: this",
    "funnel does not have 60 days of history, and comparing a full month against",
    "a part of one would read as a swing in the rate."
  )
}

# Shown under every table and chart: the exclusion changes what the numbers mean.
internal_note <- paste(
  "The headline figures, the chart and the top row are Google Analytics'",
  "own total across every relying party. Internal services such as Manage",
  "CanadaLogin are pooled into one row rather than listed, so the rows below",
  "still add up to the top one. Service names and operators come from the",
  "shared relying-party tables in the data lake, which also combine a service",
  "that Google Analytics knows by more than one name into a single row."
)
```

# Overview

## Row {height="120px"}

```{r}
#| content: valuebox
#| title: "Data through"
list(
  icon = "calendar-event",
  color = "primary",
  value = data_through_label
)
```

## Row

::: {.card title="About this dashboard"}

This is an internal working instrument for the EDCP Data and Research Team. It
watches CanadaLogin task success rates between report cycles so analysts get the
numbers in one place without digging through Google Analytics.

It is not the source of truth. The canonical task success numbers live in the
monthly task success report, a written Google doc; this dashboard feeds that
report and should not be quoted as authoritative. It is internal only, not for
partners, executives, or the public.

Task success is the share of users who start a flow and reach its defined
finishing point, measured from Google Analytics 4 funnel data. Google Analytics
runs on a deliberate two-day processing lag, so the data ends a couple of days
before today; the "Data through" date says how current it is.

`r internal_note`

`r if (!is.null(proxy_note)) proxy_note`

:::

# Sign in

## Row {height="420px"}

### Column {width="24%"}

::: {.valuebox color="primary"}
Latest 7-day rate\
(reaches `r exit_step_label("sign_in")` step)

`r fmt_pct(task_success_latest(con, "sign_in", "7", trailing_start, data_through)$value)`
:::

::: {.valuebox color="secondary"}
30-day rate\
(interim proxy)

`r fmt_pct(task_success_30d(con, "sign_in", data_through)$value)`
:::

### Column {width="76%"}

```{r}
#| title: "Task success rate over time"
#| fig-width: 7.7
#| fig-height: 3.6
#| fig-alt: |
#|   Chart of the sign-in task success rate over time, external relying parties
#|   only. A bold blue line traces the 7-day rolling rate, breaking wherever the
#|   funnel version changes; faint grey points underneath are the noisier daily
#|   rate. The y-axis runs from zero to one hundred percent.
make_funnel_chart("sign_in", funnel_meta$sign_in$label)
```

## Row

::: {.card title="By relying party (latest values)"}

```{r}
build_rp_table("sign_in")
```

::: {.figure-note}
**Caveat.** `r funnel_meta$sign_in$caveat`

`r comparison_note("sign_in")`

`r internal_note`

`r if (!is.null(proxy_note)) proxy_note`
:::

:::

# Sign up

## Row {height="420px"}

### Column {width="24%"}

::: {.valuebox color="primary"}
Latest 7-day rate\
(reaches `r exit_step_label("sign_up")` step)

`r fmt_pct(task_success_latest(con, "sign_up", "7", trailing_start, data_through)$value)`
:::

::: {.valuebox color="secondary"}
30-day rate\
(interim proxy)

`r fmt_pct(task_success_30d(con, "sign_up", data_through)$value)`
:::

### Column {width="76%"}

```{r}
#| title: "Task success rate over time"
#| fig-width: 7.7
#| fig-height: 3.6
#| fig-alt: |
#|   Chart of the sign-up task success rate over time, external relying parties
#|   only. A bold blue line traces the 7-day rolling rate, breaking wherever the
#|   funnel version changes; faint grey points underneath are the noisier daily
#|   rate. The y-axis runs from zero to one hundred percent.
make_funnel_chart("sign_up", funnel_meta$sign_up$label)
```

## Row

::: {.card title="By relying party (latest values)"}

```{r}
build_rp_table("sign_up")
```

::: {.figure-note}
**Note.** `r funnel_meta$sign_up$caveat`

`r comparison_note("sign_up")`

`r internal_note`

`r if (!is.null(proxy_note)) proxy_note`
:::

:::

```{r cleanup}
#| include: false
# include: false is layout, not tidiness: this chunk sits in the last Row, and
# anything visible there becomes a card and takes width from the table.
DBI::dbDisconnect(con)
```

{{< include _analytics.qmd >}}
