---
title: "CanadaLogin Sign-In Activity"
author: "EDCP Data and Research Team"  # colin.douglas@cds-snc.ca
slug: ibmverify
format:
  dashboard:
    # Written by the setup chunk at render time
    include-before-body: page-header.html
    include-after-body: analytics-tag.html # see _analytics.qmd
params:
  ga_page_title: "Sign-In Activity Dashboard"
---

```{r setup}
# The working directory is this folder; the shared layer is two levels up.
source("../../common/setup.R")

source("R/metrics.R")
source("R/preflight.R")

library(ggbrick)
library(reactable)
library(htmltools)

con <- connect_athena()

# This dashboard's accent, same as the primary CDS brand color
accent <- "#004986"

# A failed check adds a banner. See R/preflight.R.
preflight <- run_preflight_safety_check(con, today = Sys.Date())
write_preflight_status(preflight)

# Anchored on the newest day every table covers
data_through <- ibm_verify_data_through(con)

month_start <- as.Date(format(data_through, "%Y-%m-01"))

# How far back every chart runs
chart_months <- 3L

# Trailing span for the charts that run on days and weeks.
chart_start <- seq(data_through, by = glue("-{chart_months} months"),
                   length.out = 2)[2]

# chart_months whole calendar months plus the one in progress
mau_start <- seq(month_start, by = glue("-{chart_months} months"),
                 length.out = 2)[2]

# "Aug 8"
format_short_date <- function(d) {
  d <- as.Date(d)
  paste0(format(d, "%b"), " ", as.integer(format(d, "%d")))
}

# "August 8", not "August 08".
data_through_label <- paste0(
  format(data_through, "%B"), " ", as.integer(format(data_through, "%d")),
  ", ", format(data_through, "%Y")
)

# "August", for the value box and column naming the month-to-date figure.
month_label <- format(data_through, "%B")

# Rolling windows for comparison, calendar months for the record.
window_label <- glue("rolling {summary_window_days} days")
prior_window_label <- glue("vs previous {summary_window_days} days")

page_header <- "page-header.html"

write_preflight_banner(preflight, page_header)

cat(
  c(
    '<div class="page-strip">',
    glue('  <p><strong>Data through {data_through_label}.</strong> ',
         "Internal to Enterprise Digital Credentials, not for public ",
         "consumption.</p>"),
    "</div>"
  ),
  file = page_header, sep = "\n", append = TRUE
)

brand_figure <- function(p) {
  add_cds_logo(
    add_watermark(p, report_name = "CanadaLogin Sign-In Activity",
                  date = data_through),
    height = 0.09
  )
}

# Presentation ---------------------------------------------------------------

unit_colours <- c(
  accent,
  colors$brand[c("orange", "forest", "green", "yellow", "sky", "red")]
)

# Colours for the MFA table, from the CDS brand guide
mfa_colours <- c(
  "SMS OTP"            = colors$brand[["blue"]],
  "Passkey (FIDO2)"    = colors$brand[["orange"]],
  "Voice OTP"          = colors$brand[["forest"]],
  "Email OTP"          = colors$brand[["green"]],
  "TOTP"               = colors$brand[["yellow"]],
  "Knowledge question" = colors$brand[["sky"]],
  "QR code"            = colors$brand[["grey"]],
  "IBM Verify push"    = colors$brand[["red"]]
)

# scale_*_manual errors on a level it has no colour for, so a factor nobody
# has added here falls back to mid grey.
palette_for <- function(levels) {
  out <- unname(mfa_colours[levels])
  out[is.na(out)] <- "#5C6670"
  setNames(out, levels)
}

mau_chart_subtitle <- glue(
  "Top, distinct users who have signed in so far this calendar month. ",
  "Bottom, distinct users each day."
)

mau_chart_alt <- glue(
  "Two charts on a shared date axis. Above, monthly active users, increasing over the",
  "course of the month. Below, active users each day as a single line, dropping",
  "on the weekends."
)

# Drawn only where the launch falls inside the charted span: off-chart it pins
# to the panel edge and reads as a launch at the start of the window.
launch_layers <- function(launched, size = 2.7, label_y = Inf) {
  if (is.na(launched) || launched < chart_start) {
    return(NULL)
  }
  list(
    geom_vline(xintercept = launched, linetype = "dashed",
               colour = "grey45", linewidth = 0.4),
    annotate("text", x = launched, y = label_y,
             label = glue(" Launched {format_short_date(launched)}"),
             hjust = 0, vjust = 1.4, size = size, colour = "grey35")
  )
}

# A weekly bar spans Monday to Sunday and its tick sits at the end of that
# span, so the bar is left of the tick naming it. Move the two together.
week_offset <- 3.5
week_tick_offset <- 7L

week_axis <- function(weeks, limits = NULL, max_labels = 14L) {
  weeks <- sort(unique(weeks))
  # Every other week past max_labels, counted back so the newest keeps its.
  step <- if (length(weeks) > max_labels) 2L else 1L
  labelled <- rev(weeks[seq(length(weeks), 1L, by = -step)])
  scale_x_date(
    breaks = labelled + week_tick_offset,
    labels = format(labelled + 6L, "%b %d"),
    limits = limits
  )
}

# Goes with week_axis(), which labels a bar with the last day it covers.
week_axis_title <- "Week ending"

```

# Overall

```{r overall-summary}
#| include: false
daily_users_now <- average_daily_users(auth_totals(con), data_through)
daily_users_prior <- average_daily_users(auth_totals(con),
                                         data_through - summary_window_days)
daily_users_delta <- fmt_delta(relative_change(daily_users_now,
                                               daily_users_prior))

# The same day of the previous month, so a month 30 days in is compared with
# one 30 days in. Handles comparisons of months with different lengths
previous_month_end <- month_start - 1L
comparison_day <- min(
  as.Date(format(previous_month_end, "%Y-%m-01")) +
    (as.integer(format(data_through, "%d")) - 1L),
  previous_month_end
)

mtd_now <- latest_value(auth_totals(con), "mtd_unique_users")
mtd_prior <- auth_totals(con) |>
  filter(date == comparison_day) |>
  pull(mtd_unique_users)

rolling_line <- "Approximate, for now"

# Nothing to compare against in the first month of the data.
mtd_line <- if (length(mtd_prior) == 0) {
  "No comparable day last month"
} else {
  glue("{fmt_delta(relative_change(mtd_now, mtd_prior))} vs this time last month")
}
```

## Row {height="150px"}

::: {.valuebox color="primary"}
Average daily users (`r window_label`)

`r format(round(daily_users_now), big.mark = ",")`

`r daily_users_delta` `r prior_window_label`
:::

::: {.valuebox color="info"}
Active users in `r month_label` (to date)

`r format(mtd_now, big.mark = ",")`

`r mtd_line`
:::

::: {.valuebox color="secondary"}
Active users, last 365 days

`r format(latest_value(auth_totals(con), "rolling_365d_unique_users"), big.mark = ",")`

`r rolling_line`
:::

## Row {height="560px"}

::: {.card title="`r glue('Active users by month and by day (last {chart_months} months)')`"}

```{r overall-chart}
#| fig-width: 13
#| fig-height: 4.6
#| fig-alt: !expr mau_chart_alt

mau <- auth_totals(con) |>
  filter(date >= mau_start) |>
  mutate(month = format(date, "%Y-%m"))

# Each month's total, to label where its line ends.
month_ends <- mau |>
  group_by(month) |>
  slice_max(date, n = 1, with_ties = FALSE) |>
  ungroup()

month_starts <- unique(as.Date(paste0(mau$month, "-01")))
next_month <- seq(month_start, by = "1 month", length.out = 2)[2]
month_breaks <- c(month_starts[month_starts > min(mau$date)], next_month)

# Shared, a month lines up in both panels.
axis_limits <- c(mau_start, next_month + 4L)

month_axis <- scale_x_date(
  labels = \(d) format(d, "%B"), breaks = month_starts,
  limits = axis_limits
)

# The axis below is labelled by week, so each month names itself in place.
month_names <- tibble(
  start = month_starts,
  label = ifelse(month_starts == month_start,
                 paste0(format(month_starts, "%B"), " (in progress)"),
                 format(month_starts, "%B"))
)

users_panel <- ggplot(mau, aes(date, mtd_unique_users, group = month)) +
  geom_vline(xintercept = month_breaks, colour = "grey75", linewidth = 0.4,
             linetype = "dashed") +
  annotate("text", x = month_names$start, y = Inf, label = month_names$label,
           hjust = -0.1, vjust = 1.4, size = 3.1, colour = "grey35") +
  geom_line(colour = accent, linewidth = 0.9) +
  # Above the last point, so the total stays inside its own month's band.
  geom_text(data = month_ends, aes(label = label_comma()(mtd_unique_users)),
            hjust = 1, vjust = -0.8, size = 3.1, colour = accent,
            fontface = "bold") +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.12))) +
  month_axis +
  theme_cds() +
  # The x-axis belongs to the panel below, so this one's is blank.
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(
    # No title: the card above the figure already carries it.
    x = NULL, y = "Active users this month",
    subtitle = mau_chart_subtitle
  )

# Daily reach under monthly reach, off the same rows as the panel above.
daily_panel <- ggplot(mau, aes(date, unique_users)) +
  geom_vline(xintercept = month_breaks, colour = "grey75", linewidth = 0.4,
             linetype = "dashed") +
  geom_line(colour = accent, linewidth = 0.7) +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.05))) +
  scale_x_date(breaks = rev(seq(data_through, mau_start, by = "-2 weeks")),
               date_labels = "%b %d", limits = axis_limits) +
  theme_cds() +
  labs(x = NULL, y = "Active users each day")

# align = "v" with axis = "lr" so the two plotting areas line up despite
# different y-axis label widths.
p <- cowplot::plot_grid(
  users_panel, daily_panel,
  ncol = 1, align = "v", axis = "lr", rel_heights = c(1.4, 1)
)

brand_figure(p)
```

:::

## Row

::: {.card title="By calendar month" width="40%"}

```{r overall-monthly}
monthly_auth_totals(auth_totals(con), data_through) |>
  # The month still filling up says so.
  mutate(month = ifelse(month == month_start,
                        paste0(format(month, "%B %Y"), " (to date)"),
                        format(month, "%B %Y"))) |>
  gt() |>
  fmt_number(c(authentications, users), decimals = 0) |>
  cols_label(
    month = "Month",
    authentications = "Authentications",
    users = "Active users"
  ) |>
  tab_options(
    table.width = pct(100),
    table.font.size = px(14),
    data_row.padding = px(4),
    table.border.top.style = "none"
  )
```

:::

::: {.card title="Active users by calendar month" width="60%"}

```{r overall-monthly-chart}
#| fig-width: 8
#| fig-height: 3.4
#| fig-alt: |
#|   Bar chart of active users in each calendar month, one bar per month, with
#|   the current month drawn faded because it is still filling up.

# Twelve months where there are twelve
monthly_users <- monthly_auth_totals(auth_totals(con), data_through) |>
  arrange(month) |>
  tail(12) |>
  mutate(in_progress = month == month_start)

# Fade the incomplete month
p <- ggplot(monthly_users, aes(month, users)) +
  geom_col(aes(alpha = in_progress), fill = accent, width = 25) +
  scale_alpha_manual(values = c("FALSE" = 1, "TRUE" = 0.4), guide = "none") +
  scale_x_date(breaks = monthly_users$month, date_labels = "%b %Y") +
  scale_y_continuous(labels = label_comma(), breaks = pretty_breaks(4),
                     expand = expansion(mult = c(0, 0.08))) +
  theme_cds() +
  theme(panel.grid.major.x = element_blank()) +
  labs(x = NULL, y = NULL)

brand_figure(p)
```

:::

# Services

```{r rp-data}
#| include: false

rp_services <- external_services(con)

# The parenthetical on its own line
stacked_header <- function(label, note) {
  htmltools::div(label, htmltools::br(), paste0("(", note, ")"))
}

# reactable, use the brand colors
rp_theme <- reactableTheme(
  borderColor = "#dfe2e5",
  highlightColor = "#f5f7f9",
  cellPadding = "6px 8px",
  style = list(fontSize = "14px"),
  headerStyle = list(fontWeight = 600, color = "#5C6670")
)

# Weekly sign-ins per unit, feedis both the detail chart and the sparkline
service_weekly <- function(key) {
  service_daily(con, key) |>
    mutate(week = as.Date(cut(date, "week"))) |>
    count(week, unit, wt = total_logins, name = "sign_ins") |>
    filter(week >= chart_start, week + 6L <= data_through)
}

# One row per service: the summary columns, a sparkline, and the expandable detail
rp_rows <- lapply(rp_services, function(key) {
  daily <- service_daily(con, key)
  units <- service_units(daily)
  window_rows <- in_window(daily, data_through)
  prior_rows <- in_window(daily, data_through - summary_window_days)

  sign_ins <- sum(window_rows$total_logins)
  prior <- sum(prior_rows$total_logins)

  tibble(
    service = key,
    operator = coalesce(service_operators(con, key), ""),
    launched = service_launch(daily),
    applications = length(units),
    sign_ins = sign_ins,
    prior_sign_ins = prior,
    change_value = relative_change(sign_ins, prior),
    mtd = sum(latest_per_unit(daily, month_start, data_through)$mtd_unique_users),
    rolling = sum(
      latest_per_unit(daily, ibm_verify_launch, data_through)$rolling_365d_unique_users
    )
  )
}) |>
  bind_rows() |>
  mutate(
    launched = format(launched, "%Y-%m-%d"),
    change = fmt_delta(change_value),
    direction = delta_direction(change_value)
  )

# Total weekly sign-ins as a data URI, sized to sit inside a table row
rp_sparkline <- function(key) {
  weekly <- service_weekly(key) |>
    count(week, wt = sign_ins, name = "sign_ins")
  if (nrow(weekly) < 2) {
    return('<span style="color:#5C6670">-</span>')
  }
  as.character(plotTag(
    print(
      ggplot(weekly, aes(week, sign_ins)) +
        geom_area(fill = accent, alpha = 0.15) +
        geom_line(colour = accent, linewidth = 0.7) +
        scale_y_continuous(limits = c(0, NA), expand = expansion(0)) +
        theme_void()
    ),
    alt = "", width = 150, height = 30,
    device = ragg::agg_png, deviceArgs = list(background = "transparent")
  ))
}

# The expanded row: the weekly stack beside the calendar months
rp_detail <- function(key) {
  daily <- service_daily(con, key)
  units <- service_units(daily)
  weekly <- service_weekly(key) |>
    mutate(unit = factor(unit, levels = units))
  launched <- service_launch(daily)

  # Grey past the end of unit_colours, since scale_fill_manual() errors on a
  # level with no corresponding color
  palette <- rep("#5C6670", length(units))
  taken <- seq_len(min(length(units), length(unit_colours)))
  palette[taken] <- unit_colours[taken]
  palette <- setNames(palette, units)

  # plotTag renders at 72 dpi, so width is inches times 72 and base_size sizes
  # text against that. suppressSize drops the img dimensions to fill the row.
  chart <- plotTag(
    print(
      ggplot(weekly, aes(week + week_offset, sign_ins, fill = unit)) +
        geom_col(width = 7, colour = "white", linewidth = 0.25) +
        launch_layers(launched, size = 3.9) +
        scale_fill_manual(values = palette) +
        scale_y_continuous(labels = label_comma(),
                           expand = expansion(mult = c(0, 0.08))) +
        week_axis(weekly$week) +
        theme_cds(base_size = 15) +
        theme(legend.position = "top", legend.justification = "left",
              legend.margin = margin(0, 0, 0, 0)) +
        labs(x = week_axis_title, y = "Sign-ins", fill = NULL)
    ),
    alt = glue(
      "Stacked bar chart of weekly sign-ins to {key} over the last ",
      "{chart_months} months, split by application."
    ),
    width = 820, height = 340, pixelratio = 2,
    suppressSize = "xy",
    attribs = list(style = "width:100%;height:auto"),
    device = ragg::agg_png, deviceArgs = list(background = "white")
  )

  total_or_na <- function(x) if (all(is.na(x))) NA_real_ else sum(x, na.rm = TRUE)

  monthly <- monthly_unit_sign_ins(daily, data_through) |>
    group_by(month) |>
    summarise(sign_ins = total_or_na(sign_ins), .groups = "drop") |>
    left_join(
      monthly_unit_users(daily, data_through) |>
        group_by(month) |>
        summarise(users = total_or_na(users), .groups = "drop"),
      by = "month"
    ) |>
    arrange(desc(month)) |>
    # The current month is still filling up, and says so on its own line.
    mutate(month = ifelse(
      month == month_start,
      paste0(format(month, "%B %Y"),
             '<br><span style="color:#5C6670;font-size:0.85em">(to date)</span>'),
      format(month, "%B %Y")
    ))

  month_columns <- list(
    sign_ins = colDef(name = "Sign-ins", format = colFormat(separators = TRUE),
                      na = "-"),
    users = colDef(name = "Active users",
                   format = colFormat(separators = TRUE), na = "-")
  )

  # We have to be a little hacky with CSS so we can get the table and the graph
  # side-by-side
  htmltools::div(
    class = "rp-detail",
    htmltools::div(
      class = "rp-detail-split",
      htmltools::div(
        class = "rp-detail-chart",
        htmltools::tags$p(
          class = "rp-detail-heading",
          glue("Weekly sign-ins, last {chart_months} months")
        ),
        chart
      ),
      htmltools::div(
        class = "rp-detail-table",
        htmltools::tags$p(
          class = "rp-detail-heading", "By calendar month"
        ),
        reactable(
          monthly,
          columns = c(
            list(month = colDef(name = "Month", minWidth = 130, html = TRUE)),
            month_columns
          ),
          compact = TRUE, borderless = TRUE, sortable = FALSE,
          defaultPageSize = 12, showPageSizeOptions = FALSE,
          theme = rp_theme
        )
      )
    ),
    htmltools::div(
      class = "figure-note",
      glue(
        "Whole calendar months, where everything above is a rolling window. ",
        "Active users are running totals, so that column cannot be added up, ",
        "and a dash is a month before the service existed, not a zero."
      )
    )
  )
}

rp_rows$trend <- vapply(rp_rows$service, rp_sparkline, character(1))
rp_details <- lapply(rp_rows$service, rp_detail)
```

```{r services-change}
#| include: false
# The sign carries the direction
services_change <- relative_change(sum(rp_rows$sign_ins),
                                   sum(rp_rows$prior_sign_ins))

# The base the percentage is measured against
services_prior_line <- glue(
  "{ifelse(services_change >= 0, 'Up', 'Down')} from ",
  "{format(sum(rp_rows$prior_sign_ins), big.mark = ',')} the window before"
)
```

## Row {height="150px"}

::: {.valuebox color="primary"}
Sign-ins (`r window_label`)

`r format(sum(rp_rows$sign_ins), big.mark = ",")`

External services only, one event per sign-in
:::

::: {.valuebox color="info"}
Sign-ins `r prior_window_label`

`r sprintf("%+.0f%%", services_change * 100)`

`r services_prior_line`
:::

::: {.valuebox color="secondary"}
External services

`r nrow(rp_rows)`

`r sum(rp_rows$applications)` applications between them
:::

## Row

::: {.card title="External services (click a row to expand it)"}

```{r rp-table}
reactable(
  select(rp_rows, service, launched, trend, sign_ins, change, mtd,
         rolling, operator, direction, applications, prior_sign_ins),
  searchable = TRUE,
  language = reactableLang(
    searchPlaceholder = "Service or department",
    searchLabel = "Search by service or department"
  ),
  defaultSorted = list(sign_ins = "desc"),
  defaultPageSize = 12,
  showPageSizeOptions = TRUE,
  pageSizeOptions = c(12, 25, 50),
  highlight = TRUE,
  borderless = TRUE,
  compact = TRUE,
  # Click anywhere on the row, not just the arrow.
  onClick = "expand",
  rowStyle = list(cursor = "pointer"),
  details = function(index) rp_details[[index]],
  theme = rp_theme,
  columns = list(
    service = colDef(
      name = "Service", minWidth = 210,
      # The operator rides under the name rather than taking a column of its
      # own, which keeps the numbers together on the right.
      cell = function(value, index) {
        htmltools::div(
          htmltools::div(style = "font-weight:600", value),
          htmltools::div(style = "font-size:0.85em;color:#5C6670",
                         rp_rows$operator[index])
        )
      }
    ),
    launched = colDef(
      name = "Launched", maxWidth = 110,
      cell = function(value) format_short_date(value)
    ),
    trend = colDef(
      name = glue("Trend ({chart_months} months)"),
      header = stacked_header("Trend", glue("{chart_months} months")),
      html = TRUE,
      sortable = FALSE, maxWidth = 170
    ),
    sign_ins = colDef(
      name = glue("Sign-ins ({window_label})"),
      header = stacked_header("Sign-ins", window_label),
      format = colFormat(separators = TRUE), maxWidth = 140
    ),
    change = colDef(
      name = prior_window_label, maxWidth = 140,
      style = function(value, index) {
        list(color = delta_colours[[rp_rows$direction[index]]])
      }
    ),
    mtd = colDef(name = glue("Active users ({month_label} to date)"),
                 header = stacked_header("Active users",
                                         glue("{month_label} to date")),
                 format = colFormat(separators = TRUE), maxWidth = 130),
    rolling = colDef(name = "Active users (365 days)",
                     header = stacked_header("Active users", "365 days"),
                     format = colFormat(separators = TRUE), maxWidth = 130),
    # Hidden, but searched: the operator is printed under the service name, so
    # searching "TBS" should find GC Digital Talent. reactable leaves hidden
    # columns out of the search box unless a column opts back in.
    operator = colDef(show = FALSE, searchable = TRUE),
    direction = colDef(show = FALSE),
    applications = colDef(show = FALSE),
    prior_sign_ins = colDef(show = FALSE)
  )
)
```

::: {.figure-note}
**Click a row** for its weekly chart and its calendar months. A *service* is one 
relying party, and the *applications* inside it are the names IBM Verify knows it by. 
One service can have several applications. CanadaLogin's own internal applications are 
left out, although they still count towards the CanadaLogin-wide figures on the front 
page.
:::

:::

# Second Factors

```{r mfa-data}
#| include: false
# One read, filtered to a factor list per figure

mfa_all <- mfa_successes(con)

# Weekly successful attempts per factor, part weeks dropped.
mfa_series <- function(types) {
  mfa_all |>
    filter(mfa_type %in% types) |>
    mutate(week = as.Date(cut(date, "week"))) |>
    count(week, factor_label, wt = count, name = "successes") |>
    filter(week >= chart_start, week + 6L <= data_through) |>
    mutate(factor_label = factor(factor_label, levels = mfa_label(types)))
}

# Each factor's share of successes over the window, as whole percentage points.
# The largest slice is nudged so the squares sum to exactly 100.
mfa_mix <- function(types) {
  mix <- mfa_all |>
    in_window(data_through) |>
    filter(mfa_type %in% types) |>
    group_by(mfa_type, factor_label) |>
    summarise(successes = sum(count), .groups = "drop") |>
    filter(successes > 0) |>
    mutate(share = successes / sum(successes), pct = round(share * 100)) |>
    arrange(desc(successes))
  largest <- which.max(mix$pct)
  mix$pct[largest] <- mix$pct[largest] + (100L - sum(mix$pct))
  mix
}

# A bare coloured arrow, for a column with a direction but no size, includes a label
# for screen readers.
arrow_html <- function(direction) {
  glyph <- c(up = "\u25b2", down = "\u25bc", flat = "")
  label <- c(up = "share up", down = "share down", flat = "")
  ifelse(
    direction == "flat", "",
    sprintf(' <span style="color:%s" role="img" aria-label="%s">%s</span>',
            delta_colours[direction], label[direction], glyph[direction])
  )
}

# Successes over the window against the one before it. Share moves on its own,
# so the count arrow and the share arrow can disagree.
mfa_table_rows <- function(types) {
  prior <- mfa_all |>
    in_window(data_through - summary_window_days) |>
    filter(mfa_type %in% types) |>
    group_by(mfa_type) |>
    summarise(prior_successes = sum(count), .groups = "drop") |>
    mutate(prior_share = prior_successes / sum(prior_successes))

  mfa_mix(types) |>
    left_join(prior, by = "mfa_type") |>
    mutate(
      prior_successes = coalesce(prior_successes, 0),
      change_value = relative_change(successes, prior_successes),
      change = fmt_delta(change_value),
      direction = delta_direction(change_value),
      share_direction = delta_direction(share - prior_share),
      share_text = paste0(percent(share, accuracy = 1),
                          arrow_html(share_direction))
    )
}

mfa_summary <- mfa_table_rows(sign_in_mfa_types)

mfa_total <- sum(mfa_summary$successes)

passkey_row <- filter(mfa_summary, mfa_type == "fido2")

# An attempt is a success or a failure. `sent` rows are not included
mfa_attempts <- mfa_activity(con) |>
  filter(mfa_type %in% sign_in_mfa_types, result %in% c("success", "failure"))

attempts_now <- sum(in_window(mfa_attempts, data_through)$count)
attempts_prior <- sum(
  in_window(mfa_attempts, data_through - summary_window_days)$count
)
attempts_delta <- fmt_delta(relative_change(attempts_now, attempts_prior))

mfa_failures <- attempts_now - mfa_total
mfa_success_rate <- mfa_total / attempts_now

# Points, not percent: 5% to 7% is a rise of two points, not 40%
passkey_share_shift <- if (nrow(passkey_row) == 0) {
  "No successful attempts this window"
} else {
  shift <- passkey_row$share - passkey_row$prior_share
  direction <- delta_direction(shift)
  if (direction == "flat") {
    glue("No change vs previous {summary_window_days} days")
  } else {
    points <- sprintf("%+.0f", shift * 100)
    glue("{c(up = '\u25b2', down = '\u25bc')[direction]} {points} ",
         "{ifelse(abs(round(shift * 100)) == 1, 'point', 'points')} vs ",
         "previous {summary_window_days} days")
  }
}

```

## Row {height="150px"}

::: {.valuebox color="primary"}
Second-factor attempts (`r window_label`)

`r format(attempts_now, big.mark = ",")`

`r attempts_delta` `r prior_window_label`
:::

::: {.valuebox color="info"}
Second-factor success rate (`r window_label`)

`r percent(mfa_success_rate, accuracy = 0.1)`

`r format(mfa_failures, big.mark = ",")` failed attempts at a passkey or OTP
:::

::: {.valuebox color="secondary"}
Passkey share of sign-in factors

`r percent(passkey_row$share, accuracy = 1)`

`r passkey_share_shift`
:::

## Row {height="520px"}

::: {.card title="`r glue('Successful sign-in factors over time (last {chart_months} months)')`" width="66%"}

```{r mfa-signin-chart}
#| fig-width: 8.6
#| fig-height: 4.1
#| fig-alt: |
#|   Stacked bar chart of successful multi-factor attempts per week over the last
#|   three months, one bar per week split by sign-in factor. Blue SMS OTP fills
#|   almost the whole of every bar, with thin bands of orange passkeys and green
#|   voice OTP on top.

rows <- mfa_series(sign_in_mfa_types)

p <- ggplot(rows, aes(week + week_offset, successes, fill = factor_label)) +
  geom_col(width = 7, colour = "white", linewidth = 0.25) +
  scale_fill_manual(values = palette_for(levels(rows$factor_label))) +
  scale_y_continuous(labels = label_comma(),
                     expand = expansion(mult = c(0, 0.05))) +
  week_axis(rows$week) +
  theme_cds() +
  # Legend on top and left, clear of the logo in the top-right corner.
  theme(legend.position = "top", legend.justification = "left",
        legend.margin = margin(0, 0, 0, 0)) +
  labs(x = week_axis_title, y = "Successful attempts", fill = NULL,
       subtitle = glue("Weekly successful second-factor attempts over the ",
                       "last {chart_months} months, for the factors the ",
                       "public can sign in with."))

brand_figure(p)
```

:::

::: {.card title="`r glue('Passkey uptake (last {chart_months} months)')`" width="34%"}

```{r mfa-passkey-chart}
#| fig-width: 5.0
#| fig-height: 4.3
#| fig-alt: |
#|   Line chart of passkeys as a share of successful sign-in factor attempts,
#|   one point per week over the last three months, rising from a low single
#|   digit percentage towards the high single digits.

# Passkeys are a few percent of the stack beside this, so a band a few pixels
# tall. Share over time is where a rise in them shows.
weekly <- mfa_series(sign_in_mfa_types) |>
  group_by(week) |>
  summarise(
    share = sum(successes[factor_label == mfa_label("fido2")]) / sum(successes),
    .groups = "drop"
  )

p <- ggplot(weekly, aes(week + week_tick_offset, share)) +
  geom_line(colour = mfa_colours[[mfa_label("fido2")]], linewidth = 0.9) +
  geom_point(colour = mfa_colours[[mfa_label("fido2")]], size = 1.8) +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.1))) +
  # A narrower card than the stack beside it, so fewer labels.
  week_axis(weekly$week, max_labels = 7L) +
  theme_cds() +
  labs(x = week_axis_title, y = "Share of successful attempts",
       subtitle = glue("Passkeys as a share of the sign-in factors\nusers ",
                       "succeeded with, week by week."))

brand_figure(p)
```

::: {.figure-note}
A focus on passkeys, the most secure factor available to the public.
:::

:::

## Row

::: {.card title="`r glue('Sign-in factor mix ({window_label})')`" width="34%"}

```{r mfa-signin-waffle}
#| fig-width: 4.4
#| fig-height: 4.6
#| fig-alt: |
#|   Waffle chart of one hundred squares showing each sign-in factor's share of
#|   successful attempts over the last four weeks, dominated by blue SMS OTP
#|   with small blocks of green voice OTP and orange passkeys.

mix <- mfa_mix(sign_in_mfa_types)

p <- ggplot(mix) +
  geom_waffle0(aes(x = "", y = pct, fill = factor_label),
               bricks_per_layer = 10) +
  coord_waffle(10) +
  scale_fill_manual(values = palette_for(mix$factor_label),
                    breaks = mix$factor_label) +
  theme_cds() +
  theme(
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_blank(),
    legend.position = "bottom",
    plot.title.position = "plot"
  ) +
  labs(x = NULL, y = NULL, fill = NULL,
       subtitle = "Each square is one percent of successful attempts.")

brand_figure(p)
```

:::

::: {.card title="`r glue('Sign-in factors ({window_label})')`" width="66%"}

```{r mfa-signin-table}
mfa_table_rows(sign_in_mfa_types) |>
  select(factor_label, successes, change, share_text, direction) |>
  gt() |>
  cols_hide(direction) |>
  fmt_number(successes, decimals = 0) |>
  # fmt_markdown, or gt renders the arrow's span as literal text.
  fmt_markdown(share_text) |>
  cols_label(
    factor_label = "Factor",
    successes = html(glue("Successful<br>({window_label})")),
    change = prior_window_label,
    share_text = "Share"
  ) |>
  tab_style(cell_text(color = delta_colours[["up"]]),
            cells_body(columns = change, rows = direction == "up")) |>
  tab_style(cell_text(color = delta_colours[["down"]]),
            cells_body(columns = change, rows = direction == "down")) |>
  tab_style(cell_text(color = delta_colours[["flat"]]),
            cells_body(columns = change, rows = direction == "flat")) |>
  tab_options(
    table.width = pct(100),
    table.font.size = px(14),
    data_row.padding = px(4),
    table.border.top.style = "none"
  )
```

::: {.figure-note}
The multi-factor authentication factors a member of the public can present when
signing in. Email OTP is left out: it validates an address at sign-up and cannot
sign anyone in.
:::

:::

# About

## Row

::: {.card title="About this dashboard"}

Sign-in activity on CanadaLogin as
[IBM Verify](https://github.com/cds-snc/canadalogin-reporting-data-pipeline)
records it. It is internal to Enterprise Digital Credentials and the link is
unlisted, so it isn't visible to the general public. It's for *your* information. 
For anything that leaves the team, please ask the Data and Research team. We are
happy to provide you with a bespoke calculation, or the underlying data.

**Active users are users and sign-ins are events.** Someone who signs in every
morning is one active user and many sign-ins. The active-user counts are
running totals IBM Verify keeps, so read them off the newest day and never add
them up across days or months.

**A red banner at the top of the page means a check failed at render time.** Do
not quote anything until it clears.

The numbers come from three daily tables in the `ibm_verify` schema, defined in
the [metrics cookbook](https://cds-snc.github.io/canadalogin-metrics-cookbook/cookbook/ibm_verify.html).
Yesterday's rows land each morning, so the figures end yesterday. The dashboard
is re-rendered weekly to this one URL and each publish overwrites the last, so a
number is only reproducible while it is still on the page.

Produced by the EDCP Data and Research Team. Questions go to
[#edcp-data-and-research](https://gcdigital.slack.com/archives/C0A6S9F7KV4).

:::

```{r cleanup}
#| include: false
# include: false matters for layout: this chunk sits in the last Row, where
# anything visible becomes a card and takes width from the table.
DBI::dbDisconnect(con)
```

{{< include ../../_analytics.qmd >}}
