```{r}
#| include: false
# One funnel page, knit as a child from experience-monitoring.qmd. The caller
# supplies `fid`, `label` and `h1` (the heading prefix: "#" for a page of its
# own, "####" for a tabset member). Chunks are unlabelled because a loop would
# emit the same label five times, and this comment sits in an include: false
# chunk because markdown ahead of the first heading renders as an empty card.

h_row <- paste0(h1, "#")
h_col <- paste0(h_row, "#")
```

`r h1` `r label`

`r h_row` Row {height="420px"}

`r h_col` Column {width="24%"}

::: {.valuebox color="primary"}
Latest 7-day rate

`r fmt_pct(task_success_latest(con, fid, "7", trailing_start, data_through)$value)`
:::

::: {.valuebox color="secondary"}
`r long_window_label` rate (rolling)

`r fmt_pct(task_success_long_window(con, fid, data_through)$value)`
:::

::: {.valuebox color="info"}
`r starts_box_title(fid)`

`r funnel_starts(fid)`
:::

`r h_col` Column {width="76%"}

```{r}
#| title: "Task success rate over time"
#| fig-width: 7.7
#| fig-height: 3.6
#| fig-alt: !expr chart_alt(fid)

s7 <- task_success_series(con, fid, "7", series_start, data_through)
s1 <- task_success_series(con, fid, "1", series_start, data_through)

p <- ggplot() +
  # Sized by denominator, so a low-volume day draws small. No log transform:
  # the size scale already square-roots the value on its way to an area.
  geom_point(
    data = s1, aes(window_end, value, size = denominator),
    colour = "grey70", alpha = 0.6
  ) +
  scale_size(range = c(0.4, 2.4), guide = "none") +
  # Grouped by version so the line breaks where the definition changes.
  geom_line(
    data = s7, aes(window_end, value, group = funnel_version),
    colour = colors$brand[["blue"]], linewidth = 1
  ) +
  scale_y_continuous(
    labels = label_percent(accuracy = 1), limits = c(0, 1),
    expand = expansion(mult = c(0, 0.05))
  ) +
  scale_x_date(date_labels = "%b %d") +
  theme_cds() +
  labs(
    x = NULL, y = "Task success rate",
    title = chart_title(fid),
    subtitle = chart_subtitle(fid)
  )

# The logo is sized as a fraction of figure height, so a small figure needs a
# smaller fraction.
add_cds_logo(add_watermark(p, date = data_through), height = 0.09)
```

`r h_row` Row

::: {.card title="By relying party (latest values)"}

```{r}
exit_label <- exit_step_label(fid)
compare <- prior_period_complete(fid)

latest_7d <- party_step_counts(
  con, fid, "7", trailing_start, data_through
) |>
  group_by(breakdown_value) |>
  slice_max(window_end, n = 1, with_ties = FALSE) |>
  ungroup() |>
  mutate(rp = rp_display_name(breakdown_value)) |>
  as_task_success(rp) |>
  select(rp, rate_7d = value)

# Both periods use task_success_long_window(); they never share a day.
by_rp_long <- function(as_of) {
  task_success_long_window(con, fid, as_of, breakdown_value,
                           counts = party_step_counts) |>
    mutate(rp = rp_display_name(breakdown_value)) |>
    as_task_success(rp)
}

counts_long <- by_rp_long(data_through) |>
  select(rp, rate_long = value, entered = denominator, finished = numerator)
prior_long <- by_rp_long(data_through - long_window_days) |>
  select(rp, prior_long = value)

merged <- reduce(list(latest_7d, counts_long, prior_long), full_join, by = "rp")

# rp is already the service name, so the operator is looked up by that.
per_rp <- merged |>
  mutate(Operator = coalesce(service_operators(con, rp), "")) |>
  transmute(
    Service = rp, Operator,
    rate_7d, rate_long, prior_long, entered, finished
  ) |>
  # The pooled rows are not services, and the tail of the list shuffles from
  # day to day.
  filter(!Service %in% pooled_rp_labels) |>
  arrange(desc(entered)) |>
  slice_head(n = party_rows)

overall <- task_success_long_window(con, fid, data_through) |>
  transmute(
    Service = "All users",
    Operator = "",
    rate_7d = task_success_latest(
      con, fid, "7", trailing_start, data_through
    )$value,
    rate_long = value,
    prior_long = task_success_long_window(
      con, fid, data_through - long_window_days
    )$value,
    entered = denominator, finished = numerator
  )

rows <- bind_rows(overall, per_rp) |>
  # The column stays even with nothing to compare against: every row reads as
  # a dash and comparison_note() explains it.
  mutate(
    delta = ifelse(compare, rate_long - prior_long, NA_real_),
    direction = delta_direction(delta)
  ) |>
  transmute(
    Service, Operator, rate_7d, rate_long,
    change = fmt_delta(delta), entered, finished, delta, direction
  )

gt(rows) |>
  cols_hide(c(delta, direction)) |>
  fmt_percent(c(rate_7d, rate_long), decimals = 0) |>
  fmt_number(c(entered, finished), decimals = 0) |>
  sub_missing(missing_text = "n/a") |>
  cols_label(
    rate_7d = "7-day rate",
    rate_long = glue("{long_window_label} rate"),
    change = glue("vs previous {long_window_days} days"),
    entered = html(glue("{starts_column_label(fid)}<br>({long_window_label})")),
    finished = html(glue("Reached {exit_label}<br>({long_window_label})"))
  ) |>
  tab_style(cell_text(weight = "bold"), cells_body(rows = 1)) |>
  tab_style(
    cell_text(color = delta_colours[["up"]]),
    cells_body(columns = change, rows = direction == "up")
  ) |>
  tab_style(
    cell_text(color = delta_colours[["down"]]),
    cells_body(columns = change, rows = direction == "down")
  ) |>
  tab_style(
    cell_text(color = delta_colours[["flat"]]),
    cells_body(columns = change, rows = direction == "flat")
  ) |>
  tab_options(
    table.width = pct(100),
    table.font.size = px(14),
    data_row.padding = px(4),
    table.border.top.style = "none"
  )
```

::: {.figure-note}
`r funnel_note(fid)`

`r points_note` `r internal_note`

`r comparison_note(fid)`
:::

:::
