---
title: "CanadaLogin Experience Monitoring"
author: "EDCP Data and Research Team"  # colin.douglas@cds-snc.ca
slug: expmon
# Shared format, theme and brand defaults come from _common.yml, via
# _quarto.yml here.
format:
  dashboard:
    # Written by the setup chunk at render time: the preflight banner, empty
    # unless a check failed, followed by the always-on context strip.
    include-before-body: page-header.html
    # Written by the analytics chunk at render time; see _analytics.qmd.
    include-after-body: analytics-tag.html
params:
  ga_page_title: "Experience Monitoring Dashboard"
---

```{r setup}
# The working directory is this folder; the shared layer is two levels up.
source("../../common/setup.R")

source("R/metrics.R")
source("R/preflight.R")

con <- connect_athena()

# This dashboard's accent, mirroring $primary in _theme.scss. ggplot cannot read
# the scss, so the hex is written in both places; keep them in step.
accent <- "#4B2E83"

# The help tab filters on this stream
help_stream_id <- "13052807364"
help_stream_name <- "CanadaLogin Website (Help/About/GC Partner info)"

# A failed check adds a banner rather than stopping the render. It also
# fails the Github job so an alert is sent out.
ga_lag <- 2L
preflight <- run_preflight_safety_check(
  con, today = Sys.Date(), ga_export_lag_days = ga_lag
)
write_preflight_status(preflight)

today <- Sys.Date()
as_of <- today - ga_lag        # GA's ~2-day processing lag; newest day expected

# The newest complete 7-day window across the required funnels.
data_through <- tbl(
  con, in_schema("google_analytics", "funnel_metrics_current")
) |>
  filter(
    metric_id == "task_success",
    funnel_id %in% !!required_funnels,
    window_days == "7",
    breakdown_value == "RESERVED_TOTAL",
    !window_incomplete
  ) |>
  summarise(m = max(window_end)) |>
  pull(m) |>
  as.Date()

series_start   <- as.Date("2000-01-01")          # early bound; pulls all history
trailing_start <- data_through - (7L * 12L)       # ~12-week working window

# "August 8", not "August 08".
format_long_date <- function(d) {
  d <- as.Date(d)
  paste0(format(d, "%B"), " ", as.integer(format(d, "%d")), ", ", format(d, "%Y"))
}
data_through_label <- format_long_date(data_through)

# The preflight banner and the context strip under the navbar, composed into
# the one file include-before-body reads, so both show on every page.
page_header <- "page-header.html"

write_preflight_banner(preflight, page_header)

cat(
  c(
    '<div class="page-strip">',
    glue('  <p><strong>Data through {data_through_label}.</strong> ',
         "Internal to the Data and Research team, not for public ",
         "consumption.</p>"),
    "</div>"
  ),
  file = page_header, sep = "\n", append = TRUE
)

# Whole-number percent, or "n/a" for an undefined rate.
fmt_pct <- function(x) ifelse(is.na(x), "n/a", paste0(round(x * 100), "%"))

# Pooled rows: GA's "" and "(not set)" mean the same thing, and internal
# services are not listed individually. Neither label reaches the table.
internal_rp_label <- "Internal apps"
unrecorded_rp_label <- "Relying party not recorded"
pooled_rp_labels <- c(internal_rp_label, unrecorded_rp_label)

# GA caps the funnel breakdown at 15 parties and the tail of that list shuffles
# from day to day, so the table shows only the busiest few.
party_rows <- 5L

# For spelling small counts out in prose; GA caps the breakdown at 15.
number_words <- c(
  "one", "two", "three", "four", "five", "six", "seven", "eight", "nine",
  "ten", "eleven", "twelve", "thirteen", "fourteen", "fifteen"
)

# Resolves GA's rp_name to the lookup's service name, pooling a service GA
# knows by more than one name into one row.
#
# replace(), not ifelse(): ifelse() on an empty frame returns logical(0), which
# breaks on type when an empty period is joined to a full one.
rp_display_name <- function(rp_name) {
  service <- label_relying_parties(con, rp_name)$service_name
  out <- coalesce(service, rp_name)
  out <- replace(out, rp_name %in% ga_excluded_rp_names, unrecorded_rp_label)
  replace(out, is_internal_rp(con, rp_name), internal_rp_label)
}

# Read once per funnel, for the exit step named in the table headings.
step_labels <- lapply(required_funnels, \(f) funnel_step_names(con, f))
names(step_labels) <- required_funnels

# Step names are slugs; open the underscores up for display.
format_step_name <- function(step) {
  if (is.na(step)) "unknown step" else paste0("'", gsub("_", " ", step), "'")
}

exit_step_label <- function(funnel_id) {
  format_step_name(step_labels[[funnel_id]]$exit_step)
}

entry_step_label <- function(funnel_id) {
  format_step_name(step_labels[[funnel_id]]$entry_step)
}

# The ratio denominator is not always the funnel's first step: the migration
# funnels are measured from a prompt part way through.
denominator_is_entry <- function(funnel_id) {
  isTRUE(step_labels[[funnel_id]]$entry_number == 1L)
}

# People reaching the entry step over the long window. One token, no spaces, or
# Quarto renders it at body size.
funnel_starts <- function(funnel_id) {
  format(
    task_success_long_window(con, funnel_id, data_through)$denominator,
    big.mark = ","
  )
}

long_window_label <- glue("{long_window_days}-day")

# funnel_starts() counts the ratio denominator, so only a funnel measured from
# its own first step can call that number "starts".
starts_box_title <- function(funnel_id) {
  if (denominator_is_entry(funnel_id)) {
    glue("{long_window_label} starts")
  } else {
    glue("{long_window_label} {entry_step_label(funnel_id)}")
  }
}

# The table's count column holds the same denominator as the value box.
starts_column_label <- function(funnel_id) {
  if (denominator_is_entry(funnel_id)) {
    "Started"
  } else {
    glue("Reached {entry_step_label(funnel_id)}")
  }
}

chart_title <- function(funnel_id) {
  glue("Task Success: {funnel_label(funnel_id)}")
}

# Wrapped by hand to two lines: one runs under the logo, three crowd the plot.
# Line two names the denominator where it is not the funnel's first step.
chart_subtitle <- function(funnel_id) {
  parties <- if (denominator_is_entry(funnel_id)) {
    "All relying parties, as reported by Google Analytics."
  } else {
    glue("All relying parties. Rate is of people who reached ",
         "{entry_step_label(funnel_id)}.")
  }
  paste(
    "7-day rolling rate (violet line) over the daily rate (grey points).",
    parties,
    sep = "\n"
  )
}

chart_alt <- function(funnel_id) {
  glue(
    "Chart of the task success rate over time for the ",
    "{tolower(funnel_label(funnel_id))} funnel, across all relying parties. ",
    "A bold violet line traces the 7-day ",
    "rolling rate, breaking wherever the funnel version changes; faint grey ",
    "points underneath are the noisier daily rate, sized by how many people ",
    "were in that day's denominator. The y-axis runs from zero to one ",
    "hundred percent."
  )
}

# Tested on the rate, not nrow(): an ungrouped summarise over no rows still
# returns a row, one reading 0 out of 0.
prior_period_complete <- function(funnel_id) {
  prior <- task_success_long_window(
    con, funnel_id, data_through - long_window_days
  )
  nrow(prior) > 0 && !is.na(prior$value)
}

# "up" / "down" / "flat"; a change under half a tenth of a point reads as none.
delta_direction <- function(delta) {
  case_when(
    is.na(delta) | abs(delta) <= 0.0005 ~ "flat",
    delta > 0 ~ "up",
    .default = "down"
  )
}

# Direction is carried by the arrow and the sign, not colour alone; an
# uncalculable change is a dash, not a zero. gt colours it, see delta_colours.
fmt_delta <- function(delta) {
  direction <- delta_direction(delta)
  case_when(
    is.na(delta) ~ "-",
    direction == "up" ~ sprintf("\u25b2 %+.1f pts", delta * 100),
    direction == "down" ~ sprintf("\u25bc %+.1f pts", delta * 100),
    .default = "no change"
  )
}

# Change colours: forest rather than brand green, too light to pass contrast.
delta_colours <- c(up = "#115740", down = "#AB2328", flat = "#5C6670")

# Shown when the comparison column is all dashes, so it reads as too early
# rather than broken.
comparison_note <- function(funnel_id) {
  if (prior_period_complete(funnel_id)) {
    return(NULL)
  }
  glue(
    "The change against the previous {long_window_days} days cannot be ",
    "calculated yet: this funnel does not yet have {2 * long_window_days} days ",
    "of history, and there is no earlier window to compare against."
  )
}

# Shown under every chart: point size is an encoding, not decoration.
points_note <- paste(
  "The daily points on the chart are sized by how many people were in that",
  "day's denominator."
)

# Shown under every chart and on the Overview: what the numbers cover.
internal_note <- glue(
  "The headline figures and the top row are Google Analytics' own total across ",
  "every relying party. The table lists the {number_words[party_rows]} busiest ",
  "services only."
)
```

# Overview

<!-- Pinned, or this card fills the viewport and pushes the rest below the
     fold. Sized for the text at the narrowest width, so loose on a wide one. -->
## Row {height="360px"}

::: {.card title="About this dashboard"}

This dashboard watches **task success on CanadaLogin** as recorded by
[Google Analytics 4](https://github.com/cds-snc/canadalogin-reporting-data-pipeline/tree/main/infra/modules/google_analytics/funnel_src/funnels).
It is internal to the Data and Research Team and the link is unlisted, so it
isn't visible to the general public. It's for *your* information.
For anything that leaves EDCP, please reach out to the
[Data and Research team](https://gcdigital.slack.com/archives/C0A6S9F7KV4).
We are happy to provide you with a bespoke calculation or the underlying data.

**A red banner at the top of the page means a check failed at render time.** Do
not quote anything until it clears. If you don't see a red banner (it's hard to miss),
then you can assume that all of the preflight data quality checks passed.

The numbers come from Google Analytics funnel data, defined in the
[metrics cookbook](https://cds-snc.github.io/canadalogin-metrics-cookbook/). Google
Analytics runs on a deliberate two-day processing lag, so the data ends a couple of
days before today; the "Data through" date says how current it is. Numbers from this
dashboard are preliminary. The canonical task success metrics live in the
[monthly task success report](https://drive.google.com/drive/folders/1gqU2XQfkH5ARbdc1gVRS4SdnZivZzjnR),
which is created thoughtfully and contains proper analysis and context.

:::

## Row

::: {.card title="Understanding the metrics"}

### What task success measures

Task success is the share of users who **start a flow and reach its defined
finishing point**. Each tab on this dashboard tracks one flow: sign in, sign up,
recover password, and the two migration paths.

The rate is shown over two rolling windows. The **7-day rate** is the primary
series on every chart, one point per day showing the rate over the week ending
that day. The **`r long_window_days`-day rate** is the headline figure, a single
number covering about a month. Both are rolling windows, not calendar months.
Underneath the 7-day line, faint grey points show the **daily rate**, sized by
how many people were in that day's denominator: a small point is a thin day,
where one person can move the rate by double digits.

### Reading the numbers

**Each funnel page shows a table below the chart.** The table lists the
`r number_words[party_rows]` busiest services and a total row across all of
them. The rows do not add up to the total, because the total includes every
service and the table is only a top `r number_words[party_rows]`.

**Sign-in and sign-up are not comparable to each other.** Sign-up's exit is a
real confirmation page, so it is a true completion rate. Sign-in's exit is only
reaching MFA selection, the last thing Google Analytics can see before the
redirect to IBM Verify, so it reads lower by construction. Do not present the
gap between them as a performance difference.

:::

```{r funnel-pages}
#| output: asis
# Generated from one child template, since the pages differ only by funnel id
# and a copy-pasted mismatch would render one funnel's numbers under another's.
funnel_page <- function(fid, h1) {
  label <- funnel_label(fid)
  # cat to stderr, not message(): the document sets message: false
  log_render <- function(...) cat(sprintf(...), file = stderr())
  started <- Sys.time()
  log_render("[funnel] %s: rendering\n", fid)
  page <- knitr::knit_child("_funnel-page.qmd", envir = environment(), quiet = TRUE)
  log_render(
    "[funnel] %s: done in %.1fs\n", fid,
    as.numeric(difftime(Sys.time(), started, units = "secs"))
  )
  page
}

# Sign in and sign up stay first: they are the metric of record that feeds the
# monthly task success report.
standalone_funnels <- c("sign_in", "sign_up", "recover_password")

cat(unlist(lapply(standalone_funnels, funnel_page, h1 = "#")), sep = "\n")
```

# Migration

## Row

### Column {.tabset}

```{r migration-pages}
#| output: asis
# The two migration funnels are one flow split on whether the person already had
# a CanadaLogin account, so they share a tab. The tabset sits on the Column, not
# on the Row: on the Row, only the first tab's layout is read.
migration_funnels <- c("migration_existing_to_cl", "migration_new_to_cl")

cat(unlist(lapply(migration_funnels, funnel_page, h1 = "####")), sep = "\n")
```


# Help site

```{r help-site-data}
#| include: false
# One read serves the value boxes, all four tables and the chart. include: false
# so the chunk does not become a card.
help_top_n <- 15L

# The stream carries pre-launch traffic back to 2025-11-28, which is not the
# site the dashboard reports on.
help_launch_date <- as.Date("2026-04-22")

# A few thousand rows, so the whole span is read at once: the since-launch
# share needs every day, everything else the last 12 weeks.
help_all <- tbl(con, in_schema("google_analytics", "page_traffic")) |>
  filter(
    streamid == !!help_stream_id,
    as.Date(date) >= as.Date(!!as.character(help_launch_date)),
    as.Date(date) <= as.Date(!!as.character(data_through))
  ) |>
  select(date, pagepath, pagetitle, screenpageviews) |>
  collect() |>
  mutate(
    date = as.Date(date),
    # integer64 does not survive arithmetic with doubles cleanly.
    views = as.numeric(screenpageviews),
    # /en and /en/ are one page, and the site emits both.
    path = ifelse(pagepath == "/", pagepath, sub("/+$", "", pagepath)),
    # The bare root is the English landing page, so it folds into /en.
    path = ifelse(path == "/", "/en", path),
    # Strip the site name every title ends in.
    title = sub(" - (CanadaLogin|ConnexionCanada)$", "", pagetitle),
    # Anything outside /en and /fr is vulnerability-scanner traffic
    # (oast.live callbacks, /swagger-ui, /login.php), not a page anyone wrote.
    lang = case_when(
      path == "/en" | startsWith(path, "/en/") ~ "en",
      path == "/fr" | startsWith(path, "/fr/") ~ "fr"
    )
  )

help_window <- filter(help_all, date >= trailing_start)

# Ranked once for every window and language, so each table below is a filter.
help_ranked <- bind_rows(
  filter(help_window, date > data_through - 7L) |> mutate(window = "7"),
  filter(help_window, date > data_through - long_window_days) |>
    mutate(window = as.character(long_window_days))
) |>
  filter(!is.na(lang)) |>
  group_by(window, lang, path, title) |>
  summarise(title_views = sum(views), .groups = "drop_last") |>
  # A page is a path, labelled with the title it was viewed under most often:
  # a reader whose browser translates the page reports a translated title.
  mutate(views = sum(title_views)) |>
  slice_max(title_views, n = 1, with_ties = FALSE) |>
  group_by(window, lang) |>
  arrange(desc(views), .by_group = TRUE) |>
  slice_head(n = help_top_n) |>
  ungroup() |>
  mutate(
    # The two languages are served from their own domains.
    page = paste0(
      '<a href="',
      ifelse(lang == "fr", "https://connexion.canada.ca",
             "https://login.canada.ca"),
      path, '" target="_blank" rel="noopener">',
      htmltools::htmlEscape(title), "</a>"
    )
  )

help_7d <- filter(help_window, date > data_through - 7L)
help_long <- filter(help_window, date > data_through - long_window_days)

# Language share over the long window. Scanner traffic has no language, so it
# is out of the denominator.
help_split <- help_long |>
  filter(!is.na(lang)) |>
  count(lang, wt = views, name = "views") |>
  mutate(share = round(100 * views / sum(views)))

# One token, no spaces, or Quarto renders it at body size.
help_split_label <- paste0(help_split$share[help_split$lang == "fr"], "%")

help_section_levels <- c("Users", "Partners")

help_sections <- help_all |>
  filter(!is.na(lang)) |>
  mutate(
    segment = sub("/.*$", "", sub("^/(en|fr)/?", "", path)),
    section = case_when(
      segment %in% c("users", "utilisateurs") ~ "Users",
      segment %in% c("partners", "partenaires") ~ "Partners"
    )
  ) |>
  # The landing pages are about a third of all views and are in neither
  # section, so nothing on this tab adds up to the counts on the pages tab.
  filter(!is.na(section)) |>
  mutate(section = factor(section, levels = help_section_levels))

# .drop = FALSE keeps a section with no views as a zero row.
help_section_views <- function(days) {
  help_sections |>
    filter(date > data_through - days) |>
    count(section, wt = views, name = "views", .drop = FALSE)
}

help_sections_7d <- help_section_views(7L)
help_sections_long <- help_section_views(long_window_days)

# Partners' share of the two sections' views, over whatever rows it is given.
# A window with no views at all is undefined, not zero.
partners_share <- function(rows) {
  total <- sum(rows$views)
  if (total == 0) return(NA_real_)
  sum(rows$views[rows$section == "Partners"]) / total
}

# A calendar three months, not 90 days.
three_months_start <- seq(data_through, by = "-3 months", length.out = 2)[2]

# "April 22", built from the constant so the box title cannot drift from it.
help_launch_label <- paste0(
  format(help_launch_date, "%B"), " ",
  as.integer(format(help_launch_date, "%d"))
)

# One token, no spaces, or Quarto renders it at body size.
share_label <- function(share) {
  if (is.na(share)) "n/a" else paste0(round(100 * share), "%")
}

partners_share_long <- partners_share(
  filter(help_sections, date > data_through - long_window_days)
)
partners_share_3m <- partners_share(
  filter(help_sections, date > three_months_start)
)
partners_share_launch <- partners_share(help_sections)

sections_note <- glue(
  "Sections are read off the page path: the users section is /en/users and ",
  "/fr/utilisateurs, the partners section is /en/partners and /fr/partenaires. ",
  "The chart pools by week and runs back to launch. The line under it is the ",
  "partners share of those same weekly views, week by week."
)
```


## Row

### Column {.tabset}

#### Top pages

##### Row {height="420px"}

###### Column {width="24%"}

::: {.valuebox color="primary"}
Views, last 7 days

`r format(sum(help_7d$views), big.mark = ",")`
:::

::: {.valuebox color="secondary"}
Views, last `r long_window_days` days

`r format(sum(help_long$views), big.mark = ",")`
:::

::: {.valuebox color="info"}
French share, last `r long_window_days` days

`r help_split_label`
:::

###### Column {width="76%"}

```{r help-site-chart}
#| title: "Help site page views over time"
#| fig-width: 7.7
#| fig-height: 3.6
#| fig-alt: |
#|   Chart of daily page views on the CanadaLogin help site over the last twelve
#|   weeks. A violet line traces total views per day across every help page, with
#|   a regular dip each weekend.

p <- help_window |>
  group_by(date) |>
  summarise(views = sum(views), .groups = "drop") |>
  ggplot(aes(date, views)) +
  geom_line(colour = accent, linewidth = 0.8) +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.05))) +
  scale_x_date(date_labels = "%b %d") +
  theme_cds() +
  labs(
    x = NULL, y = "Page views",
    title = "Help site page views",
    # Wrapped by hand: a single-line subtitle runs under the logo.
    subtitle = "Daily views across every page of the CanadaLogin help stream."
  )

add_cds_logo(add_watermark(p, date = data_through), height = 0.09)
```

##### Row

::: {.card title="English pages, last 7 days"}

```{r help-table-en-7d}
help_ranked |>
  filter(window == "7", lang == "en") |>
  select(page, views) |>
  gt() |>
  fmt_markdown(page) |>
  fmt_number(views, decimals = 0) |>
  cols_label(page = "Page", views = "Views") |>
  tab_options(table.width = pct(100), table.font.size = px(13),
              data_row.padding = px(3), table.border.top.style = "none")
```

:::

::: {.card title="English pages, last `r long_window_days` days"}

```{r help-table-en-long}
help_ranked |>
  filter(window == as.character(long_window_days), lang == "en") |>
  select(page, views) |>
  gt() |>
  fmt_markdown(page) |>
  fmt_number(views, decimals = 0) |>
  cols_label(page = "Page", views = "Views") |>
  tab_options(table.width = pct(100), table.font.size = px(13),
              data_row.padding = px(3), table.border.top.style = "none")
```

:::

##### Row

::: {.card title="French pages, last 7 days"}

```{r help-table-fr-7d}
help_ranked |>
  filter(window == "7", lang == "fr") |>
  select(page, views) |>
  gt() |>
  fmt_markdown(page) |>
  fmt_number(views, decimals = 0) |>
  cols_label(page = "Page", views = "Views") |>
  tab_options(table.width = pct(100), table.font.size = px(13),
              data_row.padding = px(3), table.border.top.style = "none")
```

:::

::: {.card title="French pages, last `r long_window_days` days"}

```{r help-table-fr-long}
help_ranked |>
  filter(window == as.character(long_window_days), lang == "fr") |>
  select(page, views) |>
  gt() |>
  fmt_markdown(page) |>
  fmt_number(views, decimals = 0) |>
  cols_label(page = "Page", views = "Views") |>
  tab_options(table.width = pct(100), table.font.size = px(13),
              data_row.padding = px(3), table.border.top.style = "none")
```

:::

#### Users and partners

##### Row {height="120px"}

::: {.valuebox color="primary"}
Partners share, last `r long_window_days` days

`r share_label(partners_share_long)`
:::

::: {.valuebox color="secondary"}
Last 3 months

`r share_label(partners_share_3m)`
:::

::: {.valuebox color="info"}
Since launch, `r help_launch_label`

`r share_label(partners_share_launch)`
:::

##### Row {height="580px"}

```{r help-section-chart}
#| title: "Help site views by section over time"
#| fig-width: 9.5
#| fig-height: 4.5
#| fig-alt: |
#|   Two stacked charts on a shared weekly axis, from launch in late April to
#|   late August. Above, weekly page views by section, users in violet under a much
#|   smaller partners band in orange. Below, the partners share of those views,
#|   peaking near twenty-two percent in early June and ending near eight.

weekly_sections <- help_sections |>
  mutate(week = as.Date(cut(date, "week"))) |>
  count(week, section, wt = views, name = "views", .drop = FALSE) |>
  # Drop the part weeks at either end, which would read as a collapse in views.
  filter(week >= help_launch_date, week + 6L <= data_through)

weekly_share <- weekly_sections |>
  group_by(week) |>
  summarise(share = partners_share(pick(views, section)), .groups = "drop")

week_axis <- scale_x_date(date_labels = "%b", date_breaks = "1 month")

views_panel <- ggplot(weekly_sections, aes(week, views, fill = section)) +
  geom_col(width = 7, colour = "white", linewidth = 0.25) +
  scale_fill_manual(
    values = c(
      Users = accent,
      Partners = colors$brand[["orange"]]
    )
  ) +
  scale_y_continuous(labels = label_comma(),
                     expand = expansion(mult = c(0, 0.05))) +
  week_axis +
  theme_cds() +
  # Legend on top and left, clear of the logo. The x-axis belongs to the panel
  # below, so this one's is blank.
  theme(legend.position = "top", legend.justification = "left",
        legend.margin = margin(0, 0, 0, 0),
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(
    x = NULL, y = "Page views", fill = NULL,
    title = "Help site views by section",
    subtitle = "Weekly views of the users and partners sections, both languages."
  )

share_panel <- ggplot(weekly_share, aes(week, share)) +
  geom_line(colour = colors$brand[["orange"]], linewidth = 0.8) +
  geom_point(colour = colors$brand[["orange"]], size = 0.9) +
  scale_y_continuous(labels = label_percent(accuracy = 1), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.05))) +
  week_axis +
  theme_cds() +
  labs(x = NULL, y = "Partners share")

# align = "v" with axis = "lr" so the two panels' plotting areas line up
# despite different y-axis label widths.
p <- cowplot::plot_grid(
  views_panel, share_panel,
  ncol = 1, align = "v", axis = "lr", rel_heights = c(1.7, 1)
)

add_cds_logo(add_watermark(p, date = data_through), height = 0.09)
```

##### Row

::: {.card title="Views by section"}

```{r help-section-table}
by_section <- full_join(
  rename(help_sections_7d, views_7d = views),
  rename(help_sections_long, views_long = views),
  by = "section"
) |>
  mutate(section = as.character(section))

# Total row first and bolded, as the funnel tables read.
both_sections <- tibble(
  section = "Both sections",
  views_7d = sum(help_sections_7d$views),
  views_long = sum(help_sections_long$views)
)

bind_rows(both_sections, by_section) |>
  mutate(share = views_long / both_sections$views_long) |>
  gt() |>
  fmt_number(c(views_7d, views_long), decimals = 0) |>
  fmt_percent(share, decimals = 0) |>
  cols_label(
    section = "Section",
    views_7d = "Views (7 days)",
    views_long = glue("Views ({long_window_days} days)"),
    share = glue("Share ({long_window_days} days)")
  ) |>
  tab_style(cell_text(weight = "bold"), cells_body(rows = 1)) |>
  tab_options(
    table.width = pct(100),
    table.font.size = px(14),
    data_row.padding = px(4),
    table.border.top.style = "none"
  )
```

::: {.figure-note}
`r sections_note`
:::

:::

```{r cleanup}
#| include: false
# include: false matters for layout: this chunk sits in the last Row, and
# anything visible there becomes a card and takes width from the table.
DBI::dbDisconnect(con)
```

{{< include ../../_analytics.qmd >}}
