---
title: "CanadaLogin Automated Traffic"
author: "EDCP Data and Research Team"  # colin.douglas@cds-snc.ca
slug: autotraffic
format:
  dashboard:
    # Written by the setup chunk at render time
    include-before-body: page-header.html
    include-after-body: analytics-tag.html # see _analytics.qmd
params:
  ga_page_title: "Automated Traffic Dashboard"
---

```{r setup}
# Thresholds ------------------------------------------------------------------
#
# Every number that decides whether a method fires. Calibrated on 2026-10-07
# against the confirmed bot days below. A change here changes what the
# dashboard flags, so it goes through a PR; the known-days-fire preflight
# check fails if an edit stops a confirmed day firing.
thresholds <- list(
  # A day is compared with the median of the same kind of day (weekday or
  # weekend) over this many days before it, leaving out days that fired.
  baseline_days = 28L,
  # Fewer baseline days than this and the day is not scored. 28 days hold
  # only 8 weekend days.
  baseline_min_days = c(weekday = 10L, weekend = 4L),
  # Codes sent at least `volume` times a typical day, and fewer than
  # `entry_rate_below` of them entered correctly.
  sms = list(volume = 3, entry_rate_below = 0.5),
  # New accounts at least `volume` times a typical day, and at least
  # `idle_share_at_least` of them idle on the day they were made.
  idle = list(volume = 2, idle_share_at_least = 0.5),
  # At least `groups_at_least` of the four signature errors each
  # `group_volume` times their own typical day (never less than
  # `group_floor` events), and together at least `share_at_least` of all
  # errors.
  errors = list(group_volume = 3, groups_at_least = 3L, group_floor = 20,
                share_at_least = 0.3),
  # A method that fired at least this many times its typical day gets a dot.
  spike_multiple = 10
)

# Confirmed bot days, and the methods each should fire on. Days the methods
# flag that nobody has confirmed (Sep 7 and 8) stay off this list.
known_bot_days <- tibble::tribble(
  ~day,                  ~sms, ~idle, ~errors,
  as.Date("2026-09-17"), TRUE, TRUE,  TRUE,
  as.Date("2026-09-24"), TRUE, TRUE,  TRUE,
  # Ran without a browser, or blocked GA, so no error trail.
  as.Date("2026-09-30"), TRUE, TRUE,  FALSE
)

# Setup -----------------------------------------------------------------------

# The working directory is this folder; the shared layer is two levels up.
source("../../common/setup.R")

source("R/metrics.R")
source("R/preflight.R")

library(htmltools)

con <- connect_athena()

# A failed check adds a banner. See R/preflight.R.
preflight <- run_preflight_safety_check(con, thresholds, known_bot_days)
write_preflight_status(preflight)

# Yesterday is the newest whole day; the event stream also holds today's.
through <- toronto_today() - 1L
calendar_from <- calendar_start(through)

pairs <- account_pairs(con)
sms <- dplyr::filter(sms_days(con), day <= through)
accounts <- account_days(pairs, through)
errors <- dplyr::filter(error_days(error_codes(con)), day <= through)

scored <- list(
  sms = score_sms(sms, thresholds),
  idle = score_idle(accounts, thresholds),
  errors = score_errors(errors, thresholds)
)
scores <- method_scores(scored)
calendar <- calendar_days(scores, calendar_from, through, thresholds)
since_launch <- accounts_since_launch(pairs, through)

write_traffic_summary(calendar, through)

# The newest day each method reported, which differs: GA runs a day behind.
reported_through <- purrr::map(scored, \(rows) max(rows$day[!is.na(rows$fired)]))

through_label <- format_long_date(through)

page_header <- "page-header.html"

write_preflight_banner(preflight, page_header)

lagging <- purrr::keep(reported_through, \(d) d < through)
lag_note <- if (length(lagging) > 0) {
  lagging_labels <- methods$label[match(names(lagging), methods$method)]
  glue(" {glue_collapse(lagging_labels, sep = ', ')} ",
       "through {format_short_date(lagging[[1]])}.")
} else {
  ""
}

cat(
  c(
    '<div class="page-strip">',
    glue("  <p><strong>Data through {through_label}.</strong>{lag_note} ",
         "Internal to Enterprise Digital Credentials, not for public ",
         "consumption.</p>"),
    "</div>"
  ),
  file = page_header, sep = "\n", append = TRUE
)

# Presentation ---------------------------------------------------------------

# Chart colours, mirroring _theme.scss: amber, the indicator light, only for
# what fired; slate grey for the rest. The calendar ramp climbs in lightness,
# so it reads in greyscale: each step is one more method.
robot <- list(
  accent = "#C77700", quiet = "#BFC6CD",
  ramp = c("#E6E9EC", "#F7D58A", "#E89B00", "#9A5B00")
)
ink <- "#1F2933"

brand_figure <- function(p, height = 0.09) {
  add_cds_logo(
    add_watermark(p, report_name = "CanadaLogin Automated Traffic",
                  date = through),
    height = height
  )
}

method_label <- function(m) methods$label[match(m, methods$method)]

# Days in the calendar a method fired on, newest first.
fired_days <- function(m) {
  scores |>
    dplyr::filter(method == m, fired, day >= calendar_from) |>
    dplyr::arrange(dplyr::desc(day)) |>
    dplyr::pull(day)
}

days_flagged_line <- function(m) {
  days <- fired_days(m)
  if (length(days) == 0) "None in the last 13 weeks" else
    glue("Most recent {format_short_date(days[1])}")
}

# "a typical weekday", for a value box comparing a day with its baseline.
typical_day <- function(day) glue("a typical {day_type(day)}")

# Relative luminance, to pick a dot colour that shows on its cell.
luminance <- function(hex) {
  rgb <- grDevices::col2rgb(hex) / 255
  rgb <- ifelse(rgb <= 0.03928, rgb / 12.92, ((rgb + 0.055) / 1.055)^2.4)
  as.vector(c(0.2126, 0.7152, 0.0722) %*% rgb)
}

weekday_names <- c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun")

# GitHub-style grid: a column per week, Monday at the top, shaded by how many
# methods fired.
calendar_plot <- function(cal) {
  levels <- as.character(0:nrow(methods))
  dot_on <- ifelse(purrr::map_dbl(robot$ramp, luminance) > 0.4, ink, "#FFFFFF")

  cells <- cal |>
    dplyr::mutate(
      week = day - (as.integer(format(day, "%u")) - 1L),
      wday = factor(weekday_names[as.integer(format(day, "%u"))],
                    levels = rev(weekday_names)),
      level = factor(n_fired, levels = levels)
    )

  firsts <- seq(as.Date(format(min(cells$day), "%Y-%m-01")), max(cells$day),
                by = "month")
  firsts <- firsts[firsts >= min(cells$week)]
  month_weeks <- firsts - (as.integer(format(firsts, "%u")) - 1L)

  ggplot(cells, aes(week, wday)) +
    geom_tile(aes(fill = level), width = 6, height = 0.86) +
    geom_tile(data = dplyr::filter(cells, partial),
              aes(linetype = "Not every method reported"),
              fill = NA, colour = ink, width = 6, height = 0.86,
              linewidth = 0.45) +
    geom_point(data = dplyr::filter(cells, spike),
               aes(shape = glue("A method at {thresholds$spike_multiple}x ",
                                "or more")),
               colour = dot_on[as.integer(as.character(
                 dplyr::filter(cells, spike)$level
               )) + 1L],
               size = 1.4) +
    scale_fill_manual(
      values = setNames(robot$ramp, levels), drop = FALSE,
      labels = c("None", "1 method", "2 methods", "All 3"),
      name = "Methods that fired"
    ) +
    scale_linetype_manual(values = "11", name = NULL) +
    scale_shape_manual(values = 16, name = NULL) +
    scale_x_date(position = "top", breaks = month_weeks,
                 labels = format(firsts, "%b"), expand = c(0, 0)) +
    scale_y_discrete(labels = \(x) ifelse(x %in% c("Mon", "Wed", "Fri"), x, ""),
                     expand = c(0, 0)) +
    coord_fixed(ratio = 7) +
    guides(
      fill = guide_legend(order = 1, nrow = 1),
      linetype = guide_legend(order = 2,
                              override.aes = list(fill = robot$ramp[1])),
      shape = guide_legend(order = 3, override.aes = list(colour = ink))
    ) +
    theme_cds(base_size = 9) +
    theme(
      panel.border = element_blank(), panel.grid = element_blank(),
      axis.ticks = element_blank(), axis.title = element_blank(),
      axis.text = element_text(colour = "grey35"),
      legend.position = "bottom", legend.box = "vertical",
      legend.box.just = "left", legend.justification = "left",
      legend.key.size = unit(0.35, "cm"), legend.text = element_text(size = 7.5),
      legend.title = element_text(size = 7.5), legend.spacing.y = unit(0, "cm")
    )
}

# Two panels on one date axis: volume against the line it must clear, and the
# ratio against its threshold. A day fires when both are past their lines.
method_figure <- function(rows, volume, volume_label, cut, cut_label,
                          ratio_label, ratio_cut, ratio_cut_label,
                          ratio_labels = label_percent(), cut_line = FALSE) {
  rows <- rows |>
    dplyr::filter(day >= calendar_from) |>
    dplyr::mutate(
      volume = .data[[volume]],
      cut = .data[[cut]],
      kind = dplyr::case_when(fired %in% TRUE ~ "fired",
                              day_type(day) == "weekend" ~ "weekend",
                              .default = "weekday")
    )
  fills <- c(fired = robot$accent, weekday = robot$quiet,
             weekend = grDevices::adjustcolor(robot$quiet, alpha.f = 0.5))
  limits <- c(calendar_from - 1L, through + 1L)

  # A cut that moves with each day's baseline is a tick per bar; a fixed one
  # is a single line.
  cut_layer <- if (cut_line) {
    geom_hline(yintercept = max(rows$cut, na.rm = TRUE), linetype = "dashed",
               colour = "grey45", linewidth = 0.4)
  } else {
    geom_segment(aes(x = day - 0.45, xend = day + 0.45, y = cut, yend = cut),
                 colour = ink, linewidth = 0.5, na.rm = TRUE)
  }

  volume_panel <- ggplot(rows, aes(day, volume)) +
    geom_col(aes(fill = kind), width = 0.8) +
    cut_layer +
    scale_fill_manual(values = fills, guide = "none") +
    scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                       expand = expansion(mult = c(0, 0.06))) +
    scale_x_date(limits = limits, expand = c(0, 0)) +
    theme_cds() +
    theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(),
          panel.grid.minor = element_blank()) +
    labs(x = NULL, y = volume_label, subtitle = cut_label)

  ratio_panel <- ggplot(rows, aes(day, ratio)) +
    geom_hline(yintercept = ratio_cut, linetype = "dashed", colour = "grey45",
               linewidth = 0.4) +
    annotate("text", x = calendar_from, y = ratio_cut, label = ratio_cut_label,
             hjust = 0, vjust = -0.5, size = 2.9, colour = "grey35") +
    geom_line(colour = robot$quiet, linewidth = 0.5, na.rm = TRUE) +
    geom_point(aes(colour = kind == "fired", size = kind == "fired"),
               na.rm = TRUE) +
    scale_colour_manual(values = c(`TRUE` = robot$accent, `FALSE` = "grey55"),
                        guide = "none") +
    scale_size_manual(values = c(`TRUE` = 2.2, `FALSE` = 0.8), guide = "none") +
    scale_y_continuous(labels = ratio_labels, limits = c(0, 1)) +
    scale_x_date(limits = limits, expand = c(0, 0),
                 breaks = rev(seq(through, calendar_from, by = "-2 weeks")),
                 date_labels = "%b %d") +
    theme_cds() +
    theme(panel.grid.minor = element_blank()) +
    labs(x = NULL, y = ratio_label)

  cowplot::plot_grid(volume_panel, ratio_panel, ncol = 1, align = "v",
                     axis = "lr", rel_heights = c(1.4, 1))
}

# The quarter's daily numbers, newest first.
daily_table <- function(rows, columns, labels, decimals) {
  rows |>
    dplyr::filter(day >= calendar_from) |>
    dplyr::arrange(dplyr::desc(day)) |>
    dplyr::mutate(
      day = paste(format(day, "%a"), format_short_date(day)),
      multiple = fmt_multiple(multiple),
      fired = dplyr::case_when(is.na(fired) ~ "Not scored",
                               fired ~ "Fired", .default = "")
    ) |>
    dplyr::select(day, dplyr::all_of(columns), multiple, ratio, fired) |>
    gt() |>
    cols_align("right", multiple) |>
    fmt_number(dplyr::all_of(columns), decimals = 0) |>
    fmt_percent(ratio, decimals = decimals) |>
    sub_missing(missing_text = "-") |>
    cols_label(.list = c(list(day = "Day"), labels,
                         list(multiple = "vs typical day", fired = ""))) |>
    tab_style(style = cell_text(weight = "bold", color = robot$accent),
              locations = cells_body(rows = fired == "Fired")) |>
    tab_options(table.width = pct(100), table.font.size = px(14),
                data_row.padding = px(3), table.border.top.style = "none")
}

# Methods with no score at the start of the calendar: a source too new to
# have a baseline. Named in the note under the calendar.
late_starts <- purrr::imap(scored, \(rows, m) {
  first <- min(rows$day[!is.na(rows$fired)])
  if (first > calendar_from) first else NULL
}) |> purrr::compact()
```

# Overview

```{r overview-summary}
#| include: false
flagged <- dplyr::filter(calendar, n_fired > 0) |> dplyr::arrange(dplyr::desc(day))
all_three <- sum(calendar$n_fired == nrow(methods))
latest_flag <- flagged[1, ]

latest_value <- if (nrow(flagged) == 0) {
  "None"
} else {
  nbsp(format_short_date(latest_flag$day))
}
latest_line <- if (nrow(flagged) == 0) {
  "No method fired in the last 13 weeks"
} else {
  glue("{latest_flag$n_fired} of {nrow(methods)}: ",
       "{glue_collapse(method_label(latest_flag$methods_fired[[1]]), sep = ', ')}")
}

newest <- calendar[calendar$day == through, ]
reporting_value <- nbsp(glue("{newest$reported} of {nrow(methods)}"))
reporting_line <- if (!newest$partial) {
  glue("All methods through {format_short_date(through)}")
} else {
  glue("Waiting on {glue_collapse(waiting_on(scores, through), sep = ', ')}")
}

# Why some squares have a dotted outline: a source too new to compare with,
# or one that has not caught up with the newest days.
calendar_note <- c(
  purrr::imap_chr(late_starts, \(d, m) {
    glue("{method_label(m)} has no score before {format_short_date(d)}: its ",
         "source had too few earlier days to compare with.")
  }),
  if (any(calendar$partial & calendar$day > through - 7L)) {
    "The newest days have a dotted outline until slower sources catch up."
  }
) |> paste(collapse = " ")

shaded_days <- if (nrow(flagged) == 0) {
  "none"
} else {
  glue_collapse(format_short_date(flagged$day), sep = ", ", last = " and ")
}

calendar_alt <- glue(
  "Calendar grid of the last 13 weeks, one column per week and one row per ",
  "weekday, each day shaded by how many of the three detection methods ",
  "fired. {nrow(flagged)} days are shaded: {shaded_days}."
)
```

## Row {height="150px"}

::: {.valuebox color="primary"}
Days flagged, last 13 weeks

`r nrow(flagged)`

`r all_three` with all three methods
:::

::: {.valuebox color="info"}
Most recent flagged day

`r latest_value`

`r latest_line`
:::

::: {.valuebox color="secondary"}
Methods reporting, `r format_short_date(through)`

`r reporting_value`

`r reporting_line`
:::

## Row {height="auto"}

::: {.card title="Each day, how many methods found automated traffic" width="55%"}

```{r calendar}
#| fig-width: 7
#| fig-height: 2.9
#| fig-alt: !expr calendar_alt
brand_figure(calendar_plot(calendar), height = 0.12)
```

::: {.figure-note}
Each square is a day in Toronto time. A day can be flagged by up to three
methods, each on its own page. `r calendar_note`
:::

:::

::: {.card title="Flagged days" width="45%"}

```{r flagged-table}
if (nrow(flagged) == 0) {
  cat("No method fired in the last 13 weeks.")
} else {
  strongest <- scores |>
    dplyr::filter(fired) |>
    dplyr::group_by(day) |>
    dplyr::summarise(strongest = max(multiple), .groups = "drop")

  flagged |>
    dplyr::left_join(strongest, by = "day") |>
    dplyr::mutate(
      day_label = paste(format(day, "%a"), format_short_date(day)),
      count = glue("{n_fired} of {nrow(methods)}"),
      which = purrr::map_chr(methods_fired, \(m) {
        pages <- methods[methods$method %in% m, ]
        glue_collapse(glue("[{pages$label}](#{pages$page})"), sep = ", ")
      }),
      strongest = fmt_multiple(strongest)
    ) |>
    dplyr::select(day_label, count, which, strongest) |>
    gt() |>
    fmt_markdown(which) |>
    cols_label(day_label = "Day", count = "Methods", which = "Which",
               strongest = "Strongest") |>
    tab_options(table.width = pct(100), table.font.size = px(14),
                data_row.padding = px(4), table.border.top.style = "none")
}
```

::: {.figure-note}
*Strongest* is the largest volume any method that fired reached, against
that method's typical day.
:::

:::

## Row

::: {.card title="Reading this dashboard"}

This dashboard looks for **automated traffic on CanadaLogin**: scripts and bots
rather than people. It is internal to Enterprise Digital Credentials and the
link is unlisted. For anything that leaves EDCP, please reach out to the
[Data and Research team](https://gcdigital.slack.com/archives/C0A6S9F7KV4).

**A red banner at the top of the page means a check failed at render time.**
Do not quote anything until it clears. One check makes sure the confirmed bot
days of September 17, 24 and 30 are still found, so a change to the rules
cannot quietly blind the dashboard.

### Three methods, three kinds of trail

Each method watches one source and compares every day with a typical day:
the median of the same kind of day (weekday or weekend) over the 28 days
before it, leaving out days that were already flagged. **A method fires only
when two things happen together**: volume well above a typical day, *and* a
ratio that real people do not produce. Volume alone is not enough. A new
service launching brings a surge of real users, and they enter their codes and
reach their service.

- **SMS codes** fires when far more codes are sent than usual and few are
  entered. Real users enter about 96% of the codes they are sent.
- **Idle accounts** fires when far more accounts are made than usual and most
  never reach a partner service that day. Real users go straight to the service
  they came for.
- **Error patterns** fires when several rare errors spike together: invalid
  phone numbers, SMS limits, wrong codes and interrupted sign-ins.

The methods catch different bots. A bot that never loads a normal browser
leaves no trace in Google Analytics, so Error patterns misses it, as on
September 30. That is why the calendar counts methods rather than adding
volumes, which are in different units.

### What a flag means

**A flag is a suspicion, not a finding.** It says the day looked unlike real
use on that method's measures. More methods agreeing makes it more likely.
Days are in Toronto time. The numbers that decide when a method fires are
listed at the top of each method page.

:::

# SMS codes

```{r sms-summary}
#| include: false
sms_rows <- scored$sms
sms_latest <- sms_rows[sms_rows$day == reported_through$sms, ]
```

## Row {height="auto"}

::: {.card title="How this method works"}
CanadaLogin texts a one-time code to a phone number, and the user types it back.
A script that floods the sign-up flow with phone numbers sends codes nobody
enters, which costs money for every message. This method fires when **codes
sent are at least `r thresholds$sms$volume` times a typical day** and **fewer
than `r percent(thresholds$sms$entry_rate_below)` are entered correctly**. Real
users enter about 96%, even during a launch. Source: `ibm_verify.mfa_activity`.
Voice codes are shown for context, since a script blocked from SMS may switch
to voice; they do not count towards the flag.
:::

## Row {height="150px"}

::: {.valuebox color="primary"}
SMS codes sent, `r format_short_date(sms_latest$day)`

`r comma(sms_latest$sms_sent)`

`r fmt_multiple(sms_latest$multiple)` `r typical_day(sms_latest$day)`
:::

::: {.valuebox color="info"}
Codes entered, `r format_short_date(sms_latest$day)`

`r percent(sms_latest$ratio, accuracy = 1)`

Fires below `r percent(thresholds$sms$entry_rate_below)`
:::

::: {.valuebox color="secondary"}
Days flagged, last 13 weeks

`r length(fired_days("sms"))`

`r days_flagged_line("sms")`
:::

## Row {height="560px"}

::: {.card title="SMS codes sent and entered each day (last 13 weeks)"}

```{r sms-chart}
#| fig-width: 13
#| fig-height: 4.8
#| fig-alt: |
#|   Two charts on a shared date axis. Above, SMS codes sent each day, with a
#|   tick on each bar where the method would fire; bars that fired are drawn in
#|   the accent colour. Below, the share of codes entered correctly each day,
#|   near 96 percent on most days, with a dashed line at 50 percent.
p <- method_figure(
  dplyr::mutate(sms_rows, cut = baseline * thresholds$sms$volume),
  volume = "sms_sent", volume_label = "SMS codes sent", cut = "cut",
  cut_label = glue("Ticks: {thresholds$sms$volume} times a typical day. ",
                   "Lighter bars are weekends, compared only with weekends."),
  ratio_label = "Entered correctly", ratio_cut = thresholds$sms$entry_rate_below,
  ratio_cut_label = glue("Fires below {percent(thresholds$sms$entry_rate_below)}")
)
brand_figure(p)
```

:::

## Row

::: {.card title="Each day (last 13 weeks)"}

```{r sms-table}
sms_rows |>
  dplyr::select(day, sms_sent, sms_success, voice_sent, multiple, ratio, fired) |>
  daily_table(c("sms_sent", "sms_success", "voice_sent"),
              list(sms_sent = "SMS sent", sms_success = "SMS entered",
                   voice_sent = "Voice sent"), decimals = 0) |>
  cols_label(ratio = "Entered")
```

:::

# Idle accounts

```{r idle-summary}
#| include: false
idle_rows <- scored$idle
idle_latest <- idle_rows[idle_rows$day == reported_through$idle, ]
launch_latest <- since_launch[since_launch$date == through, ]

idle_flag_days <- dplyr::filter(idle_rows, fired %in% TRUE)$day

csv_name <- glue("canadalogin-accounts-{through}.csv")
```

## Row

### Column {.tabset}

#### Detection

##### Row {height="auto"}

::: {.card title="How this method works"}
An account is **idle on the day it was made** if it did not sign in to any
partner service that day. Real users sign up because they want a service, so
they go straight to it; on a typical day about 18% of new accounts are idle.
Scripts that make accounts in bulk leave them idle. This method fires when
**new accounts are at least `r thresholds$idle$volume` times a typical day**
and **at least `r percent(thresholds$idle$idle_share_at_least)` of them are
idle on the day they were made**. Source: the IBM Verify event stream
(`ibm_verify_events_raw`), which is preliminary.
:::

##### Row {height="150px"}

::: {.valuebox color="primary"}
New accounts, `r format_short_date(idle_latest$day)`

`r comma(idle_latest$new_accounts)`

`r fmt_multiple(idle_latest$multiple)` `r typical_day(idle_latest$day)`
:::

::: {.valuebox color="info"}
Idle on the day made, `r format_short_date(idle_latest$day)`

`r percent(idle_latest$ratio, accuracy = 1)`

Fires at `r percent(thresholds$idle$idle_share_at_least)` or more
:::

::: {.valuebox color="secondary"}
Days flagged, last 13 weeks

`r length(fired_days("idle"))`

`r days_flagged_line("idle")`
:::

##### Row {height="560px"}

::: {.card title="New accounts each day, and the share idle on the day made (last 13 weeks)"}

```{r idle-chart}
#| fig-width: 13
#| fig-height: 4.8
#| fig-alt: |
#|   Two charts on a shared date axis. Above, new accounts each day, with a
#|   tick on each bar where the method would fire; bars that fired are drawn in
#|   the accent colour. Below, the share of new accounts idle on the day they
#|   were made, with a dashed line at 50 percent.
p <- method_figure(
  dplyr::mutate(idle_rows, cut = baseline * thresholds$idle$volume),
  volume = "new_accounts", volume_label = "New accounts", cut = "cut",
  cut_label = glue("Ticks: {thresholds$idle$volume} times a typical day. ",
                   "Lighter bars are weekends, compared only with weekends."),
  ratio_label = "Idle on the day made",
  ratio_cut = thresholds$idle$idle_share_at_least,
  ratio_cut_label = glue("Fires at ",
                         "{percent(thresholds$idle$idle_share_at_least)} or more")
)
brand_figure(p)
```

:::

##### Row

::: {.card title="Each day (last 13 weeks)"}

```{r idle-table}
idle_rows |>
  dplyr::select(day, new_accounts, idle_same_day, multiple, ratio, fired) |>
  daily_table(c("new_accounts", "idle_same_day"),
              list(new_accounts = "New accounts",
                   idle_same_day = "Idle on the day made"), decimals = 0) |>
  cols_label(ratio = "Share idle")
```

:::

#### Accounts since launch

##### Row {height="150px"}

::: {.valuebox color="primary"}
All accounts, `r format_short_date(through)`

`r comma(launch_latest$all_accounts)`

Since the April 2026 launch
:::

::: {.valuebox color="info"}
Idle accounts

`r comma(launch_latest$idle_accounts)`

`r percent(launch_latest$idle_share, accuracy = 1)` of all accounts
:::

::: {.valuebox color="secondary"}
Signed in to a service

`r comma(launch_latest$signed_in_to_service)`

At least one partner service
:::

##### Row {height="560px"}

::: {.card title="Accounts since launch, by week" width="70%"}

```{r launch-chart}
#| fig-width: 9
#| fig-height: 4.6
#| fig-alt: |
#|   Line chart of CanadaLogin accounts since the April 2026 launch, one point
#|   per week, for all accounts and for accounts that have signed in to a
#|   partner service. The lines rise together until mid-September, then all
#|   accounts pull away. Ticks along the bottom mark the days flagged on the
#|   Detection tab.
weekly <- since_launch |>
  dplyr::mutate(week_end = pmin(date - (as.integer(format(date, "%u")) - 1L) + 6L,
                                through)) |>
  dplyr::group_by(week_end) |>
  dplyr::slice_max(date, n = 1) |>
  dplyr::ungroup() |>
  tidyr::pivot_longer(c(all_accounts, signed_in_to_service),
                      names_to = "measure", values_to = "accounts")

line_labels <- c(all_accounts = "All accounts",
                 signed_in_to_service = "Signed in to a service")
line_colours <- c(all_accounts = robot$accent, signed_in_to_service = ink)

ends <- dplyr::filter(weekly, week_end == max(week_end))

p <- ggplot(weekly, aes(week_end, accounts, colour = measure)) +
  geom_segment(data = tibble::tibble(day = idle_flag_days),
               aes(x = day, xend = day, y = 0, yend = max(weekly$accounts) * 0.04),
               inherit.aes = FALSE, colour = "grey35", linewidth = 0.6) +
  annotate("text", x = min(idle_flag_days, through), y = max(weekly$accounts) * 0.06,
           label = "Flagged on Detection tab", hjust = 1.05, vjust = 0,
           size = 2.9, colour = "grey35") +
  geom_line(linewidth = 1) +
  geom_point(data = ends, size = 2.4) +
  geom_text(data = ends,
            aes(label = paste0(comma(accounts), "  ", line_labels[measure])),
            hjust = -0.08, fontface = "bold", size = 3.3, show.legend = FALSE) +
  scale_colour_manual(values = line_colours, guide = "none") +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.06))) +
  # Breaks stop at the data; the right padding is room for the end labels.
  scale_x_date(breaks = rev(seq(through, min(weekly$week_end), by = "-4 weeks")),
               date_labels = "%b %d", expand = expansion(mult = c(0.02, 0.32))) +
  theme_cds() +
  theme(panel.grid.minor = element_blank()) +
  labs(x = NULL, y = "Accounts since launch",
       subtitle = glue("Each week's last day, through {format_short_date(through)}."))
brand_figure(p)
```

:::

::: {.card title="Download the daily numbers" width="30%"}

`r csv_download_link(since_launch, csv_name, glue("Download {csv_name}"))`

One row per day from the April 22, 2026 launch through
`r format_short_date(through)`, in Toronto time. Each count is as of the end
of that day, and earlier days do not change.

- `all_accounts`: accounts made since launch.
- `idle_accounts`: of those, accounts that had not yet signed in to any
  partner service.
- `signed_in_to_service`: accounts that had signed in to at least one partner
  service. `all_accounts` is `idle_accounts` plus `signed_in_to_service`.
- `idle_share`: `idle_accounts` over `all_accounts`.
- `new_accounts`: accounts made that day.

An idle account is not necessarily automated. Some people make an account and
never use it. Source: the IBM Verify event stream, which is preliminary.

:::

# Error patterns

```{r errors-summary}
#| include: false
error_rows <- scored$errors
errors_latest <- error_rows[error_rows$day == reported_through$errors, ]
```

## Row {height="auto"}

::: {.card title="How this method works"}
Four errors are rare on a normal day: **invalid phone numbers, SMS limits
reached, wrong one-time codes and interrupted sign-ins**.
When a script walks the SMS sign-up flow, they rise together. A single error
spiking usually means a bug or an outage instead. This method fires when **at
least `r thresholds$errors$groups_at_least` of the four are each
`r thresholds$errors$group_volume` times their typical day** (counting a
typical day as at least `r thresholds$errors$group_floor` events, so small
numbers do not jump) and **together they make up at least
`r percent(thresholds$errors$share_at_least)` of all errors**. Source:
`google_analytics.error_events`, which runs a day or two behind. A bot that
never loads a normal browser leaves no trace here.
:::

## Row {height="150px"}

::: {.valuebox color="primary"}
Signature errors up, `r format_short_date(errors_latest$day)`

`r nbsp(glue("{errors_latest$groups_up} of 4"))`

Fires at `r thresholds$errors$groups_at_least` or more
:::

::: {.valuebox color="info"}
Share of all errors, `r format_short_date(errors_latest$day)`

`r percent(errors_latest$ratio, accuracy = 1)`

Fires at `r percent(thresholds$errors$share_at_least)` or more
:::

::: {.valuebox color="secondary"}
Days flagged, last 13 weeks

`r length(fired_days("errors"))`

`r days_flagged_line("errors")`
:::

## Row {height="560px"}

::: {.card title="Signature errors each day (last 13 weeks)"}

```{r errors-chart}
#| fig-width: 13
#| fig-height: 4.8
#| fig-alt: |
#|   Two charts on a shared date axis. Above, how many of the four signature
#|   errors were at least three times their typical day, with a tick at three;
#|   bars that fired are drawn in the accent colour. Below, the signature
#|   errors' share of all error events each day, with a dashed line at 30
#|   percent.
p <- method_figure(
  dplyr::mutate(error_rows, cut = ifelse(is.na(fired), NA,
                                         thresholds$errors$groups_at_least)),
  volume = "groups_up", volume_label = "Signature errors up", cut = "cut",
  cut_label = glue("Dashed line: {thresholds$errors$groups_at_least} of 4 ",
                   "errors at {thresholds$errors$group_volume} times their ",
                   "typical day. Lighter bars are weekends."),
  cut_line = TRUE,
  ratio_label = "Share of all errors",
  ratio_cut = thresholds$errors$share_at_least,
  ratio_cut_label = glue("Fires at {percent(thresholds$errors$share_at_least)} or more")
)
brand_figure(p)
```

:::

## Row

::: {.card title="Each day (last 13 weeks)"}

```{r errors-table}
error_rows |>
  dplyr::select(day, dplyr::all_of(names(signature_labels)), all_errors,
                multiple, ratio, fired) |>
  daily_table(c(names(signature_labels), "all_errors"),
              c(as.list(signature_labels), list(all_errors = "All errors")),
              decimals = 0) |>
  cols_label(ratio = "Signature share")
```

:::

```{r cleanup}
#| include: false
# include: false matters for layout: this chunk sits in the last Row, where
# anything visible becomes a card and takes width from the table.
DBI::dbDisconnect(con)
```

{{< include ../../_analytics.qmd >}}
