---
title: "CanadaLogin Automated Traffic"
author: "EDCP Data and Research Team"  # colin.douglas@cds-snc.ca
slug: autotraffic
format:
  dashboard:
    # Written by the setup chunk at render time
    include-before-body: page-header.html
    include-after-body: analytics-tag.html # see _analytics.qmd
params:
  ga_page_title: "Automated Traffic Dashboard"
---

```{r setup}
# Thresholds ------------------------------------------------------------------
#
# Every number that decides whether a method fires. The known-days-fire
# preflight check fails if an edit stops a confirmed day firing.
thresholds <- list(
  # A day is compared with the median of the same kind of day (weekday or
  # weekend) over this many days before it, leaving out days that fired.
  baseline_days = 28L,
  # Fewer baseline days than this and the day is not scored. 28 days hold
  # only 8 weekend days.
  baseline_min_days = c(weekday = 10L, weekend = 4L),
  # Codes sent at least `volume` times a typical day, and fewer than
  # `entry_rate_below` of them entered correctly.
  sms = list(volume = 3, entry_rate_below = 0.5),
  # Codes sent at least `volume` times a typical day, and at least
  # `share_at_least` of them requested from outside Canada and the US.
  location = list(volume = 1.5, share_at_least = 0.3),
  # New accounts at least `volume` times a typical day, and at least
  # `idle_share_at_least` of them idle on the day they were made.
  idle = list(volume = 2, idle_share_at_least = 0.5),
  # Email codes entered at least `volume` times a typical day, and the median
  # entered in under `median_seconds_below` seconds.
  speed = list(volume = 2, median_seconds_below = 10),
  # At least `groups_at_least` of the four signature errors each
  # `group_volume` times their own typical day (never less than
  # `group_floor` events), and together at least `share_at_least` of all
  # errors.
  errors = list(group_volume = 3, groups_at_least = 3L, group_floor = 20,
                share_at_least = 0.3)
)

# Confirmed bot days, and the methods each should fire on.
known_bot_days <- tibble::tribble(
  ~day,                  ~sms, ~location, ~idle, ~speed, ~errors,
  # SMS from outside Canada and the US; those days' new accounts were not idle.
  as.Date("2026-09-07"), TRUE, TRUE,      FALSE, FALSE,  TRUE,
  as.Date("2026-09-08"), TRUE, TRUE,      FALSE, FALSE,  FALSE,
  as.Date("2026-09-17"), TRUE, TRUE,      TRUE,  FALSE,  TRUE,
  as.Date("2026-09-24"), TRUE, TRUE,      TRUE,  FALSE,  TRUE,
  # Ran without a browser, or blocked GA, so no error trail.
  as.Date("2026-09-30"), TRUE, TRUE,      TRUE,  TRUE,   FALSE
)

# Setup -----------------------------------------------------------------------

# The working directory is this folder; the shared layer is two levels up.
source("../../common/setup.R")

source("R/metrics.R")
source("R/preflight.R")

# Estimated prices, in dollars before tax. `up_to` is the top of each tier
# of monthly volume. They are read from the publishing repo, and with no file
# every price is NA and the costs read "-".
prices <- private_data("prices.csv")
price_tiers <- function(item) {
  no_prices <- tibble::tibble(up_to = Inf, price = NA_real_)
  if (is.null(prices)) return(no_prices)
  tibble::as_tibble(prices[prices$item == item, c("up_to", "price")])
}
# One SMS code, by codes sent in the month.
sms_price_tiers <- price_tiers("sms")
# One monthly active user, by active users in the month.
user_price_tiers <- price_tiers("active_user")

con <- connect_athena()

# A failed check adds a banner. See R/preflight.R.
preflight <- run_preflight_safety_check(con, thresholds, known_bot_days)
write_preflight_status(preflight)

# Yesterday is the newest whole day; the event stream also holds today's.
through <- toronto_today() - 1L
calendar_from <- calendar_start(through)
chart_from <- calendar_start(through, chart_weeks)

pairs <- account_pairs(con)
sms <- dplyr::filter(sms_days(con), day <= through)
sms_origins <- dplyr::filter(sms_origin_days(con), day <= through)
accounts <- account_days(pairs, through)
errors <- dplyr::filter(error_days(error_codes(con)), day <= through)
email_seconds <- dplyr::filter(email_code_seconds(con), day <= through)

scored <- list(
  sms = score_sms(sms, thresholds),
  location = score_location(sms_origins, thresholds),
  idle = score_idle(accounts, thresholds),
  speed = score_speed(speed_days(email_seconds), thresholds),
  errors = score_errors(errors, thresholds)
)
scores <- method_scores(scored)
calendar <- calendar_days(scores, calendar_from, through)
since_launch <- accounts_since_launch(pairs, through)

write_traffic_summary(calendar, through)

# The newest day each method reported, which differs: GA runs a day behind.
reported_through <- purrr::map(scored, \(rows) max(rows$day[!is.na(rows$fired)]))

page_header <- "page-header.html"

write_preflight_banner(preflight, page_header)

cat(
  c(
    '<div class="page-strip">',
    # "Most": GA runs a day behind the rest; the calendar's outline shows it.
    glue("  <p><strong>Most data through {format_long_date(through)}.</strong> ",
         "Internal to Enterprise Digital Credentials, not for public ",
         "consumption.</p>"),
    "</div>"
  ),
  file = page_header, sep = "\n", append = TRUE
)

# Presentation ---------------------------------------------------------------

# Chart colours, mirroring _theme.scss: amber, the indicator light, only for
# what fired; slate grey for the rest.
robot <- list(accent = "#C77700", quiet = "#BFC6CD")

# Calendar shading: a fixed log scale, so a colour means the same every week,
# darkening as it climbs so it reads in greyscale.
strength_limits <- c(0.5, 50)
strength_breaks <- c(0.5, 1, 2, 5, 10, 20, 50)
strength_stops <- c(0.5, 1, 2, 2.5, 10, 50)
strength_ramp <- c("#F1F3F5", "#E3E6EA", "#D5DAE0", "#F2C55C", "#E89B00",
                   "#8F5200")
# Amber and brown mean a method fired: an unflagged day is held to the greys
# however high its volume (a launch), and a flagged day starts at amber.
unflagged_cap <- 2
flagged_floor <- 2.5
strength_values <- scales::rescale(log10(strength_stops),
                                   from = log10(strength_limits))
no_data <- "#F7F8F9"

ink <- "#1F2933"

brand_figure <- function(p, height = 0.09) {
  add_cds_logo(
    add_watermark(p, report_name = "CanadaLogin Automated Traffic",
                  date = through),
    height = height
  )
}

method_label <- function(m) methods$label[match(m, methods$method)]

# Relative luminance, to pick a label colour that shows on its cell.
luminance <- function(hex) {
  rgb <- grDevices::col2rgb(hex) / 255
  rgb <- ifelse(rgb <= 0.03928, rgb / 12.92, ((rgb + 0.055) / 1.055)^2.4)
  as.vector(c(0.2126, 0.7152, 0.0722) %*% rgb)
}

# GitHub-style grid, a column per week with Monday on top. A flagged day is
# labelled with its Strongest figure; days before launch are blank.
calendar_plot <- function(cal) {
  # The fill a day gets, to pick a label colour that shows on it.
  fill_of <- scales::gradient_n_pal(strength_ramp, strength_values)
  log_position <- function(x) {
    clamped <- pmin(pmax(x, strength_limits[1]), strength_limits[2])
    scales::rescale(log10(clamped), from = log10(strength_limits))
  }

  cells <- cal |>
    dplyr::filter(day >= canadalogin_launch) |>
    dplyr::mutate(
      week = day - (as.integer(format(day, "%u")) - 1L),
      # Monday on top: row 7 is Monday, row 1 Sunday. Numeric, so the month
      # lines can run between rows.
      row = 8L - as.integer(format(day, "%u")),
      shade = ifelse(n_fired > 0, pmax(peak, flagged_floor),
                     pmin(peak, unflagged_cap))
    )
  flagged_cells <- cells |>
    dplyr::filter(n_fired > 0) |>
    dplyr::mutate(
      label = paste0(round(strongest), "x"),
      ink_on = ifelse(luminance(fill_of(log_position(shade))) > 0.4,
                      ink, "#FFFFFF")
    )

  # The grid keeps all its weeks, so the figure is the same shape every week.
  weeks <- c(min(cal$day), max(cal$day) - (as.integer(format(max(cal$day), "%u")) - 1L))
  firsts <- seq(as.Date(format(min(cal$day), "%Y-%m-01")), max(cal$day),
                by = "month")
  firsts <- firsts[firsts >= weeks[1]]
  month_weeks <- firsts - (as.integer(format(firsts, "%u")) - 1L)

  # A stepped line around the first of each month, through the gaps between
  # squares, as on GitHub: the first's column splits between the two months.
  month_lines <- purrr::map(firsts[firsts > min(cells$day)], \(d) {
    w <- d - (as.integer(format(d, "%u")) - 1L)
    k <- as.integer(format(d, "%u"))
    step <- 8 - k + 0.5
    if (k == 1L) {
      tibble::tibble(x = w - 3.5, y = c(7.5, 0.5))
    } else {
      tibble::tibble(x = c(w + 3.5, w + 3.5, w - 3.5, w - 3.5),
                     y = c(7.5, step, step, 0.5))
    }
  }) |>
    dplyr::bind_rows(.id = "month")

  ggplot(cells, aes(week, row)) +
    geom_tile(aes(fill = shade), width = 6, height = 0.86) +
    geom_path(data = month_lines, aes(x, y, group = month),
              colour = "grey45", linewidth = 0.5, linejoin = "mitre") +
    geom_tile(data = dplyr::filter(cells, waiting),
              aes(linetype = "Waiting"),
              fill = NA, colour = ink, width = 6, height = 0.86,
              linewidth = 0.45) +
    geom_text(data = flagged_cells, aes(label = label),
              colour = flagged_cells$ink_on, size = 3.3, fontface = "bold") +
    scale_fill_gradientn(
      colours = strength_ramp, values = strength_values, trans = "log10",
      limits = strength_limits, breaks = strength_breaks,
      labels = \(x) paste0(x, "x"), oob = scales::squish, na.value = no_data,
      name = "Strongest method"
    ) +
    scale_linetype_manual(values = "11", name = NULL) +
    scale_x_date(breaks = month_weeks,
                 labels = format(firsts, "%b"),
                 limits = c(weeks[1] - 4L, weeks[2] + 4L), expand = c(0, 0)) +
    scale_y_continuous(breaks = c(7, 5, 3), labels = c("Mon", "Wed", "Fri"),
                       limits = c(0.5, 7.5), expand = c(0, 0)) +
    coord_fixed(ratio = 7) +
    guides(
      fill = guide_colourbar(order = 1, barheight = unit(3.2, "cm"),
                             barwidth = unit(0.35, "cm")),
      linetype = guide_legend(order = 2,
                              override.aes = list(fill = strength_ramp[2]))
    ) +
    theme_cds(base_size = 9) +
    theme(
      panel.border = element_blank(), panel.grid = element_blank(),
      axis.ticks = element_blank(), axis.title = element_blank(),
      axis.text = element_text(colour = "grey35"),
      # Pushed down, clear of the logo in the top right corner.
      legend.position = "right", legend.justification = "top",
      legend.box.margin = margin(t = 28),
      legend.key.size = unit(0.4, "cm"), legend.text = element_text(size = 8),
      legend.title = element_text(size = 8), legend.spacing.y = unit(0.1, "cm")
    )
}

# Two panels on one date axis: volume, with days that fired highlighted, and
# the ratio against its threshold, on `ratio_scale`.
method_figure <- function(rows, volume, volume_label, volume_note,
                          ratio_label, ratio_cut, ratio_cut_label, top = NULL,
                          ratio_scale = scale_y_continuous(
                            labels = label_percent(), limits = c(0, 1)
                          )) {
  rows <- rows |>
    dplyr::filter(day >= chart_from) |>
    dplyr::mutate(
      volume = .data[[volume]],
      kind = dplyr::case_when(fired %in% TRUE ~ "fired",
                              day_type(day) == "weekend" ~ "weekend",
                              .default = "weekday")
    )
  fills <- c(fired = robot$accent, weekday = robot$quiet,
             weekend = grDevices::adjustcolor(robot$quiet, alpha.f = 0.5))
  limits <- c(chart_from - 1L, through + 1L)

  limits_x <- scale_x_date(limits = limits, expand = c(0, 0))
  no_x_text <- theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())

  # A page may bring its own top panel; it gets this date axis either way.
  volume_panel <- if (!is.null(top)) {
    top + limits_x + no_x_text
  } else {
    ggplot(rows, aes(day, volume)) +
      geom_col(aes(fill = kind), width = 0.8) +
      scale_fill_manual(values = fills, guide = "none") +
      scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                         expand = expansion(mult = c(0, 0.06))) +
      limits_x +
      theme_cds() +
      no_x_text +
      theme(panel.grid.minor = element_blank()) +
      labs(x = NULL, y = volume_label, subtitle = volume_note)
  }

  ratio_panel <- ggplot(rows, aes(day, ratio)) +
    geom_hline(yintercept = ratio_cut, linetype = "dashed", colour = "grey45",
               linewidth = 0.4) +
    annotate("text", x = chart_from, y = ratio_cut, label = ratio_cut_label,
             hjust = 0, vjust = -0.5, size = 2.9, colour = "grey35") +
    geom_line(colour = robot$quiet, linewidth = 0.5, na.rm = TRUE) +
    geom_point(aes(colour = kind == "fired", size = kind == "fired"),
               na.rm = TRUE) +
    scale_colour_manual(values = c(`TRUE` = robot$accent, `FALSE` = "grey55"),
                        guide = "none") +
    scale_size_manual(values = c(`TRUE` = 2.2, `FALSE` = 0.8), guide = "none") +
    ratio_scale +
    scale_x_date(limits = limits, expand = c(0, 0),
                 breaks = rev(seq(through, chart_from, by = "-2 weeks")),
                 date_labels = "%b %d") +
    theme_cds() +
    theme(panel.grid.minor = element_blank()) +
    labs(x = NULL, y = ratio_label)

  cowplot::plot_grid(volume_panel, ratio_panel, ncol = 1, align = "v",
                     axis = "lr", rel_heights = c(1.4, 1))
}

# The quarter's daily numbers, newest first. The ratio is a percentage, or
# whole seconds.
daily_table <- function(rows, columns, labels, ratio_unit = "percent") {
  table <- rows |>
    dplyr::filter(day >= chart_from) |>
    dplyr::arrange(dplyr::desc(day)) |>
    dplyr::mutate(
      day = paste(format(day, "%a"), format_short_date(day)),
      multiple = fmt_multiple(multiple),
      fired = fired %in% TRUE
    ) |>
    dplyr::select(day, dplyr::all_of(columns), multiple, ratio, fired) |>
    gt() |>
    cols_align("right", multiple) |>
    fmt_number(dplyr::all_of(columns), decimals = 0)
  table <- if (ratio_unit == "seconds") {
    fmt_number(table, ratio, decimals = 0, pattern = "{x} s")
  } else {
    fmt_percent(table, ratio, decimals = 0)
  }
  table |>
    sub_missing(missing_text = "-") |>
    cols_label(.list = c(list(day = "Day"), labels,
                         list(multiple = "vs typical day"))) |>
    # The highlight alone marks a day that fired; a day not scored shows a
    # dash under "vs typical day".
    tab_style(style = cell_text(weight = "bold", color = robot$accent),
              locations = cells_body(rows = fired)) |>
    cols_hide(fired) |>
    tab_options(table.width = pct(100), table.font.size = px(14),
                data_row.padding = px(3), table.border.top.style = "none")
}

# Methods with no score at the start of the calendar, for the note under it.
late_starts <- purrr::imap(scored, \(rows, m) {
  first <- min(rows$day[!is.na(rows$fired)])
  if (first > calendar_from) first else NULL
}) |> purrr::compact()
```

# Overview

```{r overview-summary}
#| include: false
flagged <- dplyr::filter(calendar, n_fired > 0) |> dplyr::arrange(dplyr::desc(day))

# The note under the calendar. Methods that start on the same day share a
# sentence.
starts <- tibble::tibble(method = names(late_starts),
                         day = do.call(c, unname(late_starts)))
calendar_note <- c(
  if (length(late_starts) > 0) "Blank days have no method scored yet.",
  purrr::map_chr(split(starts$method, starts$day), \(m) {
    d <- starts$day[match(m[1], starts$method)]
    glue("{glue_collapse(method_label(m), sep = ', ', last = ' and ')} ",
         "{if (length(m) > 1) 'have' else 'has'} no score before ",
         "{format_short_date(d)}: too few earlier days to compare with.")
  }),
  if (any(calendar$waiting)) {
    "The newest days have a dotted outline until slower sources catch up."
  }
) |> paste(collapse = " ")

shaded_days <- if (nrow(flagged) == 0) {
  "none"
} else {
  glue_collapse(format_short_date(flagged$day), sep = ", ", last = " and ")
}

calendar_alt <- glue(
  "Calendar grid of the last six months, one column per week and one row per ",
  "weekday, each day shaded by how far its strongest method was above a ",
  "typical day: greys for days no method flagged, amber to brown for ",
  "flagged days. ",
  "Flagged days are labelled with their strongest method's multiple. ",
  "{nrow(flagged)} days are flagged: {shaded_days}."
)
```

## Row {height="auto"}

::: {.card title="Reading this dashboard"}

This dashboard looks for **automated traffic on CanadaLogin**: scripts and bots
rather than people. It is internal to Enterprise Digital Credentials and the
link is unlisted. For anything that leaves EDCP, please reach out to the
[Data and Research team](https://gcdigital.slack.com/archives/C0A6S9F7KV4).

It uses **five methods**, each on its own page: [SMS codes](#sms-codes),
[SMS location](#sms-location), [Idle accounts](#idle-accounts),
[Sign-up speed](#sign-up-speed) and [Error patterns](#error-patterns). Each
page explains how its method works and when it fires. The last page,
[Extra costs](#extra-costs), estimates what the flagged days cost. The calendar below
shades every day by its strongest method and labels the days a method flagged.
As we find more methods, we will add them here.

**A flag is a suspicion, not a finding.** It says the day looked different from typical 
usage. Further investigation is needed to determine if the flagged activity is truly
automated.

:::

## Row {height="auto"}

::: {.card title="Days flagged"}

```{r calendar}
#| fig-width: 11
#| fig-height: 2.9
#| fig-alt: !expr calendar_alt
brand_figure(calendar_plot(calendar), height = 0.12)
```

::: {.figure-note}
A flagged day shows its *strongest* method from the table below, rounded. `r calendar_note`
:::

:::

## Row {height="auto"}

::: {.card title="Flagged days"}

```{r flagged-table}
if (nrow(flagged) == 0) {
  cat("No method fired in the last six months.")
} else {
  flagged |>
    dplyr::mutate(
      day_label = paste(format(day, "%a"), format_short_date(day)),
      count = glue("{n_fired} of {nrow(methods)}"),
      which = purrr::map_chr(methods_fired, \(m) {
        pages <- methods[methods$method %in% m, ]
        glue_collapse(glue("[{pages$label}](#{pages$page})"), sep = ", ")
      }),
      strongest = fmt_multiple(strongest)
    ) |>
    dplyr::select(day_label, count, which, strongest) |>
    gt() |>
    fmt_markdown(which) |>
    cols_label(day_label = "Day", count = "Methods", which = "Which",
               strongest = "Strongest") |>
    tab_options(table.width = pct(100), table.font.size = px(14),
                data_row.padding = px(4), table.border.top.style = "none")
}
```

::: {.figure-note}
*Strongest* is the largest volume any method that fired reached, against
that method's typical day.
:::

:::

# SMS codes

```{r sms-summary}
#| include: false
sms_rows <- scored$sms
sms_flag <- last_flag(sms_rows, chart_from, "sms_sent",
                      thresholds$baseline_days)

phone_rows <- sms_phone_days(con) |>
  dplyr::filter(day >= chart_from, day <= through) |>
  dplyr::mutate(fired = day %in% sms_rows$day[sms_rows$fired %in% TRUE])
typical_per_phone <- stats::median(phone_rows$per_phone[!phone_rows$fired])
busiest_phone <- dplyr::slice_max(phone_rows, top_phone, n = 1, with_ties = FALSE)
phones_alt <- glue(
  "Line chart of SMS codes sent per phone number each day for the last three ",
  "months, about {number(typical_per_phone, accuracy = 0.1)} on a typical ",
  "day, with days this method fired in amber. The most codes to one number ",
  "in a day was {busiest_phone$top_phone}."
)
```

## Row {height="auto"}

::: {.card title="How this method works"}
When a user needs to prove they control a phone number, CanadaLogin texts a 
one-time-password to that number, and the user types it back. Real users enter about 96%
 of their codes correctly. A bot flooding the sign-up page sends codes that nobody 
 enters. This method fires when **codes sent are at least `r thresholds$sms$volume`x a typical day** and **fewer than `r percent(thresholds$sms$entry_rate_below)` are
 entered**.
:::

## Row {height="150px"}

::: {.valuebox color="primary"}
Last flagged day

`r fmt_flag_day(sms_flag$day)`

`r flag_count_line(sms_flag)`
:::

::: {.valuebox color="info"}
SMS codes sent, last flagged day

`r fmt_count(sms_flag$volume)`

`r multiple_line(sms_flag)`
:::

::: {.valuebox color="secondary"}
Codes entered, last flagged day

`r fmt_share(sms_flag$ratio)`

`r typical_line(sms_flag, fmt_share)`
:::

## Row {height="560px"}

::: {.card title="SMS codes sent and entered each day (last three months)"}

```{r sms-chart}
#| fig-width: 13
#| fig-height: 4.8
#| fig-alt: |
#|   Two charts on a shared date axis. Above, SMS codes sent each day, with
#|   flagged days in amber. Below, the share of codes entered each day, near
#|   96 percent on most days, with a dashed line at 50 percent.
p <- method_figure(
  sms_rows,
  volume = "sms_sent", volume_label = "SMS codes sent",
  volume_note = glue("Fires at {thresholds$sms$volume}x a typical day or ",
                     "more. Lighter bars are weekends, compared only with ",
                     "weekends."),
  ratio_label = "Entered correctly", ratio_cut = thresholds$sms$entry_rate_below,
  ratio_cut_label = glue("Fires below {percent(thresholds$sms$entry_rate_below)}")
)
brand_figure(p)
```

:::

## Row {height="470px"}

::: {.card title="SMS codes per phone number each day (last three months)"}

```{r sms-phones-chart}
#| fig-width: 13
#| fig-height: 3.2
#| fig-alt: !expr phones_alt
p <- ggplot(phone_rows, aes(day, per_phone)) +
  geom_line(colour = robot$quiet, linewidth = 0.5) +
  geom_point(aes(colour = fired, size = fired)) +
  scale_colour_manual(values = c(`TRUE` = robot$accent, `FALSE` = "grey55"),
                      guide = "none") +
  scale_size_manual(values = c(`TRUE` = 2.2, `FALSE` = 0.8), guide = "none") +
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.06))) +
  scale_x_date(limits = c(chart_from - 1L, through + 1L), expand = c(0, 0),
               breaks = rev(seq(through, chart_from, by = "-2 weeks")),
               date_labels = "%b %d") +
  theme_cds() +
  theme(panel.grid.minor = element_blank()) +
  labs(
    x = NULL, y = "Codes per number",
    subtitle = glue(
      "About {number(typical_per_phone, accuracy = 0.1)} on a typical day. ",
      "The most to one number was {busiest_phone$top_phone}, on ",
      "{format_short_date(busiest_phone$day)}."
    )
  )
brand_figure(p, height = 0.13)
```

::: {.figure-note}
Not part of the flag. A person rarely needs more than one or two codes a day.
Many codes to the same numbers can be a sign of SMS fraud, where a bot runs up
texts that are billed per code. Phone numbers are hashed before they reach us,
so this counts numbers without seeing them.
:::

:::

## Row

::: {.card title="Each day (last three months)"}

```{r sms-table}
sms_rows |>
  dplyr::select(day, sms_sent, sms_success, multiple, ratio, fired) |>
  daily_table(c("sms_sent", "sms_success"),
              list(sms_sent = "SMS sent", sms_success = "SMS entered")) |>
  cols_label(ratio = "Entered")
```

:::

# SMS location

```{r location-summary}
#| include: false
location_rows <- scored$location
location_flag <- last_flag(location_rows, chart_from, "sms_sent",
                           thresholds$baseline_days)
```

## Row {height="auto"}

::: {.card title="How this method works"}
Almost every SMS code is requested from Canada or the US. On a typical day,
only a few percent come from anywhere else. This method fires when **codes
sent are at least
`r thresholds$location$volume`x a typical day** and **at least
`r percent(thresholds$location$share_at_least)` of them were requested from
outside Canada and the US**. The location comes from the requester's IP
address, so a bot using a Canadian or US address leaves no trace here.
:::

## Row {height="150px"}

::: {.valuebox color="primary"}
Last flagged day

`r fmt_flag_day(location_flag$day)`

`r flag_count_line(location_flag)`
:::

::: {.valuebox color="info"}
SMS codes sent, last flagged day

`r fmt_count(location_flag$volume)`

`r multiple_line(location_flag)`
:::

::: {.valuebox color="secondary"}
Share from outside, last flagged day

`r fmt_share(location_flag$ratio)`

`r typical_line(location_flag, fmt_share)`
:::

## Row {height="560px"}

::: {.card title="SMS codes sent each day, and the share from outside Canada and the US (last three months)"}

```{r location-chart}
#| fig-width: 13
#| fig-height: 4.8
#| fig-alt: |
#|   Two charts on a shared date axis. Above, SMS codes sent each day, with
#|   flagged days in amber. Below, the share of codes requested from outside
#|   Canada and the US each day, near zero on most days, with a dashed line
#|   at 30 percent.
p <- method_figure(
  location_rows,
  volume = "sms_sent", volume_label = "SMS codes sent",
  volume_note = glue("Fires at {thresholds$location$volume}x a typical day or ",
                     "more. Lighter bars are weekends, compared only with ",
                     "weekends."),
  ratio_label = "Outside Canada and the US",
  ratio_cut = thresholds$location$share_at_least,
  ratio_cut_label = glue("Fires at ",
                         "{percent(thresholds$location$share_at_least)} or more")
)
brand_figure(p)
```

:::

## Row

::: {.card title="Each day (last three months)"}

```{r location-table}
location_rows |>
  dplyr::select(day, sms_sent, sms_outside, multiple, ratio, fired) |>
  daily_table(c("sms_sent", "sms_outside"),
              list(sms_sent = "SMS sent",
                   sms_outside = "Outside Canada and the US")) |>
  cols_label(ratio = "Share outside")
```

:::

# Idle accounts

```{r idle-summary}
#| include: false
idle_rows <- scored$idle
idle_flag <- last_flag(idle_rows, chart_from, "new_accounts",
                       thresholds$baseline_days)
launch_latest <- since_launch[since_launch$date == through, ]

idle_flag_days <- dplyr::filter(idle_rows, fired %in% TRUE)$day

by_week <- accounts_by_week(since_launch)
```

## Row {height="auto"}

::: {.card title="How this method works"}
When real users sign up for a CanadaLogin account, they are doing so to reach a public 
service. Most go straight to it. On a typical day, only about 18% of new accounts don't.
Often, a bot making accounts in bulk leaves them idle. This method fires when **new accounts 
are at least `r thresholds$idle$volume`x a typical day** and **at least
`r percent(thresholds$idle$idle_share_at_least)` of them are idle on the day they were 
made**.
:::

## Row

### Column {.tabset}

#### Detection

##### Row {height="150px"}

::: {.valuebox color="primary"}
Last flagged day

`r fmt_flag_day(idle_flag$day)`

`r flag_count_line(idle_flag)`
:::

::: {.valuebox color="info"}
New accounts, last flagged day

`r fmt_count(idle_flag$volume)`

`r multiple_line(idle_flag)`
:::

::: {.valuebox color="secondary"}
Idle on the day made, last flagged day

`r fmt_share(idle_flag$ratio)`

`r typical_line(idle_flag, fmt_share)`
:::

##### Row {height="560px"}

::: {.card title="New accounts each day, and the share idle on the day made (last three months)"}

```{r idle-chart}
#| fig-width: 13
#| fig-height: 4.8
#| fig-alt: |
#|   Two charts on a shared date axis. Above, new accounts each day, with
#|   flagged days in amber. Below, the share of new accounts idle on the day
#|   they were made, with a dashed line at 50 percent.
p <- method_figure(
  idle_rows,
  volume = "new_accounts", volume_label = "New accounts",
  volume_note = glue("Fires at {thresholds$idle$volume}x a typical day or ",
                     "more. Lighter bars are weekends, compared only with ",
                     "weekends."),
  ratio_label = "Idle on the day made",
  ratio_cut = thresholds$idle$idle_share_at_least,
  ratio_cut_label = glue("Fires at ",
                         "{percent(thresholds$idle$idle_share_at_least)} or more")
)
brand_figure(p)
```

:::

##### Row

::: {.card title="Each day (last three months)"}

```{r idle-table}
idle_rows |>
  dplyr::select(day, new_accounts, idle_same_day, multiple, ratio, fired) |>
  daily_table(c("new_accounts", "idle_same_day"),
              list(new_accounts = "New accounts",
                   idle_same_day = "Idle on the day made")) |>
  cols_label(ratio = "Share idle")
```

:::

#### Accounts since launch

##### Row {height="150px"}

::: {.valuebox color="primary"}
All accounts, `r format_short_date(through)`

`r comma(launch_latest$all_accounts)`

Since the April 2026 launch
:::

::: {.valuebox color="info"}
Idle accounts

`r comma(launch_latest$idle_accounts)`

`r percent(launch_latest$idle_share, accuracy = 1)` of all accounts
:::

::: {.valuebox color="secondary"}
Signed in to a service

`r comma(launch_latest$signed_in_to_service)`

At least one partner service
:::

##### Row {height="560px"}

::: {.card title="Accounts since launch, by week"}

```{r launch-chart}
#| fig-width: 13
#| fig-height: 4.6
#| fig-alt: |
#|   Line chart of CanadaLogin accounts since the April 2026 launch, one point
#|   per week: all accounts, and accounts that have signed in to a partner
#|   service. The gap between the lines is idle accounts. Ticks along the
#|   bottom mark days flagged on the Detection tab.
# Each week's point sits on its last day so far (`date`, not `week_end`), so
# an unfinished week does not plot ahead of the data.
weekly <- by_week |>
  tidyr::pivot_longer(c(all_accounts, signed_in_to_service),
                      names_to = "measure", values_to = "accounts")

line_labels <- c(all_accounts = "All accounts",
                 signed_in_to_service = "Signed in to a service")
line_colours <- c(all_accounts = robot$accent, signed_in_to_service = ink)

ends <- dplyr::filter(weekly, date == max(date))

p <- ggplot(weekly, aes(date, accounts, colour = measure)) +
  geom_segment(data = tibble::tibble(day = idle_flag_days),
               aes(x = day, xend = day, y = 0, yend = max(weekly$accounts) * 0.04),
               inherit.aes = FALSE, colour = "grey35", linewidth = 0.6) +
  annotate("text", x = min(idle_flag_days, through), y = max(weekly$accounts) * 0.06,
           label = "Flagged on Detection tab", hjust = 1.05, vjust = 0,
           size = 2.9, colour = "grey35") +
  geom_line(linewidth = 1) +
  geom_point(data = ends, size = 2.4) +
  geom_text(data = ends,
            aes(label = paste0(comma(accounts), "  ", line_labels[measure])),
            hjust = -0.08, fontface = "bold", size = 3.3, show.legend = FALSE) +
  scale_colour_manual(values = line_colours, guide = "none") +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.06))) +
  # Breaks stop at the data; the right padding is room for the end labels.
  scale_x_date(breaks = rev(seq(through, min(weekly$date), by = "-4 weeks")),
               date_labels = "%b %d", expand = expansion(mult = c(0.02, 0.32))) +
  theme_cds() +
  theme(panel.grid.minor = element_blank()) +
  labs(x = NULL, y = "Accounts since launch",
       subtitle = glue("Each week's last day, through {format_short_date(through)}."))
brand_figure(p)
```

:::

##### Row {height="auto"}

::: {.card title="Accounts by week"}

```{r accounts-weekly-table}
by_week |>
  dplyr::arrange(dplyr::desc(week_end)) |>
  dplyr::transmute(
    week = ifelse(date < week_end,
                  paste(format_short_date(week_end), "(to date)"),
                  format_short_date(week_end)),
    all_accounts, idle_accounts, signed_in_to_service, idle_share, new_accounts
  ) |>
  gt() |>
  fmt_number(c(all_accounts, idle_accounts, signed_in_to_service, new_accounts),
             decimals = 0) |>
  fmt_percent(idle_share, decimals = 0) |>
  cols_label(week = "Week ending", all_accounts = "All accounts",
             idle_accounts = "Idle accounts",
             signed_in_to_service = "Signed in to a service",
             idle_share = "Idle share", new_accounts = "New that week") |>
  tab_options(table.width = pct(100), table.font.size = px(14),
              data_row.padding = px(3), table.border.top.style = "none")
```

::: {.figure-note}
Weeks run Monday to Sunday, as on Sign-In Activity. Each count is as of the end
of the week, and earlier weeks do not change. *Idle accounts* had not yet signed
in to any partner service; *signed in to a service* had signed in to at least
one, and the two add up to *all accounts*. *New that week* is accounts made in
the week. An idle account is not necessarily automated: some people make an
account and never use it.
:::

:::

# Sign-up speed

```{r speed-summary}
#| include: false
speed_rows <- scored$speed
speed_flag <- last_flag(speed_rows, chart_from, "codes_entered",
                        thresholds$baseline_days)
```

## Row {height="auto"}

::: {.card title="How this method works"}
A new account confirms its email address by entering a code that CanadaLogin
emails to it. A person has to open the email and type the code, which takes
about 20 seconds. A bot that reads its mail by machine takes a second or two.
This method fires when **email codes entered are at least
`r thresholds$speed$volume`x a typical day** and **the median code is entered
in under `r thresholds$speed$median_seconds_below` seconds**. A bot that
waits before entering its codes leaves no trace here.
:::

## Row {height="150px"}

::: {.valuebox color="primary"}
Last flagged day

`r fmt_flag_day(speed_flag$day)`

`r flag_count_line(speed_flag)`
:::

::: {.valuebox color="info"}
Email codes entered, last flagged day

`r fmt_count(speed_flag$volume)`

`r multiple_line(speed_flag)`
:::

::: {.valuebox color="secondary"}
Median time to enter, last flagged day

`r fmt_seconds(speed_flag$ratio)`

`r typical_line(speed_flag, fmt_seconds)`
:::

## Row {height="560px"}

::: {.card title="Email codes entered each day, and the median time to enter one (last three months)"}

```{r speed-chart}
#| fig-width: 13
#| fig-height: 4.8
#| fig-alt: |
#|   Two charts on a shared date axis. Above, email codes entered each day,
#|   with flagged days in amber. Below, the median seconds from an email code
#|   being sent to being entered each day, near 20 seconds on most days, with
#|   a dashed line at 10 seconds.
p <- method_figure(
  speed_rows,
  volume = "codes_entered", volume_label = "Email codes entered",
  volume_note = glue("Fires at {thresholds$speed$volume}x a typical day or ",
                     "more. Lighter bars are weekends, compared only with ",
                     "weekends."),
  ratio_label = "Median time to enter",
  ratio_cut = thresholds$speed$median_seconds_below,
  ratio_cut_label = glue("Fires below ",
                         "{thresholds$speed$median_seconds_below} seconds"),
  ratio_scale = scale_y_continuous(labels = \(x) paste0(x, " s"),
                                   limits = c(0, NA))
)
brand_figure(p)
```

:::

## Row

::: {.card title="Each day (last three months)"}

```{r speed-table}
speed_rows |>
  dplyr::select(day, codes_entered, multiple, ratio, fired) |>
  daily_table("codes_entered", list(codes_entered = "Email codes entered"),
              ratio_unit = "seconds") |>
  cols_label(ratio = "Median time")
```

::: {.figure-note}
*Email codes entered* are those sent by the sign-up service, mostly to new
accounts, timed from the code being sent to it being entered.
:::

:::

# Error patterns

```{r errors-summary}
#| include: false
error_rows <- scored$errors
errors_flag <- last_flag(error_rows, chart_from, "signature",
                         thresholds$baseline_days)
```

## Row {height="auto"}

::: {.card title="How this method works"}
Four errors are rare on a normal day: invalid phone numbers, SMS limits, wrong
codes and interrupted sign-ins. When a bot works through sign-up, they rise
together. This method fires when **at least
`r thresholds$errors$groups_at_least` of the 4 are each
`r thresholds$errors$group_volume`x their typical day** and **together
they are at least `r percent(thresholds$errors$share_at_least)` of all
errors**. A bot that doesn't use a normal browser leaves no trace here.
:::

## Row {height="150px"}

::: {.valuebox color="primary"}
Last flagged day

`r fmt_flag_day(errors_flag$day)`

`r flag_count_line(errors_flag)`
:::

::: {.valuebox color="info"}
Signature errors, last flagged day

`r fmt_count(errors_flag$volume)`

`r multiple_line(errors_flag)`
:::

::: {.valuebox color="secondary"}
Share of all errors, last flagged day

`r fmt_share(errors_flag$ratio)`

`r typical_line(errors_flag, fmt_share)`
:::

## Row {height="560px"}

::: {.card title="Error events each day, and the signature errors' share (last three months)"}

```{r errors-chart}
#| fig-width: 13
#| fig-height: 4.8
#| fig-alt: |
#|   Two charts on a shared date axis. Above, stacked bars of error events
#|   each day, the four signature errors in colour and all others in grey,
#|   with a marker above each flagged day. Below, the signature errors' share
#|   of all errors each day, with a dashed line at 30 percent.
# Signature errors in brand colours other than orange, since amber means
# "fired". Each legend label has its error codes on a second line.
group_codes <- purrr::map_chr(names(signature_labels), \(g) {
  paste(names(signature_groups)[signature_groups == g], collapse = ", ")
})
error_groups <- c(
  setNames(paste0(signature_labels, "\n", group_codes), names(signature_labels)),
  other = "All other errors"
)
error_colours <- c(
  phone_invalid = unname(colors$brand["red"]),
  sms_limit = unname(colors$brand["blue"]),
  interrupted = unname(colors$brand["forest"]),
  wrong_code = unname(colors$brand["green"]),
  other = "#C9CED4"
)

error_stack <- error_rows |>
  dplyr::filter(day >= chart_from) |>
  dplyr::mutate(other = all_errors - signature) |>
  tidyr::pivot_longer(dplyr::all_of(names(error_groups)),
                      names_to = "group", values_to = "events") |>
  # The first level stacks on top, so grey caps each bar.
  dplyr::mutate(group = factor(group, rev(names(error_groups))))

error_fired <- error_rows |>
  dplyr::filter(day >= chart_from, fired %in% TRUE)

error_top <- ggplot(error_stack, aes(day, events)) +
  geom_col(aes(fill = group), width = 0.85) +
  geom_point(data = error_fired, aes(day, all_errors), shape = 25,
             fill = robot$accent, colour = robot$accent, size = 2.2,
             position = position_nudge(y = max(error_rows$all_errors) * 0.04)) +
  scale_fill_manual(values = error_colours, labels = error_groups,
                    breaks = names(error_groups), name = NULL) +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.1))) +
  guides(fill = guide_legend(nrow = 1)) +
  theme_cds() +
  # Room after each label, or the long codes run into the next key.
  theme(panel.grid.minor = element_blank(), legend.position = "top",
        legend.justification = "left", legend.key.size = unit(0.35, "cm"),
        legend.text = element_text(margin = margin(r = 14)),
        legend.margin = margin(0, 0, 0, 0)) +
  labs(x = NULL, y = "Error events per day")

p <- method_figure(
  error_rows,
  volume = "signature", volume_label = NULL, volume_note = NULL,
  top = error_top,
  ratio_label = "Share of all errors",
  ratio_cut = thresholds$errors$share_at_least,
  ratio_cut_label = glue("Fires at {percent(thresholds$errors$share_at_least)} or more")
)
brand_figure(p)
```

:::

## Row

::: {.card title="Each day (last three months)"}

```{r errors-table}
error_rows |>
  dplyr::select(day, dplyr::all_of(names(signature_labels)), all_errors,
                multiple, ratio, fired) |>
  daily_table(c(names(signature_labels), "all_errors"),
              c(as.list(signature_labels), list(all_errors = "All errors"))) |>
  cols_label(ratio = "Signature share")
```

:::

# Extra costs

```{r costs-summary}
#| include: false
months <- cost_months(through)
cost_days <- flagged_any(scored, months[1])
sms_billed <- sms |>
  dplyr::group_by(month = month_start(day)) |>
  dplyr::summarise(volume = sum(sms_sent), .groups = "drop")
sms_costs <- extra_cost_by_month(scored$sms, cost_days, "sms_sent",
                                 sms_billed, sms_price_tiers, months)
account_costs <- extra_cost_by_month(scored$idle, cost_days, "new_accounts",
                                     active_users_by_month(con),
                                     user_price_tiers, months)
costs <- tibble::tibble(
  month = month_label(months, through),
  sms_extra = sms_costs$extra,
  sms_cost = sms_costs$cost,
  account_extra = account_costs$extra,
  account_cost = account_costs$cost
)
costs <- dplyr::bind_rows(
  costs,
  dplyr::summarise(costs, month = "Total",
                   dplyr::across(-month, sum))
)
```

## Row {height="auto"}

::: {.card title="How we estimate the costs"}
We count only the `r length(cost_days)`
`r if (length(cost_days) == 1) "day" else "days"` any method flagged in the last
12 months. On each, the extra is how far SMS codes sent and new accounts went
above a typical day.

Each extra is priced at an estimate of what one more costs that month, before
tax. Prices are lower per unit at higher monthly volumes.

- An extra SMS code costs the price per code at the month's total codes sent.
- An extra account costs the price of one monthly active user at the month's
  total active users. We assume an extra account is active only in the month
  it was made.

The cost is the extra times the price. Fixed monthly charges are left out,
since they do not change with traffic. A month not yet over is priced at its
volume so far.
:::

## Row

::: {.card title="Estimated extra costs by month"}

```{r costs-table}
costs |>
  gt() |>
  fmt_number(c(sms_extra, account_extra), decimals = 0) |>
  fmt_currency(c(sms_cost, account_cost), decimals = 0) |>
  sub_missing(missing_text = "-") |>
  cols_merge(c(sms_extra, sms_cost), pattern = "{1} ({2})") |>
  cols_merge(c(account_extra, account_cost), pattern = "{1} ({2})") |>
  cols_label(month = "", sms_extra = "Extra SMS codes (cost)",
             account_extra = "Extra new accounts (cost)") |>
  tab_style(cell_text(weight = "bold"),
            cells_body(rows = month == "Total")) |>
  tab_options(table.width = pct(100), table.font.size = px(14),
              data_row.padding = px(3), table.border.top.style = "none")
```

:::

```{r cleanup}
#| include: false
# include: false matters for layout: this chunk sits in the last Row, where
# anything visible becomes a card and takes width from the table.
DBI::dbDisconnect(con)
```

{{< include ../../_analytics.qmd >}}
