---
title: "CanadaLogin Automated Traffic"
author: "EDCP Data and Research Team"  # colin.douglas@cds-snc.ca
slug: autotraffic
format:
  dashboard:
    # Written by the setup chunk at render time
    include-before-body: page-header.html
    include-after-body: analytics-tag.html # see _analytics.qmd
params:
  ga_page_title: "Automated Traffic Dashboard"
---

```{r setup}
# Thresholds ------------------------------------------------------------------
#
# Every number that decides whether a method fires. Calibrated on 2026-10-07
# against the confirmed bot days below. A change here changes what the
# dashboard flags, so it goes through a PR; the known-days-fire preflight
# check fails if an edit stops a confirmed day firing.
thresholds <- list(
  # A day is compared with the median of the same kind of day (weekday or
  # weekend) over this many days before it, leaving out days that fired.
  baseline_days = 28L,
  # Fewer baseline days than this and the day is not scored. 28 days hold
  # only 8 weekend days.
  baseline_min_days = c(weekday = 10L, weekend = 4L),
  # Codes sent at least `volume` times a typical day, and fewer than
  # `entry_rate_below` of them entered correctly.
  sms = list(volume = 3, entry_rate_below = 0.5),
  # New accounts at least `volume` times a typical day, and at least
  # `idle_share_at_least` of them idle on the day they were made.
  idle = list(volume = 2, idle_share_at_least = 0.5),
  # At least `groups_at_least` of the four signature errors each
  # `group_volume` times their own typical day (never less than
  # `group_floor` events), and together at least `share_at_least` of all
  # errors.
  errors = list(group_volume = 3, groups_at_least = 3L, group_floor = 20,
                share_at_least = 0.3)
)

# Confirmed bot days, and the methods each should fire on. Days the methods
# flag that nobody has confirmed (Sep 7 and 8) stay off this list.
known_bot_days <- tibble::tribble(
  ~day,                  ~sms, ~idle, ~errors,
  as.Date("2026-09-17"), TRUE, TRUE,  TRUE,
  as.Date("2026-09-24"), TRUE, TRUE,  TRUE,
  # Ran without a browser, or blocked GA, so no error trail.
  as.Date("2026-09-30"), TRUE, TRUE,  FALSE
)

# Setup -----------------------------------------------------------------------

# The working directory is this folder; the shared layer is two levels up.
source("../../common/setup.R")

source("R/metrics.R")
source("R/preflight.R")

library(htmltools)

con <- connect_athena()

# A failed check adds a banner. See R/preflight.R.
preflight <- run_preflight_safety_check(con, thresholds, known_bot_days)
write_preflight_status(preflight)

# Yesterday is the newest whole day; the event stream also holds today's.
through <- toronto_today() - 1L
calendar_from <- calendar_start(through)
chart_from <- calendar_start(through, chart_weeks)

pairs <- account_pairs(con)
sms <- dplyr::filter(sms_days(con), day <= through)
accounts <- account_days(pairs, through)
errors <- dplyr::filter(error_days(error_codes(con)), day <= through)

scored <- list(
  sms = score_sms(sms, thresholds),
  idle = score_idle(accounts, thresholds),
  errors = score_errors(errors, thresholds)
)
scores <- method_scores(scored)
calendar <- calendar_days(scores, calendar_from, through)
since_launch <- accounts_since_launch(pairs, through)

write_traffic_summary(calendar, through)

# The newest day each method reported, which differs: GA runs a day behind.
reported_through <- purrr::map(scored, \(rows) max(rows$day[!is.na(rows$fired)]))

through_label <- format_long_date(through)

page_header <- "page-header.html"

write_preflight_banner(preflight, page_header)

cat(
  c(
    '<div class="page-strip">',
    # "Most": GA runs a day behind the rest; the calendar's outline shows it.
    glue("  <p><strong>Most data through {through_label}.</strong> ",
         "Internal to Enterprise Digital Credentials, not for public ",
         "consumption.</p>"),
    "</div>"
  ),
  file = page_header, sep = "\n", append = TRUE
)

# Presentation ---------------------------------------------------------------

# Chart colours, mirroring _theme.scss: amber, the indicator light, only for
# what fired; slate grey for the rest.
robot <- list(accent = "#C77700", quiet = "#BFC6CD")

# The calendar shades every day by its strongest method's volume against a
# typical day, so ordinary variation shows. A log scale with fixed limits, so
# a colour means the same every week: greys up to 2x, amber from 2.5x, brown
# at the top. It darkens as it climbs, so it reads in greyscale. A day no
# method could score yet is blank.
strength_limits <- c(0.5, 50)
strength_breaks <- c(0.5, 1, 2, 5, 10, 20, 50)
strength_stops <- c(0.5, 1, 2, 2.5, 10, 50)
strength_ramp <- c("#F1F3F5", "#E3E6EA", "#D5DAE0", "#F2C55C", "#E89B00",
                   "#8F5200")
# Amber and brown mean a method fired: an unflagged day is held to the greys
# however high its volume (a launch), and a flagged day starts at amber.
unflagged_cap <- 2
flagged_floor <- 2.5
strength_values <- scales::rescale(log10(strength_stops),
                                   from = log10(strength_limits))
no_data <- "#F7F8F9"

ink <- "#1F2933"

brand_figure <- function(p, height = 0.09) {
  add_cds_logo(
    add_watermark(p, report_name = "CanadaLogin Automated Traffic",
                  date = through),
    height = height
  )
}

method_label <- function(m) methods$label[match(m, methods$method)]

# Days in a method page's charts that it fired on, newest first.
fired_days <- function(m) {
  scores |>
    dplyr::filter(method == m, fired, day >= chart_from) |>
    dplyr::arrange(dplyr::desc(day)) |>
    dplyr::pull(day)
}

days_flagged_line <- function(m) {
  days <- fired_days(m)
  if (length(days) == 0) "None in the last 13 weeks" else
    glue("Most recent {format_short_date(days[1])}")
}

# "a typical weekday", for a value box comparing a day with its baseline.
typical_day <- function(day) glue("a typical {day_type(day)}")

# Relative luminance, to pick a label colour that shows on its cell.
luminance <- function(hex) {
  rgb <- grDevices::col2rgb(hex) / 255
  rgb <- ifelse(rgb <= 0.03928, rgb / 12.92, ((rgb + 0.055) / 1.055)^2.4)
  as.vector(c(0.2126, 0.7152, 0.0722) %*% rgb)
}

weekday_names <- c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun")

# GitHub-style grid: a column per week, Monday at the top, shaded by the
# strongest method on the day. A flagged day carries its Strongest figure,
# the same as in the table below. Days before launch are left blank.
calendar_plot <- function(cal) {
  # The fill each flagged day gets, to pick a label colour that shows on it.
  fill_of <- scales::gradient_n_pal(strength_ramp, strength_values)
  log_position <- function(x) {
    clamped <- pmin(pmax(x, strength_limits[1]), strength_limits[2])
    scales::rescale(log10(clamped), from = log10(strength_limits))
  }

  cells <- cal |>
    dplyr::filter(day >= canadalogin_launch) |>
    dplyr::mutate(
      week = day - (as.integer(format(day, "%u")) - 1L),
      # Monday on top: row 7 is Monday, row 1 Sunday. Numeric, so the month
      # lines can run between rows.
      row = 8L - as.integer(format(day, "%u")),
      shade = ifelse(n_fired > 0, pmax(peak, flagged_floor),
                     pmin(peak, unflagged_cap))
    )
  flagged_cells <- cells |>
    dplyr::filter(n_fired > 0) |>
    dplyr::mutate(
      label = paste0(round(strongest), "x"),
      ink_on = ifelse(luminance(fill_of(log_position(shade))) > 0.4,
                      ink, "#FFFFFF")
    )

  # The grid keeps all its weeks, so the figure is the same shape every week.
  weeks <- c(min(cal$day), max(cal$day) - (as.integer(format(max(cal$day), "%u")) - 1L))
  firsts <- seq(as.Date(format(min(cal$day), "%Y-%m-01")), max(cal$day),
                by = "month")
  firsts <- firsts[firsts >= weeks[1]]
  month_weeks <- firsts - (as.integer(format(firsts, "%u")) - 1L)

  # A stepped line around the first of each month, through the gaps between
  # squares, as on GitHub: the first's column splits between the two months.
  month_lines <- purrr::map(firsts[firsts > min(cells$day)], \(d) {
    w <- d - (as.integer(format(d, "%u")) - 1L)
    k <- as.integer(format(d, "%u"))
    step <- 8 - k + 0.5
    if (k == 1L) {
      tibble::tibble(x = w - 3.5, y = c(7.5, 0.5))
    } else {
      tibble::tibble(x = c(w + 3.5, w + 3.5, w - 3.5, w - 3.5),
                     y = c(7.5, step, step, 0.5))
    }
  }) |>
    dplyr::bind_rows(.id = "month")

  ggplot(cells, aes(week, row)) +
    geom_tile(aes(fill = shade), width = 6, height = 0.86) +
    geom_path(data = month_lines, aes(x, y, group = month),
              colour = "grey45", linewidth = 0.5, linejoin = "mitre") +
    geom_tile(data = dplyr::filter(cells, waiting),
              aes(linetype = "Waiting"),
              fill = NA, colour = ink, width = 6, height = 0.86,
              linewidth = 0.45) +
    geom_text(data = flagged_cells, aes(label = label),
              colour = flagged_cells$ink_on, size = 3.3, fontface = "bold") +
    scale_fill_gradientn(
      colours = strength_ramp, values = strength_values, trans = "log10",
      limits = strength_limits, breaks = strength_breaks,
      labels = \(x) paste0(x, "x"), oob = scales::squish, na.value = no_data,
      name = "Strongest method"
    ) +
    scale_linetype_manual(values = "11", name = NULL) +
    scale_x_date(breaks = month_weeks,
                 labels = format(firsts, "%b"),
                 limits = c(weeks[1] - 4L, weeks[2] + 4L), expand = c(0, 0)) +
    scale_y_continuous(breaks = c(7, 5, 3), labels = c("Mon", "Wed", "Fri"),
                       limits = c(0.5, 7.5), expand = c(0, 0)) +
    coord_fixed(ratio = 7) +
    guides(
      fill = guide_colourbar(order = 1, barheight = unit(3.2, "cm"),
                             barwidth = unit(0.35, "cm")),
      linetype = guide_legend(order = 2,
                              override.aes = list(fill = strength_ramp[2]))
    ) +
    theme_cds(base_size = 9) +
    theme(
      panel.border = element_blank(), panel.grid = element_blank(),
      axis.ticks = element_blank(), axis.title = element_blank(),
      axis.text = element_text(colour = "grey35"),
      # Pushed down, clear of the logo in the top right corner.
      legend.position = "right", legend.justification = "top",
      legend.box.margin = margin(t = 28),
      legend.key.size = unit(0.4, "cm"), legend.text = element_text(size = 8),
      legend.title = element_text(size = 8), legend.spacing.y = unit(0.1, "cm")
    )
}

# Two panels on one date axis: volume, with days that fired highlighted, and
# the ratio against its threshold. The threshold line is drawn only below,
# where it is a single line rather than a mark per day.
method_figure <- function(rows, volume, volume_label, volume_note,
                          ratio_label, ratio_cut, ratio_cut_label,
                          ratio_labels = label_percent(), top = NULL) {
  rows <- rows |>
    dplyr::filter(day >= chart_from) |>
    dplyr::mutate(
      volume = .data[[volume]],
      kind = dplyr::case_when(fired %in% TRUE ~ "fired",
                              day_type(day) == "weekend" ~ "weekend",
                              .default = "weekday")
    )
  fills <- c(fired = robot$accent, weekday = robot$quiet,
             weekend = grDevices::adjustcolor(robot$quiet, alpha.f = 0.5))
  limits <- c(chart_from - 1L, through + 1L)

  limits_x <- scale_x_date(limits = limits, expand = c(0, 0))
  no_x_text <- theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())

  # A page may bring its own top panel; it gets this date axis either way.
  volume_panel <- if (!is.null(top)) {
    top + limits_x + no_x_text
  } else {
    ggplot(rows, aes(day, volume)) +
      geom_col(aes(fill = kind), width = 0.8) +
      scale_fill_manual(values = fills, guide = "none") +
      scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                         expand = expansion(mult = c(0, 0.06))) +
      limits_x +
      theme_cds() +
      no_x_text +
      theme(panel.grid.minor = element_blank()) +
      labs(x = NULL, y = volume_label, subtitle = volume_note)
  }

  ratio_panel <- ggplot(rows, aes(day, ratio)) +
    geom_hline(yintercept = ratio_cut, linetype = "dashed", colour = "grey45",
               linewidth = 0.4) +
    annotate("text", x = chart_from, y = ratio_cut, label = ratio_cut_label,
             hjust = 0, vjust = -0.5, size = 2.9, colour = "grey35") +
    geom_line(colour = robot$quiet, linewidth = 0.5, na.rm = TRUE) +
    geom_point(aes(colour = kind == "fired", size = kind == "fired"),
               na.rm = TRUE) +
    scale_colour_manual(values = c(`TRUE` = robot$accent, `FALSE` = "grey55"),
                        guide = "none") +
    scale_size_manual(values = c(`TRUE` = 2.2, `FALSE` = 0.8), guide = "none") +
    scale_y_continuous(labels = ratio_labels, limits = c(0, 1)) +
    scale_x_date(limits = limits, expand = c(0, 0),
                 breaks = rev(seq(through, chart_from, by = "-2 weeks")),
                 date_labels = "%b %d") +
    theme_cds() +
    theme(panel.grid.minor = element_blank()) +
    labs(x = NULL, y = ratio_label)

  cowplot::plot_grid(volume_panel, ratio_panel, ncol = 1, align = "v",
                     axis = "lr", rel_heights = c(1.4, 1))
}

# The quarter's daily numbers, newest first.
daily_table <- function(rows, columns, labels, decimals) {
  rows |>
    dplyr::filter(day >= chart_from) |>
    dplyr::arrange(dplyr::desc(day)) |>
    dplyr::mutate(
      day = paste(format(day, "%a"), format_short_date(day)),
      multiple = fmt_multiple(multiple),
      fired = fired %in% TRUE
    ) |>
    dplyr::select(day, dplyr::all_of(columns), multiple, ratio, fired) |>
    gt() |>
    cols_align("right", multiple) |>
    fmt_number(dplyr::all_of(columns), decimals = 0) |>
    fmt_percent(ratio, decimals = decimals) |>
    sub_missing(missing_text = "-") |>
    cols_label(.list = c(list(day = "Day"), labels,
                         list(multiple = "vs typical day"))) |>
    # The highlight alone marks a day that fired; a day not scored shows a
    # dash under "vs typical day".
    tab_style(style = cell_text(weight = "bold", color = robot$accent),
              locations = cells_body(rows = fired)) |>
    cols_hide(fired) |>
    tab_options(table.width = pct(100), table.font.size = px(14),
                data_row.padding = px(3), table.border.top.style = "none")
}

# Methods with no score at the start of the calendar: a source too new to
# have a baseline. Named in the note under the calendar.
late_starts <- purrr::imap(scored, \(rows, m) {
  first <- min(rows$day[!is.na(rows$fired)])
  if (first > calendar_from) first else NULL
}) |> purrr::compact()
```

# Overview

```{r overview-summary}
#| include: false
flagged <- dplyr::filter(calendar, n_fired > 0) |> dplyr::arrange(dplyr::desc(day))
all_three <- sum(calendar$n_fired == nrow(methods))
latest_flag <- flagged[1, ]

latest_value <- if (nrow(flagged) == 0) {
  "None"
} else {
  nbsp(format_short_date(latest_flag$day))
}
latest_line <- if (nrow(flagged) == 0) {
  "No method fired in the last six months"
} else {
  glue("{latest_flag$n_fired} of {nrow(methods)}: ",
       "{glue_collapse(method_label(latest_flag$methods_fired[[1]]), sep = ', ')}")
}

quiet_days <- if (nrow(flagged) == 0) NA else as.integer(through - latest_flag$day)
quiet_value <- if (is.na(quiet_days)) "None" else comma(quiet_days)
quiet_line <- if (is.na(quiet_days)) {
  "No method fired in the last six months"
} else {
  glue("Through {format_short_date(through)}")
}

# Why some squares have a dotted outline: a source too new to compare with,
# or one that has not caught up with the newest days.
# Methods that start on the same day share a sentence.
starts <- tibble::tibble(method = names(late_starts),
                         day = do.call(c, unname(late_starts)))
calendar_note <- c(
  if (length(late_starts) > 0) "Blank days have no method scored yet.",
  purrr::map_chr(split(starts$method, starts$day), \(m) {
    d <- starts$day[match(m[1], starts$method)]
    glue("{glue_collapse(method_label(m), sep = ', ', last = ' and ')} ",
         "{if (length(m) > 1) 'have' else 'has'} no score before ",
         "{format_short_date(d)}: too few earlier days to compare with.")
  }),
  if (any(calendar$waiting)) {
    "The newest days have a dotted outline until slower sources catch up."
  }
) |> paste(collapse = " ")

shaded_days <- if (nrow(flagged) == 0) {
  "none"
} else {
  glue_collapse(format_short_date(flagged$day), sep = ", ", last = " and ")
}

calendar_alt <- glue(
  "Calendar grid of the last six months, one column per week and one row per ",
  "weekday, each day shaded by how far its strongest method was above a ",
  "typical day: greys for days no method flagged, amber to brown for ",
  "flagged days. ",
  "Flagged days are labelled with their strongest method's multiple. ",
  "{nrow(flagged)} days are flagged: {shaded_days}."
)
```

## Row {height="auto"}

::: {.card title="Reading this dashboard"}

This dashboard looks for **automated traffic on CanadaLogin**: scripts and bots
rather than people. It is internal to Enterprise Digital Credentials and the
link is unlisted. For anything that leaves EDCP, please reach out to the
[Data and Research team](https://gcdigital.slack.com/archives/C0A6S9F7KV4).

**A red banner at the top of the page means a check failed at render time.**
Do not quote anything until it clears. One check makes sure the confirmed bot
days of September 17, 24 and 30 are still found, so a change to the rules
cannot quietly blind the dashboard.

### Three methods, three kinds of trail

Each method watches one source and compares every day with a typical day:
the median of the same kind of day (weekday or weekend) over the 28 days
before it, leaving out days that were already flagged. **A method fires only
when two things happen together**: volume well above a typical day, *and* a
ratio that real people do not produce. Volume alone is not enough. A new
service launching brings a surge of real users, and they enter their codes and
reach their service.

- **SMS codes** fires when far more codes are sent than usual and few are
  entered. Real users enter about 96% of the codes they are sent.
- **Idle accounts** fires when far more accounts are made than usual and most
  never reach a partner service that day. Real users go straight to the service
  they came for.
- **Error patterns** fires when several rare errors spike together: invalid
  phone numbers, SMS limits, wrong codes and interrupted sign-ins.

The methods catch different bots. A bot that never loads a normal browser
leaves no trace in Google Analytics, so Error patterns misses it, as on
September 30. So the calendar shades every day by its strongest method,
which shows ordinary day-to-day variation too, and labels the flagged days;
the table under it says how many methods agreed.

### What a flag means

**A flag is a suspicion, not a finding.** It says the day looked unlike real
use on that method's measures. More methods agreeing makes it more likely.
Days are in Toronto time. The numbers that decide when a method fires are
listed at the top of each method page.

:::

## Row {height="150px"}

::: {.valuebox color="primary"}
Days flagged, last six months

`r nrow(flagged)`

`r all_three` with all three methods
:::

::: {.valuebox color="info"}
Most recent flagged day

`r latest_value`

`r latest_line`
:::

::: {.valuebox color="secondary"}
Days since suspected automated traffic

`r quiet_value`

`r quiet_line`
:::

## Row {height="auto"}

::: {.card title="Days flagged, by the strongest method"}

```{r calendar}
#| fig-width: 11
#| fig-height: 2.9
#| fig-alt: !expr calendar_alt
brand_figure(calendar_plot(calendar), height = 0.12)
```

::: {.figure-note}
Each square is a day in Toronto time, shaded by its strongest method against a
typical day. Days no method flagged stay grey, however high their volume, so
amber and brown always mean a method fired. A flagged day shows its *Strongest*
figure from the table below, rounded. `r calendar_note`
:::

:::

## Row {height="auto"}

::: {.card title="Flagged days"}

```{r flagged-table}
if (nrow(flagged) == 0) {
  cat("No method fired in the last six months.")
} else {
  # The same strongest the calendar is shaded by.
  flagged |>
    dplyr::mutate(
      day_label = paste(format(day, "%a"), format_short_date(day)),
      count = glue("{n_fired} of {nrow(methods)}"),
      which = purrr::map_chr(methods_fired, \(m) {
        pages <- methods[methods$method %in% m, ]
        glue_collapse(glue("[{pages$label}](#{pages$page})"), sep = ", ")
      }),
      strongest = fmt_multiple(strongest)
    ) |>
    dplyr::select(day_label, count, which, strongest) |>
    gt() |>
    fmt_markdown(which) |>
    cols_label(day_label = "Day", count = "Methods", which = "Which",
               strongest = "Strongest") |>
    tab_options(table.width = pct(100), table.font.size = px(14),
                data_row.padding = px(4), table.border.top.style = "none")
}
```

::: {.figure-note}
*Strongest* is the largest volume any method that fired reached, against
that method's typical day.
:::

:::

# SMS codes

```{r sms-summary}
#| include: false
sms_rows <- scored$sms
sms_latest <- sms_rows[sms_rows$day == reported_through$sms, ]
sms_extra <- extra_sms(sms_rows, chart_from)
```

## Row {height="auto"}

::: {.card title="How this method works"}
CanadaLogin texts a one-time code to a phone number, and the user types it back.
A script that floods the sign-up flow with phone numbers sends codes nobody
enters, which costs money for every message. This method fires when **codes
sent are at least `r thresholds$sms$volume` times a typical day** and **fewer
than `r percent(thresholds$sms$entry_rate_below)` are entered correctly**. Real
users enter about 96%, even during a launch. Source: `ibm_verify.mfa_activity`.
Voice codes are shown for context, since a script blocked from SMS may switch
to voice; they do not count towards the flag.
:::

## Row {height="150px"}

::: {.valuebox color="primary"}
SMS codes sent, `r format_short_date(sms_latest$day)`

`r comma(sms_latest$sms_sent)`

`r fmt_multiple(sms_latest$multiple)` `r typical_day(sms_latest$day)`
:::

::: {.valuebox color="info"}
Codes entered, `r format_short_date(sms_latest$day)`

`r percent(sms_latest$ratio, accuracy = 1)`

Fires below `r percent(thresholds$sms$entry_rate_below)`
:::

::: {.valuebox color="secondary"}
Days flagged, last 13 weeks

`r length(fired_days("sms"))`

`r days_flagged_line("sms")`
:::

::: {.valuebox color="info"}
Extra SMS codes on flagged days, last 13 weeks

`r if (sms_extra == 0) "None" else nbsp(paste("About", comma(round(sms_extra, -3))))`

Sent above a typical day
:::

## Row {height="560px"}

::: {.card title="SMS codes sent and entered each day (last 13 weeks)"}

```{r sms-chart}
#| fig-width: 13
#| fig-height: 4.8
#| fig-alt: |
#|   Two charts on a shared date axis. Above, SMS codes sent each day; bars
#|   that fired are drawn in the accent colour. Below, the share of codes
#|   entered correctly each day,
#|   near 96 percent on most days, with a dashed line at 50 percent.
p <- method_figure(
  sms_rows,
  volume = "sms_sent", volume_label = "SMS codes sent",
  volume_note = glue("Fires at {thresholds$sms$volume} times a typical day or ",
                     "more. Lighter bars are weekends, compared only with ",
                     "weekends."),
  ratio_label = "Entered correctly", ratio_cut = thresholds$sms$entry_rate_below,
  ratio_cut_label = glue("Fires below {percent(thresholds$sms$entry_rate_below)}")
)
brand_figure(p)
```

:::

## Row

::: {.card title="Each day (last 13 weeks)"}

```{r sms-table}
sms_rows |>
  dplyr::select(day, sms_sent, sms_success, voice_sent, multiple, ratio, fired) |>
  daily_table(c("sms_sent", "sms_success", "voice_sent"),
              list(sms_sent = "SMS sent", sms_success = "SMS entered",
                   voice_sent = "Voice sent"), decimals = 0) |>
  cols_label(ratio = "Entered")
```

:::

# Idle accounts

```{r idle-summary}
#| include: false
idle_rows <- scored$idle
idle_latest <- idle_rows[idle_rows$day == reported_through$idle, ]
launch_latest <- since_launch[since_launch$date == through, ]

idle_flag_days <- dplyr::filter(idle_rows, fired %in% TRUE)$day

by_week <- accounts_by_week(since_launch)
```

## Row

### Column {.tabset}

#### Detection

##### Row {height="auto"}

::: {.card title="How this method works"}
An account is **idle on the day it was made** if it did not sign in to any
partner service that day. Real users sign up because they want a service, so
they go straight to it; on a typical day about 18% of new accounts are idle.
Scripts that make accounts in bulk leave them idle. This method fires when
**new accounts are at least `r thresholds$idle$volume` times a typical day**
and **at least `r percent(thresholds$idle$idle_share_at_least)` of them are
idle on the day they were made**. Source: the IBM Verify event stream
(`ibm_verify_events_raw`), which is preliminary.
:::

##### Row {height="150px"}

::: {.valuebox color="primary"}
New accounts, `r format_short_date(idle_latest$day)`

`r comma(idle_latest$new_accounts)`

`r fmt_multiple(idle_latest$multiple)` `r typical_day(idle_latest$day)`
:::

::: {.valuebox color="info"}
Idle on the day made, `r format_short_date(idle_latest$day)`

`r percent(idle_latest$ratio, accuracy = 1)`

Fires at `r percent(thresholds$idle$idle_share_at_least)` or more
:::

::: {.valuebox color="secondary"}
Days flagged, last 13 weeks

`r length(fired_days("idle"))`

`r days_flagged_line("idle")`
:::

##### Row {height="560px"}

::: {.card title="New accounts each day, and the share idle on the day made (last 13 weeks)"}

```{r idle-chart}
#| fig-width: 13
#| fig-height: 4.8
#| fig-alt: |
#|   Two charts on a shared date axis. Above, new accounts each day; bars that
#|   fired are drawn in the accent colour. Below, the share of new accounts
#|   idle on the day they
#|   were made, with a dashed line at 50 percent.
p <- method_figure(
  idle_rows,
  volume = "new_accounts", volume_label = "New accounts",
  volume_note = glue("Fires at {thresholds$idle$volume} times a typical day or ",
                     "more. Lighter bars are weekends, compared only with ",
                     "weekends."),
  ratio_label = "Idle on the day made",
  ratio_cut = thresholds$idle$idle_share_at_least,
  ratio_cut_label = glue("Fires at ",
                         "{percent(thresholds$idle$idle_share_at_least)} or more")
)
brand_figure(p)
```

:::

##### Row

::: {.card title="Each day (last 13 weeks)"}

```{r idle-table}
idle_rows |>
  dplyr::select(day, new_accounts, idle_same_day, multiple, ratio, fired) |>
  daily_table(c("new_accounts", "idle_same_day"),
              list(new_accounts = "New accounts",
                   idle_same_day = "Idle on the day made"), decimals = 0) |>
  cols_label(ratio = "Share idle")
```

:::

#### Accounts since launch

##### Row {height="150px"}

::: {.valuebox color="primary"}
All accounts, `r format_short_date(through)`

`r comma(launch_latest$all_accounts)`

Since the April 2026 launch
:::

::: {.valuebox color="info"}
Idle accounts

`r comma(launch_latest$idle_accounts)`

`r percent(launch_latest$idle_share, accuracy = 1)` of all accounts
:::

::: {.valuebox color="secondary"}
Signed in to a service

`r comma(launch_latest$signed_in_to_service)`

At least one partner service
:::

##### Row {height="560px"}

::: {.card title="Accounts since launch, by week"}

```{r launch-chart}
#| fig-width: 13
#| fig-height: 4.6
#| fig-alt: |
#|   Line chart of CanadaLogin accounts since the April 2026 launch, one point
#|   per week, for all accounts and for accounts that have signed in to a
#|   partner service. The lines rise together until mid-September, then all
#|   accounts pull away. Ticks along the bottom mark the days flagged on the
#|   Detection tab.
# Each week's point sits on its last day so far, so an unfinished week does
# not plot ahead of the data.
weekly <- by_week |>
  dplyr::mutate(week_end = date) |>
  tidyr::pivot_longer(c(all_accounts, signed_in_to_service),
                      names_to = "measure", values_to = "accounts")

line_labels <- c(all_accounts = "All accounts",
                 signed_in_to_service = "Signed in to a service")
line_colours <- c(all_accounts = robot$accent, signed_in_to_service = ink)

ends <- dplyr::filter(weekly, week_end == max(week_end))

p <- ggplot(weekly, aes(week_end, accounts, colour = measure)) +
  geom_segment(data = tibble::tibble(day = idle_flag_days),
               aes(x = day, xend = day, y = 0, yend = max(weekly$accounts) * 0.04),
               inherit.aes = FALSE, colour = "grey35", linewidth = 0.6) +
  annotate("text", x = min(idle_flag_days, through), y = max(weekly$accounts) * 0.06,
           label = "Flagged on Detection tab", hjust = 1.05, vjust = 0,
           size = 2.9, colour = "grey35") +
  geom_line(linewidth = 1) +
  geom_point(data = ends, size = 2.4) +
  geom_text(data = ends,
            aes(label = paste0(comma(accounts), "  ", line_labels[measure])),
            hjust = -0.08, fontface = "bold", size = 3.3, show.legend = FALSE) +
  scale_colour_manual(values = line_colours, guide = "none") +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.06))) +
  # Breaks stop at the data; the right padding is room for the end labels.
  scale_x_date(breaks = rev(seq(through, min(weekly$week_end), by = "-4 weeks")),
               date_labels = "%b %d", expand = expansion(mult = c(0.02, 0.32))) +
  theme_cds() +
  theme(panel.grid.minor = element_blank()) +
  labs(x = NULL, y = "Accounts since launch",
       subtitle = glue("Each week's last day, through {format_short_date(through)}."))
brand_figure(p)
```

:::

##### Row {height="auto"}

::: {.card title="Accounts by week"}

```{r accounts-weekly-table}
by_week |>
  dplyr::arrange(dplyr::desc(week_end)) |>
  dplyr::transmute(
    week = ifelse(date < week_end,
                  paste(format_short_date(week_end), "(to date)"),
                  format_short_date(week_end)),
    all_accounts, idle_accounts, signed_in_to_service, idle_share, new_accounts
  ) |>
  gt() |>
  fmt_number(c(all_accounts, idle_accounts, signed_in_to_service, new_accounts),
             decimals = 0) |>
  fmt_percent(idle_share, decimals = 0) |>
  cols_label(week = "Week ending", all_accounts = "All accounts",
             idle_accounts = "Idle accounts",
             signed_in_to_service = "Signed in to a service",
             idle_share = "Idle share", new_accounts = "New that week") |>
  tab_options(table.width = pct(100), table.font.size = px(14),
              data_row.padding = px(3), table.border.top.style = "none")
```

::: {.figure-note}
Weeks run Monday to Sunday, as on Sign-In Activity. Each count is as of the end
of the week, and earlier weeks do not change. *Idle accounts* had not yet signed
in to any partner service; *signed in to a service* had signed in to at least
one, and the two add up to *all accounts*. *New that week* is accounts made in
the week. An idle account is not necessarily automated: some people make an
account and never use it.
:::

:::

# Error patterns

```{r errors-summary}
#| include: false
error_rows <- scored$errors
errors_latest <- error_rows[error_rows$day == reported_through$errors, ]
```

## Row {height="auto"}

::: {.card title="How this method works"}
Four errors are rare on a normal day: **invalid phone numbers, SMS limits
reached, wrong one-time codes and interrupted sign-ins**.
When a script walks the SMS sign-up flow, they rise together. A single error
spiking usually means a bug or an outage instead. This method fires when **at
least `r thresholds$errors$groups_at_least` of the four are each
`r thresholds$errors$group_volume` times their typical day** (counting a
typical day as at least `r thresholds$errors$group_floor` events, so small
numbers do not jump) and **together they make up at least
`r percent(thresholds$errors$share_at_least)` of all errors**. Source:
`google_analytics.error_events`, which runs a day or two behind. A bot that
never loads a normal browser leaves no trace here.
:::

## Row {height="150px"}

::: {.valuebox color="primary"}
Signature errors up, `r format_short_date(errors_latest$day)`

`r nbsp(glue("{errors_latest$groups_up} of 4"))`

Fires at `r thresholds$errors$groups_at_least` or more
:::

::: {.valuebox color="info"}
Share of all errors, `r format_short_date(errors_latest$day)`

`r percent(errors_latest$ratio, accuracy = 1)`

Fires at `r percent(thresholds$errors$share_at_least)` or more
:::

::: {.valuebox color="secondary"}
Days flagged, last 13 weeks

`r length(fired_days("errors"))`

`r days_flagged_line("errors")`
:::

## Row {height="560px"}

::: {.card title="Error events each day, and the signature errors' share (last 13 weeks)"}

```{r errors-chart}
#| fig-width: 13
#| fig-height: 4.8
#| fig-alt: |
#|   Two charts on a shared date axis. Above, stacked bars of error events
#|   each day, the four signature errors in colour and all other errors in
#|   grey; most days are mostly grey, and on September 17 and 24 the
#|   signature errors make up most of a large spike. A small marker sits above
#|   each day the method fired. Below, the signature errors' share of all
#|   error events each day, with a dashed line at 30 percent.
# Every error each day, signature errors in colour, as in Signal Check
# edition 8. Brand red, blue, forest and green, not orange: amber here means
# "fired".
# Each signature label over its error codes, on a second line.
group_codes <- purrr::map_chr(names(signature_labels), \(g) {
  paste(names(signature_groups)[signature_groups == g], collapse = ", ")
})
error_groups <- c(
  setNames(paste0(signature_labels, "\n", group_codes), names(signature_labels)),
  other = "All other errors"
)
error_colours <- c(
  phone_invalid = unname(colors$brand["red"]),
  sms_limit = unname(colors$brand["blue"]),
  interrupted = unname(colors$brand["forest"]),
  wrong_code = unname(colors$brand["green"]),
  other = "#C9CED4"
)

error_stack <- error_rows |>
  dplyr::filter(day >= chart_from) |>
  dplyr::mutate(other = all_errors - signature) |>
  tidyr::pivot_longer(dplyr::all_of(names(error_groups)),
                      names_to = "group", values_to = "events") |>
  # The first level stacks on top, so grey caps each bar.
  dplyr::mutate(group = factor(group, rev(names(error_groups))))

error_fired <- error_rows |>
  dplyr::filter(day >= chart_from, fired %in% TRUE)

error_top <- ggplot(error_stack, aes(day, events)) +
  geom_col(aes(fill = group), width = 0.85) +
  geom_point(data = error_fired, aes(day, all_errors), shape = 25,
             fill = robot$accent, colour = robot$accent, size = 2.2,
             position = position_nudge(y = max(error_rows$all_errors) * 0.04)) +
  scale_fill_manual(values = error_colours, labels = error_groups,
                    breaks = names(error_groups), name = NULL) +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.1))) +
  guides(fill = guide_legend(nrow = 1)) +
  theme_cds() +
  # Room after each label, or the long codes run into the next key.
  theme(panel.grid.minor = element_blank(), legend.position = "top",
        legend.justification = "left", legend.key.size = unit(0.35, "cm"),
        legend.text = element_text(margin = margin(r = 14)),
        legend.margin = margin(0, 0, 0, 0)) +
  labs(x = NULL, y = "Error events per day",
       subtitle = glue("Markers: days the method fired, when at least ",
                       "{thresholds$errors$groups_at_least} of the 4 coloured ",
                       "errors were {thresholds$errors$group_volume} times ",
                       "their typical day."))

p <- method_figure(
  error_rows,
  volume = "signature", volume_label = NULL, volume_note = NULL,
  top = error_top,
  ratio_label = "Share of all errors",
  ratio_cut = thresholds$errors$share_at_least,
  ratio_cut_label = glue("Fires at {percent(thresholds$errors$share_at_least)} or more")
)
brand_figure(p)
```

:::

## Row

::: {.card title="Each day (last 13 weeks)"}

```{r errors-table}
error_rows |>
  dplyr::select(day, dplyr::all_of(names(signature_labels)), all_errors,
                multiple, ratio, fired) |>
  daily_table(c(names(signature_labels), "all_errors"),
              c(as.list(signature_labels), list(all_errors = "All errors")),
              decimals = 0) |>
  cols_label(ratio = "Signature share")
```

:::

```{r cleanup}
#| include: false
# include: false matters for layout: this chunk sits in the last Row, where
# anything visible becomes a card and takes width from the table.
DBI::dbDisconnect(con)
```

{{< include ../../_analytics.qmd >}}
