---
title: "CanadaLogin Automated Traffic"
author: "EDCP Data and Research Team"  # colin.douglas@cds-snc.ca
slug: autotraffic
format:
  dashboard:
    # Written by the setup chunk at render time
    include-before-body: page-header.html
    include-after-body: analytics-tag.html # see _analytics.qmd
params:
  ga_page_title: "Automated Traffic Dashboard"
---

```{r setup}
# Thresholds ------------------------------------------------------------------
#
# Every number that decides whether a method fires. The known-days-fire
# preflight check fails if an edit stops a confirmed day firing.
thresholds <- list(
  # A day is compared with the median of the same kind of day (weekday or
  # weekend) over this many days before it, leaving out days that fired.
  baseline_days = 28L,
  # Fewer baseline days than this and the day is not scored. 28 days hold
  # only 8 weekend days.
  baseline_min_days = c(weekday = 10L, weekend = 4L),
  # Codes sent at least `volume` times a typical day, and fewer than
  # `entry_rate_below` of them entered correctly.
  sms = list(volume = 3, entry_rate_below = 0.5),
  # New accounts at least `volume` times a typical day, and at least
  # `idle_share_at_least` of them idle on the day they were made.
  idle = list(volume = 2, idle_share_at_least = 0.5),
  # At least `groups_at_least` of the four signature errors each
  # `group_volume` times their own typical day (never less than
  # `group_floor` events), and together at least `share_at_least` of all
  # errors.
  errors = list(group_volume = 3, groups_at_least = 3L, group_floor = 20,
                share_at_least = 0.3)
)

# Confirmed bot days, and the methods each should fire on. Days the methods
# flag that nobody has confirmed (Sep 7 and 8) stay off this list.
known_bot_days <- tibble::tribble(
  ~day,                  ~sms, ~idle, ~errors,
  as.Date("2026-09-17"), TRUE, TRUE,  TRUE,
  as.Date("2026-09-24"), TRUE, TRUE,  TRUE,
  # Ran without a browser, or blocked GA, so no error trail.
  as.Date("2026-09-30"), TRUE, TRUE,  FALSE
)

# What one SMS costs, in dollars, by codes sent in the trailing 30 days.
# `up_to` is the top of each tier.
sms_price_tiers <- tibble::tribble(
  ~up_to,    ~price,
  50000,     0.0456,
  250000,    0.0453,
  1000000,   0.0428,
  Inf,       0.0402
)

# Setup -----------------------------------------------------------------------

# The working directory is this folder; the shared layer is two levels up.
source("../../common/setup.R")

source("R/metrics.R")
source("R/preflight.R")

con <- connect_athena()

# A failed check adds a banner. See R/preflight.R.
preflight <- run_preflight_safety_check(con, thresholds, known_bot_days)
write_preflight_status(preflight)

# Yesterday is the newest whole day; the event stream also holds today's.
through <- toronto_today() - 1L
calendar_from <- calendar_start(through)
chart_from <- calendar_start(through, chart_weeks)

pairs <- account_pairs(con)
sms <- dplyr::filter(sms_days(con), day <= through)
accounts <- account_days(pairs, through)
errors <- dplyr::filter(error_days(error_codes(con)), day <= through)

scored <- list(
  sms = score_sms(sms, thresholds),
  idle = score_idle(accounts, thresholds),
  errors = score_errors(errors, thresholds)
)
scores <- method_scores(scored)
calendar <- calendar_days(scores, calendar_from, through)
since_launch <- accounts_since_launch(pairs, through)

write_traffic_summary(calendar, through)

# The newest day each method reported, which differs: GA runs a day behind.
reported_through <- purrr::map(scored, \(rows) max(rows$day[!is.na(rows$fired)]))

page_header <- "page-header.html"

write_preflight_banner(preflight, page_header)

cat(
  c(
    '<div class="page-strip">',
    # "Most": GA runs a day behind the rest; the calendar's outline shows it.
    glue("  <p><strong>Most data through {format_long_date(through)}.</strong> ",
         "Internal to Enterprise Digital Credentials, not for public ",
         "consumption.</p>"),
    "</div>"
  ),
  file = page_header, sep = "\n", append = TRUE
)

# Presentation ---------------------------------------------------------------

# Chart colours, mirroring _theme.scss: amber, the indicator light, only for
# what fired; slate grey for the rest.
robot <- list(accent = "#C77700", quiet = "#BFC6CD")

# Calendar shading: a fixed log scale, so a colour means the same every week,
# darkening as it climbs so it reads in greyscale.
strength_limits <- c(0.5, 50)
strength_breaks <- c(0.5, 1, 2, 5, 10, 20, 50)
strength_stops <- c(0.5, 1, 2, 2.5, 10, 50)
strength_ramp <- c("#F1F3F5", "#E3E6EA", "#D5DAE0", "#F2C55C", "#E89B00",
                   "#8F5200")
# Amber and brown mean a method fired: an unflagged day is held to the greys
# however high its volume (a launch), and a flagged day starts at amber.
unflagged_cap <- 2
flagged_floor <- 2.5
strength_values <- scales::rescale(log10(strength_stops),
                                   from = log10(strength_limits))
no_data <- "#F7F8F9"

ink <- "#1F2933"

brand_figure <- function(p, height = 0.09) {
  add_cds_logo(
    add_watermark(p, report_name = "CanadaLogin Automated Traffic",
                  date = through),
    height = height
  )
}

method_label <- function(m) methods$label[match(m, methods$method)]

# Relative luminance, to pick a label colour that shows on its cell.
luminance <- function(hex) {
  rgb <- grDevices::col2rgb(hex) / 255
  rgb <- ifelse(rgb <= 0.03928, rgb / 12.92, ((rgb + 0.055) / 1.055)^2.4)
  as.vector(c(0.2126, 0.7152, 0.0722) %*% rgb)
}

# GitHub-style grid, a column per week with Monday on top. A flagged day is
# labelled with its Strongest figure; days before launch are blank.
calendar_plot <- function(cal) {
  # The fill a day gets, to pick a label colour that shows on it.
  fill_of <- scales::gradient_n_pal(strength_ramp, strength_values)
  log_position <- function(x) {
    clamped <- pmin(pmax(x, strength_limits[1]), strength_limits[2])
    scales::rescale(log10(clamped), from = log10(strength_limits))
  }

  cells <- cal |>
    dplyr::filter(day >= canadalogin_launch) |>
    dplyr::mutate(
      week = day - (as.integer(format(day, "%u")) - 1L),
      # Monday on top: row 7 is Monday, row 1 Sunday. Numeric, so the month
      # lines can run between rows.
      row = 8L - as.integer(format(day, "%u")),
      shade = ifelse(n_fired > 0, pmax(peak, flagged_floor),
                     pmin(peak, unflagged_cap))
    )
  flagged_cells <- cells |>
    dplyr::filter(n_fired > 0) |>
    dplyr::mutate(
      label = paste0(round(strongest), "x"),
      ink_on = ifelse(luminance(fill_of(log_position(shade))) > 0.4,
                      ink, "#FFFFFF")
    )

  # The grid keeps all its weeks, so the figure is the same shape every week.
  weeks <- c(min(cal$day), max(cal$day) - (as.integer(format(max(cal$day), "%u")) - 1L))
  firsts <- seq(as.Date(format(min(cal$day), "%Y-%m-01")), max(cal$day),
                by = "month")
  firsts <- firsts[firsts >= weeks[1]]
  month_weeks <- firsts - (as.integer(format(firsts, "%u")) - 1L)

  # A stepped line around the first of each month, through the gaps between
  # squares, as on GitHub: the first's column splits between the two months.
  month_lines <- purrr::map(firsts[firsts > min(cells$day)], \(d) {
    w <- d - (as.integer(format(d, "%u")) - 1L)
    k <- as.integer(format(d, "%u"))
    step <- 8 - k + 0.5
    if (k == 1L) {
      tibble::tibble(x = w - 3.5, y = c(7.5, 0.5))
    } else {
      tibble::tibble(x = c(w + 3.5, w + 3.5, w - 3.5, w - 3.5),
                     y = c(7.5, step, step, 0.5))
    }
  }) |>
    dplyr::bind_rows(.id = "month")

  ggplot(cells, aes(week, row)) +
    geom_tile(aes(fill = shade), width = 6, height = 0.86) +
    geom_path(data = month_lines, aes(x, y, group = month),
              colour = "grey45", linewidth = 0.5, linejoin = "mitre") +
    geom_tile(data = dplyr::filter(cells, waiting),
              aes(linetype = "Waiting"),
              fill = NA, colour = ink, width = 6, height = 0.86,
              linewidth = 0.45) +
    geom_text(data = flagged_cells, aes(label = label),
              colour = flagged_cells$ink_on, size = 3.3, fontface = "bold") +
    scale_fill_gradientn(
      colours = strength_ramp, values = strength_values, trans = "log10",
      limits = strength_limits, breaks = strength_breaks,
      labels = \(x) paste0(x, "x"), oob = scales::squish, na.value = no_data,
      name = "Strongest method"
    ) +
    scale_linetype_manual(values = "11", name = NULL) +
    scale_x_date(breaks = month_weeks,
                 labels = format(firsts, "%b"),
                 limits = c(weeks[1] - 4L, weeks[2] + 4L), expand = c(0, 0)) +
    scale_y_continuous(breaks = c(7, 5, 3), labels = c("Mon", "Wed", "Fri"),
                       limits = c(0.5, 7.5), expand = c(0, 0)) +
    coord_fixed(ratio = 7) +
    guides(
      fill = guide_colourbar(order = 1, barheight = unit(3.2, "cm"),
                             barwidth = unit(0.35, "cm")),
      linetype = guide_legend(order = 2,
                              override.aes = list(fill = strength_ramp[2]))
    ) +
    theme_cds(base_size = 9) +
    theme(
      panel.border = element_blank(), panel.grid = element_blank(),
      axis.ticks = element_blank(), axis.title = element_blank(),
      axis.text = element_text(colour = "grey35"),
      # Pushed down, clear of the logo in the top right corner.
      legend.position = "right", legend.justification = "top",
      legend.box.margin = margin(t = 28),
      legend.key.size = unit(0.4, "cm"), legend.text = element_text(size = 8),
      legend.title = element_text(size = 8), legend.spacing.y = unit(0.1, "cm")
    )
}

# Two panels on one date axis: volume, with days that fired highlighted, and
# the ratio against its threshold.
method_figure <- function(rows, volume, volume_label, volume_note,
                          ratio_label, ratio_cut, ratio_cut_label, top = NULL) {
  rows <- rows |>
    dplyr::filter(day >= chart_from) |>
    dplyr::mutate(
      volume = .data[[volume]],
      kind = dplyr::case_when(fired %in% TRUE ~ "fired",
                              day_type(day) == "weekend" ~ "weekend",
                              .default = "weekday")
    )
  fills <- c(fired = robot$accent, weekday = robot$quiet,
             weekend = grDevices::adjustcolor(robot$quiet, alpha.f = 0.5))
  limits <- c(chart_from - 1L, through + 1L)

  limits_x <- scale_x_date(limits = limits, expand = c(0, 0))
  no_x_text <- theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())

  # A page may bring its own top panel; it gets this date axis either way.
  volume_panel <- if (!is.null(top)) {
    top + limits_x + no_x_text
  } else {
    ggplot(rows, aes(day, volume)) +
      geom_col(aes(fill = kind), width = 0.8) +
      scale_fill_manual(values = fills, guide = "none") +
      scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                         expand = expansion(mult = c(0, 0.06))) +
      limits_x +
      theme_cds() +
      no_x_text +
      theme(panel.grid.minor = element_blank()) +
      labs(x = NULL, y = volume_label, subtitle = volume_note)
  }

  ratio_panel <- ggplot(rows, aes(day, ratio)) +
    geom_hline(yintercept = ratio_cut, linetype = "dashed", colour = "grey45",
               linewidth = 0.4) +
    annotate("text", x = chart_from, y = ratio_cut, label = ratio_cut_label,
             hjust = 0, vjust = -0.5, size = 2.9, colour = "grey35") +
    geom_line(colour = robot$quiet, linewidth = 0.5, na.rm = TRUE) +
    geom_point(aes(colour = kind == "fired", size = kind == "fired"),
               na.rm = TRUE) +
    scale_colour_manual(values = c(`TRUE` = robot$accent, `FALSE` = "grey55"),
                        guide = "none") +
    scale_size_manual(values = c(`TRUE` = 2.2, `FALSE` = 0.8), guide = "none") +
    scale_y_continuous(labels = label_percent(), limits = c(0, 1)) +
    scale_x_date(limits = limits, expand = c(0, 0),
                 breaks = rev(seq(through, chart_from, by = "-2 weeks")),
                 date_labels = "%b %d") +
    theme_cds() +
    theme(panel.grid.minor = element_blank()) +
    labs(x = NULL, y = ratio_label)

  cowplot::plot_grid(volume_panel, ratio_panel, ncol = 1, align = "v",
                     axis = "lr", rel_heights = c(1.4, 1))
}

# The quarter's daily numbers, newest first.
daily_table <- function(rows, columns, labels) {
  rows |>
    dplyr::filter(day >= chart_from) |>
    dplyr::arrange(dplyr::desc(day)) |>
    dplyr::mutate(
      day = paste(format(day, "%a"), format_short_date(day)),
      multiple = fmt_multiple(multiple),
      fired = fired %in% TRUE
    ) |>
    dplyr::select(day, dplyr::all_of(columns), multiple, ratio, fired) |>
    gt() |>
    cols_align("right", multiple) |>
    fmt_number(dplyr::all_of(columns), decimals = 0) |>
    fmt_percent(ratio, decimals = 0) |>
    sub_missing(missing_text = "-") |>
    cols_label(.list = c(list(day = "Day"), labels,
                         list(multiple = "vs typical day"))) |>
    # The highlight alone marks a day that fired; a day not scored shows a
    # dash under "vs typical day".
    tab_style(style = cell_text(weight = "bold", color = robot$accent),
              locations = cells_body(rows = fired)) |>
    cols_hide(fired) |>
    tab_options(table.width = pct(100), table.font.size = px(14),
                data_row.padding = px(3), table.border.top.style = "none")
}

# Methods with no score at the start of the calendar, for the note under it.
late_starts <- purrr::imap(scored, \(rows, m) {
  first <- min(rows$day[!is.na(rows$fired)])
  if (first > calendar_from) first else NULL
}) |> purrr::compact()
```

# Overview

```{r overview-summary}
#| include: false
flagged <- dplyr::filter(calendar, n_fired > 0) |> dplyr::arrange(dplyr::desc(day))

# The note under the calendar. Methods that start on the same day share a
# sentence.
starts <- tibble::tibble(method = names(late_starts),
                         day = do.call(c, unname(late_starts)))
calendar_note <- c(
  if (length(late_starts) > 0) "Blank days have no method scored yet.",
  purrr::map_chr(split(starts$method, starts$day), \(m) {
    d <- starts$day[match(m[1], starts$method)]
    glue("{glue_collapse(method_label(m), sep = ', ', last = ' and ')} ",
         "{if (length(m) > 1) 'have' else 'has'} no score before ",
         "{format_short_date(d)}: too few earlier days to compare with.")
  }),
  if (any(calendar$waiting)) {
    "The newest days have a dotted outline until slower sources catch up."
  }
) |> paste(collapse = " ")

shaded_days <- if (nrow(flagged) == 0) {
  "none"
} else {
  glue_collapse(format_short_date(flagged$day), sep = ", ", last = " and ")
}

calendar_alt <- glue(
  "Calendar grid of the last six months, one column per week and one row per ",
  "weekday, each day shaded by how far its strongest method was above a ",
  "typical day: greys for days no method flagged, amber to brown for ",
  "flagged days. ",
  "Flagged days are labelled with their strongest method's multiple. ",
  "{nrow(flagged)} days are flagged: {shaded_days}."
)
```

## Row {height="auto"}

::: {.card title="Reading this dashboard"}

This dashboard looks for **automated traffic on CanadaLogin**: scripts and bots
rather than people. It is internal to Enterprise Digital Credentials and the
link is unlisted. For anything that leaves EDCP, please reach out to the
[Data and Research team](https://gcdigital.slack.com/archives/C0A6S9F7KV4).

It uses **three methods**, each on its own page: [SMS codes](#sms-codes),
[Idle accounts](#idle-accounts) and [Error patterns](#error-patterns). Each
page explains how its method works and when it fires. The calendar below
shades every day by its strongest method and labels the days a method flagged.
As we find more methods, we will add them here.

**A flag is a suspicion, not a finding.** It says the day looked different from typical 
usage. Further investigation is needed to determine if the flagged activity is truly
automated.

:::

## Row {height="auto"}

::: {.card title="Days flagged"}

```{r calendar}
#| fig-width: 11
#| fig-height: 2.9
#| fig-alt: !expr calendar_alt
brand_figure(calendar_plot(calendar), height = 0.12)
```

::: {.figure-note}
A flagged day shows its *strongest* method from the table below, rounded. `r calendar_note`
:::

:::

## Row {height="auto"}

::: {.card title="Flagged days"}

```{r flagged-table}
if (nrow(flagged) == 0) {
  cat("No method fired in the last six months.")
} else {
  flagged |>
    dplyr::mutate(
      day_label = paste(format(day, "%a"), format_short_date(day)),
      count = glue("{n_fired} of {nrow(methods)}"),
      which = purrr::map_chr(methods_fired, \(m) {
        pages <- methods[methods$method %in% m, ]
        glue_collapse(glue("[{pages$label}](#{pages$page})"), sep = ", ")
      }),
      strongest = fmt_multiple(strongest)
    ) |>
    dplyr::select(day_label, count, which, strongest) |>
    gt() |>
    fmt_markdown(which) |>
    cols_label(day_label = "Day", count = "Methods", which = "Which",
               strongest = "Strongest") |>
    tab_options(table.width = pct(100), table.font.size = px(14),
                data_row.padding = px(4), table.border.top.style = "none")
}
```

::: {.figure-note}
*Strongest* is the largest volume any method that fired reached, against
that method's typical day.
:::

:::

# SMS codes

```{r sms-summary}
#| include: false
sms_rows <- scored$sms
sms_week <- method_window(sms_rows, reported_through$sms, "sms_sent",
                          "sms_success", "sms_sent",
                          baseline_days = thresholds$baseline_days)
sms_extra <- extra_on_flagged(sms_rows, chart_from, "sms_sent")
sms_extra_cost <- extra_sms_cost(sms_rows, chart_from, sms_price_tiers)
```

## Row {height="auto"}

::: {.card title="How this method works"}
When a user needs to prove they control a phone number, CanadaLogin texts a 
one-time-password to that number, and the user types it back. Real users enter about 96%
 of their codes correctly. A bot flooding the sign-up page sends codes that nobody 
 enters. This method fires when **codes sent are at least `r thresholds$sms$volume`x a typical day** and **fewer than `r percent(thresholds$sms$entry_rate_below)` are
 entered**.
:::

## Row {height="150px"}

::: {.valuebox color="primary"}
SMS codes sent, last 7 days

`r comma(sms_week$volume)`

`r fmt_multiple(sms_week$multiple)` a typical week
:::

::: {.valuebox color="info"}
Codes entered, last 7 days

`r percent(sms_week$ratio, accuracy = 1)`

`r percent(sms_week$typical_ratio, accuracy = 1)` on a typical day
:::

::: {.valuebox color="secondary"}
Extra SMS codes, last three months

`r fmt_about(sms_extra)`

Costing about `r dollar(round(sms_extra_cost, -2))`
:::

## Row {height="560px"}

::: {.card title="SMS codes sent and entered each day (last three months)"}

```{r sms-chart}
#| fig-width: 13
#| fig-height: 4.8
#| fig-alt: |
#|   Two charts on a shared date axis. Above, SMS codes sent each day, with
#|   flagged days in amber. Below, the share of codes entered each day, near
#|   96 percent on most days, with a dashed line at 50 percent.
p <- method_figure(
  sms_rows,
  volume = "sms_sent", volume_label = "SMS codes sent",
  volume_note = glue("Fires at {thresholds$sms$volume}x a typical day or ",
                     "more. Lighter bars are weekends, compared only with ",
                     "weekends."),
  ratio_label = "Entered correctly", ratio_cut = thresholds$sms$entry_rate_below,
  ratio_cut_label = glue("Fires below {percent(thresholds$sms$entry_rate_below)}")
)
brand_figure(p)
```

:::

## Row

::: {.card title="Each day (last three months)"}

```{r sms-table}
sms_rows |>
  dplyr::select(day, sms_sent, sms_success, multiple, ratio, fired) |>
  daily_table(c("sms_sent", "sms_success"),
              list(sms_sent = "SMS sent", sms_success = "SMS entered")) |>
  cols_label(ratio = "Entered")
```

:::

# Idle accounts

```{r idle-summary}
#| include: false
idle_rows <- scored$idle
idle_week <- method_window(idle_rows, reported_through$idle, "new_accounts",
                           "idle_same_day", "new_accounts",
                           baseline_days = thresholds$baseline_days)
idle_extra <- extra_on_flagged(idle_rows, chart_from, "new_accounts")
launch_latest <- since_launch[since_launch$date == through, ]

idle_flag_days <- dplyr::filter(idle_rows, fired %in% TRUE)$day

by_week <- accounts_by_week(since_launch)
```

## Row {height="auto"}

::: {.card title="How this method works"}
When real users sign up for a CanadaLogin account, they are doing so to reach a public 
service. Most go straight to it. On a typical day, only about 18% of new accounts don't.
Often, a bot making accounts in bulk leaves them idle. This method fires when **new accounts 
are at least `r thresholds$idle$volume`x a typical day** and **at least
`r percent(thresholds$idle$idle_share_at_least)` of them are idle on the day they were 
made**.
:::

## Row

### Column {.tabset}

#### Detection

##### Row {height="150px"}

::: {.valuebox color="primary"}
New accounts, last 7 days

`r comma(idle_week$volume)`

`r fmt_multiple(idle_week$multiple)` a typical week
:::

::: {.valuebox color="info"}
Idle on the day made, last 7 days

`r percent(idle_week$ratio, accuracy = 1)`

`r percent(idle_week$typical_ratio, accuracy = 1)` on a typical day
:::

::: {.valuebox color="secondary"}
Extra accounts, last three months

`r fmt_about(idle_extra)`

`r extra_line(sum(idle_flag_days >= chart_from))`
:::

##### Row {height="560px"}

::: {.card title="New accounts each day, and the share idle on the day made (last three months)"}

```{r idle-chart}
#| fig-width: 13
#| fig-height: 4.8
#| fig-alt: |
#|   Two charts on a shared date axis. Above, new accounts each day, with
#|   flagged days in amber. Below, the share of new accounts idle on the day
#|   they were made, with a dashed line at 50 percent.
p <- method_figure(
  idle_rows,
  volume = "new_accounts", volume_label = "New accounts",
  volume_note = glue("Fires at {thresholds$idle$volume}x a typical day or ",
                     "more. Lighter bars are weekends, compared only with ",
                     "weekends."),
  ratio_label = "Idle on the day made",
  ratio_cut = thresholds$idle$idle_share_at_least,
  ratio_cut_label = glue("Fires at ",
                         "{percent(thresholds$idle$idle_share_at_least)} or more")
)
brand_figure(p)
```

:::

##### Row

::: {.card title="Each day (last three months)"}

```{r idle-table}
idle_rows |>
  dplyr::select(day, new_accounts, idle_same_day, multiple, ratio, fired) |>
  daily_table(c("new_accounts", "idle_same_day"),
              list(new_accounts = "New accounts",
                   idle_same_day = "Idle on the day made")) |>
  cols_label(ratio = "Share idle")
```

:::

#### Accounts since launch

##### Row {height="150px"}

::: {.valuebox color="primary"}
All accounts, `r format_short_date(through)`

`r comma(launch_latest$all_accounts)`

Since the April 2026 launch
:::

::: {.valuebox color="info"}
Idle accounts

`r comma(launch_latest$idle_accounts)`

`r percent(launch_latest$idle_share, accuracy = 1)` of all accounts
:::

::: {.valuebox color="secondary"}
Signed in to a service

`r comma(launch_latest$signed_in_to_service)`

At least one partner service
:::

##### Row {height="560px"}

::: {.card title="Accounts since launch, by week"}

```{r launch-chart}
#| fig-width: 13
#| fig-height: 4.6
#| fig-alt: |
#|   Line chart of CanadaLogin accounts since the April 2026 launch, one point
#|   per week: all accounts, and accounts that have signed in to a partner
#|   service. The gap between the lines is idle accounts. Ticks along the
#|   bottom mark days flagged on the Detection tab.
# Each week's point sits on its last day so far (`date`, not `week_end`), so
# an unfinished week does not plot ahead of the data.
weekly <- by_week |>
  tidyr::pivot_longer(c(all_accounts, signed_in_to_service),
                      names_to = "measure", values_to = "accounts")

line_labels <- c(all_accounts = "All accounts",
                 signed_in_to_service = "Signed in to a service")
line_colours <- c(all_accounts = robot$accent, signed_in_to_service = ink)

ends <- dplyr::filter(weekly, date == max(date))

p <- ggplot(weekly, aes(date, accounts, colour = measure)) +
  geom_segment(data = tibble::tibble(day = idle_flag_days),
               aes(x = day, xend = day, y = 0, yend = max(weekly$accounts) * 0.04),
               inherit.aes = FALSE, colour = "grey35", linewidth = 0.6) +
  annotate("text", x = min(idle_flag_days, through), y = max(weekly$accounts) * 0.06,
           label = "Flagged on Detection tab", hjust = 1.05, vjust = 0,
           size = 2.9, colour = "grey35") +
  geom_line(linewidth = 1) +
  geom_point(data = ends, size = 2.4) +
  geom_text(data = ends,
            aes(label = paste0(comma(accounts), "  ", line_labels[measure])),
            hjust = -0.08, fontface = "bold", size = 3.3, show.legend = FALSE) +
  scale_colour_manual(values = line_colours, guide = "none") +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.06))) +
  # Breaks stop at the data; the right padding is room for the end labels.
  scale_x_date(breaks = rev(seq(through, min(weekly$date), by = "-4 weeks")),
               date_labels = "%b %d", expand = expansion(mult = c(0.02, 0.32))) +
  theme_cds() +
  theme(panel.grid.minor = element_blank()) +
  labs(x = NULL, y = "Accounts since launch",
       subtitle = glue("Each week's last day, through {format_short_date(through)}."))
brand_figure(p)
```

:::

##### Row {height="auto"}

::: {.card title="Accounts by week"}

```{r accounts-weekly-table}
by_week |>
  dplyr::arrange(dplyr::desc(week_end)) |>
  dplyr::transmute(
    week = ifelse(date < week_end,
                  paste(format_short_date(week_end), "(to date)"),
                  format_short_date(week_end)),
    all_accounts, idle_accounts, signed_in_to_service, idle_share, new_accounts
  ) |>
  gt() |>
  fmt_number(c(all_accounts, idle_accounts, signed_in_to_service, new_accounts),
             decimals = 0) |>
  fmt_percent(idle_share, decimals = 0) |>
  cols_label(week = "Week ending", all_accounts = "All accounts",
             idle_accounts = "Idle accounts",
             signed_in_to_service = "Signed in to a service",
             idle_share = "Idle share", new_accounts = "New that week") |>
  tab_options(table.width = pct(100), table.font.size = px(14),
              data_row.padding = px(3), table.border.top.style = "none")
```

::: {.figure-note}
Weeks run Monday to Sunday, as on Sign-In Activity. Each count is as of the end
of the week, and earlier weeks do not change. *Idle accounts* had not yet signed
in to any partner service; *signed in to a service* had signed in to at least
one, and the two add up to *all accounts*. *New that week* is accounts made in
the week. An idle account is not necessarily automated: some people make an
account and never use it.
:::

:::

# Error patterns

```{r errors-summary}
#| include: false
error_rows <- scored$errors
errors_week <- method_window(error_rows, reported_through$errors, "signature",
                             "signature", "all_errors",
                             baseline_days = thresholds$baseline_days,
                             baseline = "typical")
errors_extra <- extra_on_flagged(error_rows, chart_from, "signature",
                                 baseline = "typical")
```

## Row {height="auto"}

::: {.card title="How this method works"}
Four errors are rare on a normal day: invalid phone numbers, SMS limits, wrong
codes and interrupted sign-ins. When a bot works through sign-up, they rise
together. This method fires when **at least
`r thresholds$errors$groups_at_least` of the 4 are each
`r thresholds$errors$group_volume`x their typical day** and **together
they are at least `r percent(thresholds$errors$share_at_least)` of all
errors**. A bot that doesn't use a normal browser leaves no trace here.
:::

## Row {height="150px"}

::: {.valuebox color="primary"}
Signature errors, last 7 days

`r comma(errors_week$volume)`

`r fmt_multiple(errors_week$multiple)` a typical week
:::

::: {.valuebox color="info"}
Share of all errors, last 7 days

`r percent(errors_week$ratio, accuracy = 1)`

`r percent(errors_week$typical_ratio, accuracy = 1)` on a typical day
:::

::: {.valuebox color="secondary"}
Extra signature errors, last three months

`r fmt_about(errors_extra)`

`r extra_line(sum(error_rows$fired[error_rows$day >= chart_from] %in% TRUE))`
:::

## Row {height="560px"}

::: {.card title="Error events each day, and the signature errors' share (last three months)"}

```{r errors-chart}
#| fig-width: 13
#| fig-height: 4.8
#| fig-alt: |
#|   Two charts on a shared date axis. Above, stacked bars of error events
#|   each day, the four signature errors in colour and all others in grey,
#|   with a marker above each flagged day. Below, the signature errors' share
#|   of all errors each day, with a dashed line at 30 percent.
# Signature errors in brand colours other than orange, since amber means
# "fired". Each legend label has its error codes on a second line.
group_codes <- purrr::map_chr(names(signature_labels), \(g) {
  paste(names(signature_groups)[signature_groups == g], collapse = ", ")
})
error_groups <- c(
  setNames(paste0(signature_labels, "\n", group_codes), names(signature_labels)),
  other = "All other errors"
)
error_colours <- c(
  phone_invalid = unname(colors$brand["red"]),
  sms_limit = unname(colors$brand["blue"]),
  interrupted = unname(colors$brand["forest"]),
  wrong_code = unname(colors$brand["green"]),
  other = "#C9CED4"
)

error_stack <- error_rows |>
  dplyr::filter(day >= chart_from) |>
  dplyr::mutate(other = all_errors - signature) |>
  tidyr::pivot_longer(dplyr::all_of(names(error_groups)),
                      names_to = "group", values_to = "events") |>
  # The first level stacks on top, so grey caps each bar.
  dplyr::mutate(group = factor(group, rev(names(error_groups))))

error_fired <- error_rows |>
  dplyr::filter(day >= chart_from, fired %in% TRUE)

error_top <- ggplot(error_stack, aes(day, events)) +
  geom_col(aes(fill = group), width = 0.85) +
  geom_point(data = error_fired, aes(day, all_errors), shape = 25,
             fill = robot$accent, colour = robot$accent, size = 2.2,
             position = position_nudge(y = max(error_rows$all_errors) * 0.04)) +
  scale_fill_manual(values = error_colours, labels = error_groups,
                    breaks = names(error_groups), name = NULL) +
  scale_y_continuous(labels = label_comma(), limits = c(0, NA),
                     expand = expansion(mult = c(0, 0.1))) +
  guides(fill = guide_legend(nrow = 1)) +
  theme_cds() +
  # Room after each label, or the long codes run into the next key.
  theme(panel.grid.minor = element_blank(), legend.position = "top",
        legend.justification = "left", legend.key.size = unit(0.35, "cm"),
        legend.text = element_text(margin = margin(r = 14)),
        legend.margin = margin(0, 0, 0, 0)) +
  labs(x = NULL, y = "Error events per day")

p <- method_figure(
  error_rows,
  volume = "signature", volume_label = NULL, volume_note = NULL,
  top = error_top,
  ratio_label = "Share of all errors",
  ratio_cut = thresholds$errors$share_at_least,
  ratio_cut_label = glue("Fires at {percent(thresholds$errors$share_at_least)} or more")
)
brand_figure(p)
```

:::

## Row

::: {.card title="Each day (last three months)"}

```{r errors-table}
error_rows |>
  dplyr::select(day, dplyr::all_of(names(signature_labels)), all_errors,
                multiple, ratio, fired) |>
  daily_table(c(names(signature_labels), "all_errors"),
              c(as.list(signature_labels), list(all_errors = "All errors"))) |>
  cols_label(ratio = "Signature share")
```

:::

```{r cleanup}
#| include: false
# include: false matters for layout: this chunk sits in the last Row, where
# anything visible becomes a card and takes width from the table.
DBI::dbDisconnect(con)
```

{{< include ../../_analytics.qmd >}}
