---
title: "CanadaLogin Support"
author: "EDCP Data and Research Team"  # colin.douglas@cds-snc.ca
slug: support
format:
  dashboard:
    include-before-body: page-header.html
    include-after-body: analytics-tag.html # see _analytics.qmd
params:
  ga_page_title: "Support Dashboard"
---

```{r setup}
# The working directory is this folder, shared layer is two levels up
source("../../common/setup.R")

source("R/metrics.R")
source("R/preflight.R")

con <- connect_athena()

accent <- "#115740"

# A failed check adds a banner. See R/preflight.R.
preflight <- run_preflight_safety_check(con, today = Sys.Date())
write_preflight_status(preflight)

# The two sources are current to different days
data_through <- call_centre_data_through(con)
snapshot_date <- psom_snapshot_date(con)

psom_through <- snapshot_date - 1L

# How far back every weekly chart runs
chart_from <- seq(as.Date(format(max(data_through, psom_through), "%Y-%m-01")),
                  by = "-2 months", length.out = 2)[2]

# For a card title, where the exact dates are on the axis below it.
chart_span_label <- "last three months"

# "Aug 8"
format_short_date <- function(d) {
  d <- as.Date(d)
  paste0(format(d, "%b"), " ", as.integer(format(d, "%d")))
}

# "August 8", not "August 08"
format_long_date <- function(d) {
  d <- as.Date(d)
  paste0(format(d, "%B"), " ", as.integer(format(d, "%d")))
}

window_label <- glue("last {tolower(fmt_count(summary_window_weeks, 'week'))}")
prior_window_label <- "vs previous"

page_header <- "page-header.html"

write_preflight_banner(preflight, page_header)

cat(
  c(
    '<div class="page-strip">',
    # The PSOM half of this line is held back with the Partner support page.
    glue('  <p><strong>Call centre data through {format_long_date(data_through)}.',
         "</strong> Internal to Enterprise Digital Credentials, not for public ",
         "consumption.</p>"),
    "</div>"
  ),
  file = page_header, sep = "\n", append = TRUE
)

brand_figure <- function(p, height = 0.09) {
  add_cds_logo(
    add_watermark(p, report_name = "CanadaLogin Support", date = data_through),
    height = height
  )
}

# A bar spans its seven days and its tick sits at the end of that span, so the
# two move together.
week_offset <- 3.5
week_tick_offset <- 7L

week_axis <- function(weeks, limits = NULL, max_labels = 14L,
                     expand = waiver()) {
  weeks <- sort(unique(weeks))
  # Every other week past max_labels, counted back so the newest keeps its.
  step <- if (length(weeks) > max_labels) 2L else 1L
  labelled <- rev(weeks[seq(length(weeks), 1L, by = -step)])
  scale_x_date(
    breaks = labelled + week_tick_offset,
    labels = format(labelled + 6L, "%b %d"),
    limits = limits,
    expand = expand
  )
}

# Goes with week_axis(), which labels a bar with the last day it covers.
week_axis_title <- "Week ending"

table_options <- function(table) {
  tab_options(
    table,
    table.width = pct(100),
    table.font.size = px(14),
    data_row.padding = px(4),
    table.border.top.style = "none"
  )
}
```

# Overview

## Row {height="330px"}

::: {.card title="About this dashboard"}

This dashboard reports the **support the CanadaLogin team provides**.
It is internal to Enterprise Digital Credentials and the link is unlisted, so
it isn't visible to the general public. It's for *your* information. For
anything that leaves EDCP, please reach out to the
[Data and Research team](https://gcdigital.slack.com/archives/C0A6S9F7KV4). We
are happy to provide you with a bespoke calculation or the underlying data.

**A red banner at the top of the page means a check failed at render time.** Do
not quote anything until it clears. If you don't see a red banner (it's hard to
miss), then you can assume that all of the preflight data quality checks passed.

The definitions come from the
[metrics cookbook](https://cds-snc.github.io/canadalogin-metrics-cookbook/cookbook/call_centre.html),
which is the source of truth. This page is republished in place every week.

:::

## Row

::: {.card title="About the call centre"}

The **Call centre** tab counts calls from members of the public to the
CanadaLogin support line. The call centre sends a weekly report covering
Sunday to Saturday, a few days after the week ends, so the newest week here is
usually last week's. Each call's reason is recorded as a *topic*. One call may
cover several topics, and some calls have no topic recorded at all.

:::: {.content-hidden when-format="html"}
The **Partner support** tab counts tickets on the Partner Success and
Operations (PSOM) Jira board, where departments integrating a service with
CanadaLogin ask for help. This includes things like onboarding requests, environment
access, and escalations to product teams. It is not where members of the public go.
Partner support metrics are currently in development, and **hidden** in this view.
::::

Volumes are small: a few dozen calls or a coule tickets a week. A change
of a few calls turns into a large percentage, so trust the counts before the
percentages. Every comparison is the last four reported weeks against the four
before them.

:::

# Call centre

```{r calls-summary}
#| include: false

weeks <- call_weeks(con)
topics <- call_topics(con)

current <- recent_weeks(weeks, data_through)
prior <- prior_weeks(weeks, data_through)

calls_now <- sum(current$calls)
calls_prior <- sum(prior$calls)
calls_delta <- fmt_delta(relative_change(calls_now, calls_prior))

wait_now <- weighted_weekly(current, "avg_delay_seconds")
abandoned_now <- sum(current$calls_abandoned)
length_now <- weighted_weekly(current, "avg_call_length_seconds")

window_weeks_label <- glue(
  "{format_short_date(min(current$week))} to {format_short_date(max(current$week_end))}"
)

# The charts run on the reported weeks ending inside the charted span.
charted <- weeks |> filter(week_end >= chart_from)

# A week the sign-in data does not cover has no rate and is left off the chart
charted_rate <- call_rate(charted, daily_active_users(con)) |>
  filter(!is.na(calls_per_100))
newest_rate <- charted_rate |> slice_max(week, n = 1)
```

## Row {height="150px"}

::: {.valuebox color="primary"}
Calls, excluding test calls (`r window_label`)

`r format(calls_now, big.mark = ",")`

`r calls_delta` `r prior_window_label`
:::

::: {.valuebox color="info"}
Average wait to answer (`r window_label`)

`r fmt_duration(wait_now)`

`r fmt_count(abandoned_now, "call")` abandoned before being answered
:::

::: {.valuebox color="secondary"}
Average call length (`r window_label`)

`r fmt_duration(length_now)`

Includes test calls
:::

## Row {height="500px"}

::: {.card title="Call volume" width="60%"}

```{r calls-chart}
#| fig-width: 8.2
#| fig-height: 4.1
#| fig-alt: |
#|   Bar chart of calls to the CanadaLogin support line per week, one bar per
#|   reported week, excluding test calls.

p <- ggplot(charted, aes(week + week_offset, calls)) +
  geom_col(width = 7, fill = accent, colour = "white", linewidth = 0.25) +
  geom_text(aes(label = calls), vjust = -0.5, size = 3, colour = "grey30") +
  scale_y_continuous(breaks = pretty_breaks(5),
                     expand = expansion(mult = c(0, 0.1))) +
  week_axis(charted$week) +
  theme_cds() +
  theme(panel.grid.major.x = element_blank()) +
  labs(x = week_axis_title, y = "Calls",
       subtitle = "Calls accepted by the support line each week, excluding test calls.")

brand_figure(p)
```

:::

::: {.card title="`r glue('Why users called ({window_label})')`" width="40%"}

```{r topics-chart}
#| fig-width: 5.4
#| fig-height: 4.3
#| fig-alt: |
#|   Horizontal bar chart of calls over the last four weeks, grouped by what they
#|   were about and sorted from most to least common, each bar labelled with its
#|   count of calls and its share of all calls in the window.

window_topics <- topics_in_weeks(topics, current)

# distinct() so a call recorded against two topics in one category counts once
by_category <- window_topics |>
  distinct(call_no, category) |>
  count(category, name = "calls") |>
  # Keep every named category on the axis so the chart always has the same rows
  complete(category = factor(topic_category_levels, levels = topic_category_levels),
           fill = list(calls = 0L)) |>
  filter(category != "Other" | calls > 0) |>
  arrange(calls) |>
  mutate(category = factor(category, levels = category))

# Calls the report counted that the topic dump has no reason
calls_without_topic <- calls_now - n_distinct(window_topics$call_no)

p <- ggplot(by_category, aes(calls, category)) +
  geom_col(fill = accent, width = 0.7) +
  geom_text(aes(label = paste0(calls, " (", round(100 * calls / calls_now), "%)")),
            hjust = -0.2, size = 3.2, colour = "grey30") +
  scale_x_continuous(breaks = pretty_breaks(4),
                     expand = expansion(mult = c(0, 0.3))) +
  theme_cds() +
  theme(panel.grid.major.y = element_blank()) +
  labs(x = "Calls", y = NULL,
       subtitle = glue("Calls by what they were about, {window_weeks_label},\n",
                       "from the topics the call centre recorded."))

brand_figure(p, height = 0.11)
```

::: {.figure-note}
Each bar counts **calls**, not topic records. One call may have many topics, one or 
none. Because of that, the percentages do not necessarily add to 100%.
:::

:::

## Row {height="420px"}

::: {.card title="`r glue('Support demand ({chart_span_label})')`"}

```{r call-rate-chart}
#| fig-width: 12
#| fig-height: 3.5
#| fig-alt: |
#|   Scatter plot of calls per 100 daily active users for each reported week, one
#|   dot per week, with a LOESS smoothing line through them and the newest week
#|   labelled with its value.

p <- ggplot(charted_rate, aes(week + week_offset, calls_per_100)) +
  geom_smooth(method = "loess", formula = y ~ x, se = FALSE,
              colour = "grey40", linewidth = 0.9) +
  geom_point(colour = accent, size = 2.4) +
  geom_text(data = newest_rate, aes(label = sprintf("%.2f", calls_per_100)),
            vjust = -1.2, colour = accent, fontface = "bold", size = 3.4) +
  scale_y_continuous(breaks = pretty_breaks(5),
                     expand = expansion(mult = c(0.05, 0.15))) +
  # Not a scale limit, which would silently drop the line falling below it.
  expand_limits(y = 0) +
  # An extra week of slack so we don't accidentally truncate labels
  week_axis(charted_rate$week, expand = expansion(add = c(2, 7))) +
  theme_cds() +
  labs(x = week_axis_title, y = "Calls per 100 daily users",
       subtitle = paste("Call centre demand, measured against the size of the user base"))

brand_figure(p)
```

::: {.figure-note}
Each week's calls, excluding test calls, divided by the sign-in user-days in
that same week. Read as a percentage: 0.5 calls per 100 users means 0.5% of the people
who signed in that called for support.
:::

:::

## Row

::: {.card title="`r glue('Call metrics ({window_label})')`"}

```{r metrics-table}
# One row per metric for cols_nanoplot()
call_metrics <- tibble::tribble(
  ~label,                        ~column,                   ~unit,      ~good,  ~agg,
  "Calls, excluding test calls", "calls",                   "count",    NA,     "mean",
  "Calls accepted",              "calls_accepted",          "count",    NA,     "mean",
  "Calls abandoned",             "calls_abandoned",         "count",    "down", "mean",
  "Test calls",                  "test_calls",              "count",    NA,     "mean",
  "Answered within 60 s",        "pct_answered_within_60s", "percent",  "up",   "weighted",
  "Average wait (m:s)",         "avg_delay_seconds",        "duration", "down", "weighted",
  "Average call (m:s)",         "avg_call_length_seconds",  "duration", NA,     "weighted"
)

# One column holds every unit, so a value is formatted before it gets there and
# the row label carries the unit.
fmt_metric <- function(x, unit) {
  switch(unit,
    count = format(round(x, 1), big.mark = ","),
    percent = sprintf("%.0f%%", x * 100),
    duration = fmt_minutes(x)
  )
}

# The summary window, oldest first, so a row reads left to right into its trend.
window_weeks <- charted |>
  slice_max(week_end, n = summary_window_weeks) |>
  arrange(week_end)

week_labels <- format_short_date(window_weeks$week_end)
newest <- nrow(window_weeks)

# One formatted string per metric per week: metrics down the rows, weeks across.
cells <- t(mapply(\(col, unit) fmt_metric(window_weeks[[col]], unit),
                  call_metrics$column, call_metrics$unit))
colnames(cells) <- week_labels

arrows <- c(up = "\u25b2", down = "\u25bc", flat = "\u2013")

# Sometimes up is good and sometimes up is bad. We use "good"/"bad" to be explicit
verdict_colours <- c(good = "#008B45",
                     bad = colors$brand[["red"]],
                     none = "#5C6670")
verdict_weights <- c(good = "700", bad = "700", none = "400")

direction <- purrr::map_chr(call_metrics$column, \(col) {
  delta_direction(relative_change(window_weeks[[col]][newest],
                                  window_weeks[[col]][newest - 1L]))
})

verdict <- purrr::map2_chr(direction, call_metrics$good, \(moved, good) {
  if (moved == "flat" || is.na(good)) "none" else if (moved == good) "good" else "bad"
})

# Only the newest week carries an arrow; the earlier columns are the record.
cells[, newest] <- paste0(
  cells[, newest],
  ' <span style="color: ', verdict_colours[verdict],
  "; font-weight: ", verdict_weights[verdict], '">', arrows[direction], "</span>"
)

# Counts just use a regular average, not weighted
averages <- purrr::pmap_chr(
  list(call_metrics$column, call_metrics$unit, call_metrics$agg),
  \(col, unit, agg) {
    fmt_metric(
      if (agg == "weighted") weighted_weekly(window_weeks, col) else mean(window_weeks[[col]]),
      unit
    )
  }
)

series <- charted |>
  arrange(week_end) |>
  transmute(week = format(week_end, "w%m%d"), across(all_of(call_metrics$column))) |>
  pivot_longer(-week, names_to = "column") |>
  pivot_wider(names_from = week, values_from = value)

dplyr::bind_cols(call_metrics["label"], tibble::tibble(average = averages),
                 as.data.frame(cells)) |>
  mutate(column = call_metrics$column) |>
  left_join(series, by = "column") |>
  select(-column) |>
  gt() |>
  fmt_markdown(columns = all_of(week_labels[newest])) |>
  cols_nanoplot(
    columns = -c(label, average, all_of(week_labels)),
    plot_type = "bar",
    # Bars run from zero, so a metric that only moves between four and five
    # draws even bars rather than a sawtooth.
    expand_y = 0,
    new_col_name = "trend",
    new_col_label = glue("Trend, {chart_span_label}"),
    options = nanoplot_options(
      data_bar_fill_color = accent,
      data_bar_stroke_color = accent
    )
  ) |>
  cols_label(
    label = "",
    average = html(glue("{fmt_count(summary_window_weeks)}-week<br>average"))
  ) |>
  cols_align("right", columns = c(average, all_of(week_labels))) |>
  cols_align("center", columns = trend) |>
  # Ruled off, or a column of averages sitting in front of four date headings
  # reads as another week.
  tab_style(
    cell_borders(sides = "right", color = "#DFE2E5", weight = px(1)),
    list(cells_body(columns = average), cells_column_labels(columns = average))
  ) |>
  cols_width(label ~ pct(24), trend ~ pct(28), everything() ~ pct(9.6)) |>
  table_options()
```

::: {.figure-note}

The color of the arrow indications whether the movement is positive or negative, 
independent of the direction. Some metrics do not an inherent value to their movement,
so they are coloured grey.

*Accepted* is every call that reached the queue, answered or abandoned. *Calls* is 
accepted minus test calls. Averages are the call centre's own weekly figures.

:::

:::

```{r partner-support-held-back}
#| include: false
# Put _partner-support.qmd back here when you're ready to sharea it
```

```{r cleanup}
#| include: false
# include: false matters for layout: this chunk sits in the last Row, where
# anything visible becomes a card and takes width from the table.
DBI::dbDisconnect(con)
```

{{< include ../../_analytics.qmd >}}
